### 2013-01-14 doc/ms.tex
Add manuscript--note it uses clemson.bib.

%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

\documentclass[manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:

%% \documentclass[preprint2]{aastex}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

\newcommand{\myemail}{skywalker@galaxy.far.far.away}
\newcommand{\ctwo}{${\rm C}_2$}
\newcommand{\cthree}{${\rm C}_3$}
\newcommand{\cfour}{${\rm C}_4$}
\newcommand{\cfive}{${\rm C}_5$}
\newcommand{\csix}{${\rm C}_6$}
\newcommand{\cseven}{${\rm C}_7$}
\newcommand{\ceight}{${\rm C}_8$}
\newcommand{\ceightr}{${\rm C}_8^r$}
\newcommand{\nar}{New Astron. Rev.}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

\shorttitle{Formation of ${\rm C}_n$ Molecules}
\shortauthors{Yu et al.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{Formation of ${\rm C}_n$ Molecules in Oxygen-rich Interiors of Type II
Supernovae}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{Tianhong Yu, Donald D. Clayton, and Bradley S. Meyer}
\affil{Department of Physics and Astronomy, Clemson Universit, Clemson, SC 29634-0978}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
Two reaction-rate-based kinetic models for condensation of carbon dust via the
growth of precursor linear carbon chains are currently under debate. The first
involved forming \ctwo\ molecules via radiative association of free C
atoms; the second forms \ctwo\ molecules by the endoergic reaction
${\rm CO} + {\rm C} \to {\rm C}_2 + O$. Both are
followed by C captures until the linear chain eventually makes an isomeric
transition to ringed carbon on which rapid growth of graphite may occur.
These two approaches give vastly different results. Because of the high
importance of condensable carbon for current problems in astronomy,
we study these competing claims with an intentionally limited reaction-rate
network that shows clearly that initiation by
${\rm C} + {\rm C} \to {\rm CO} + \gamma$  is the dominant
pathway to carbon rings. We propose an explanation for why the second pathway
is not nearly as effective as its proponents calculated it to be.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{globular clusters: general --- globular clusters: individual(NGC 6397,
NGC 6624, NGC 7078, Terzan 8}

\section{Introduction}

The problem historically of condensing carbon SUNOCONs in the interiors of
expanding Type II supernovae is that most of the synthesized carbon is bathed
in more abundant oxygen and was long presumed to be oxidized by it. This
changed when \citet{1999Sci...283.1290C} introduced a kinetic theory by
which carbon can condense thermally in gas having more abundant oxygen.
That theory is noteworthy in having every chemical reaction from the initial
O $>$ C gas to macroscopic graphite included in a kinetic network, even though
most of the cross sections for those reactions and the rates of isomeric
transitions from linear carbon chains to carbon rings are not accurately known.
Their paper provided an existence proof that carbon can condense in O-rich gas.
Its calculations showed that rare carbon-ring molecules were not prevented from
formation despite rapid oxidation of their molecular precursors, although
oxidation does greatly reduce the abundance of those Cn chains. That initial
theory has been amplified during the past decade by several studies
\citep{2001ApJ...562..480C,2003ApJ...594..312D,2006ApJ...638..234D,
2009ApJ...703..642C,2010ApJ...713....1C,2011NewAR..55..155C,
2013ApJ...762....5C}.

In basic agreement with this chemical model, \citet{2009ApJ...703..642C} raised
questions about the most effective way of producing \ctwo\ molecules,
which is the
first step to linear carbon chains. Using a large network of chemical
reactions, \citet{2009ApJ...703..642C} discovered that the neutral-neutral
reaction $CO + C \to C_2 + O$
has a reasonably large cross section at temperatures near
5000K despite being endothermic by 4.8eV. Although the CO target abundance for
production of \ctwo\ in this manner must be calculated, they stated that at
$T=5000$K the rate factor
$\langle \sigma v \rangle = k_{CO,C} = 8.6 \times 10^{-14}$ cm$^3$ s$^{-1}$
created \ctwo\ much more
rapidly than the slow radiative reaction $C + C \to C_2 + \gamma$.
Sensing its significance,
they claimed in their list of conclusions: ``2. A new pathway to the formation
of carbon chains is active in the O-rich mass zone of the unmixed ejecta and
is identified as the CO conversion to \ctwo\ via collisions with C.''  They were
unable to evaluate its full quantitative consequences because their reaction
network terminated at \cthree\
and did not include the formation of linear carbon
chains Cn and their isomerization to carbon rings. Doing so is one goal of our
study. But the overriding goal is to point out large abundance differences
between the computations of these two groups and to resolve them if possible.

Several important consequences for astronomy depend on careful
analysis of this claim that the production of \ctwo\ owing to the reaction
$C+C \to C_2 + \gamma$, as \citet{1999Sci...283.1290C,2001ApJ...562..480C}
had done, severely
underestimates the abundances of linear carbon chains because much more \ctwo\
is made earlier \citep{2010ApJ...713....1C} near T=5000K. Testing this
competition is essential for understanding of dust condensation within
supernovae. Dust created by supernova expansions is currently under intense
study owing to three types of astronomical observations: (1) of dust observed
in single supernova remnants; (2) of dust observed in early low-metallicity
galaxies; (3) of supernova-condensed carbon dust (SUNOCONs) extracted from
meteorites. Each of these topics depends sensitively on how much carbon,
both numbers and sizes, is able to condense in cooling SNII interiors.
Therefore we study this competition carefully.

Crucial to this task is the lifetime τCO of CO molecules. Their thermal
dissociation lifetime τγ is calculated from detailed balance with the
radiative association reaction, as in Section 2.1 of
\citet{2001ApJ...562..480C}.
Because of the large 11.1eV binding energy of the CO molecule,
$\tau_\gamma$ is very
temperature sensitive.  For readers numerical ease we will tabulate
$\tau_\gamma$ at
selected key temperatures in Table \ref{tab:quantities} to follow.
The flux and spectrum of newly
injected Compton electrons \citep{1991ApJ...375..221C} yields the lifetime
$\tau_e$ of CO
molecules against inelastic scattering dissociation by Compton electrons
caused by the 56Co radioactivity. In a gas of pure CO the mean energy per ion
pair is defined as the energy of primary electrons divided by the number of
pairs produced. Liu and Victor (1994) calculated the mean energy per ion pair
in pure CO gas and obtained the result ΔE=32.3 eV deposited per dissociated CO
pair, which agrees well with the measurement of 32.2 eV by
\citet{1968...Klots}.
So the efficiency of energetic electrons for dissociating CO seems well
established. A lifetime $\tau_{CO}$ near one week is typical in SN 1987A, but
would be longer in SNII synthesizing less $^{56}$Co and at times greater than
about 8 months.

\section{The Physical Model and Network}

Because our goal is to study the chemistry, we can take a very simple physical
model of the expansion; namely, temperature T=3800/(t/100d)=3.30x1010Ks/t(s),
where t is the time elapsed since core collapse and nO=1010cm-3 and
$n_C = 10^9$ cm$^{-3}$
at the starting time t=t(6000K) for our chemical network at
T=6000K. From our model choice for T(t) we get
$t(6000K) = 5.47 \times 10^6$s. At
subsequent times nO(t)=1010cm-3(t/t(6000))-3 owing to homologous expansion.
Let N be the number in a comoving, expanding, initially 1cm3 volume at 6000K
that held initially nO=1010cm-3 and nC=109cm-3. The only change of N during
expansion occurs through chemical reactions. N may be expressed as atom
fraction Y of the initial total number NO+NC= 1.10x1010 atoms. We
intentionally choose an O-rich interior having NO/NC=10, so that no carbon at
all would be able to condense if that interior were governed by chemical
equilibrium.

We use an intentionally limited set of chemical species because our goal is
to study carbon chemistry: C, O, CO, \ctwo, \cthree, ... \ceight and
\ceightr, the ringed isomer of \ceight, to which we give a lifetime
$\tau_8^r = 10$ s against thermal isomeric transition
from linear \ceight to ringed \ceightr.
Those ringed molecules are the seeds for carbon
growth because their oxidation rates are much smaller than oxidation rates of
linear Cn whereas its C capture rates are fast. We take ringed \ceightr to be
indestructible, simply integrating their rate of production. Our strategy is
to compute the number \ceightr remaining after expansion from two differing
sources of \ctwo\ initiating the linear Cn chains. Those two source reactions
are
\begin{itemize}
\item $C + C \to C_2 + \gamma$ \citep{1999Sci...283.1290C}.
\item $CO + C \to C_2 + O$  \citep{2009ApJ...703..642C,2010ApJ...713....1C}.
\end{itemize}
We take our reaction rates from the rate tables in
\citet{2009ApJ...703..642C,2010ApJ...713....1C}.
The rate for the second reaction is indeed
much greater than that of the first reaction above T=3000K;
but it becomes increasingly the smaller of the two below T=2500K.
We include the thermal inverse reaction of every reaction,
which we calculate as in Eq.(3) of \citet{2001ApJ...562..480C}.
See Table 1 below for sample thermal dissociation rates for CO molecules.
We also include in our network dissociation of CO by Compton electrons.
CO is the only molecule for which thermal photodissociation is the dominant
destruction mechanism. For that rate we use
$\tau_e = 10^5$s $\exp( (t-10^6{\rm s}) / 111 {\rm d} )$,
not fit to any specific model but with plausibility for SN1987A.
It lengthens to $\tau_e = 10^6$ s near eight months.
Because of their helpful cataloging of reaction rate tables,
and in order to compare results without rate differences, we take the
rates as given in the tables of
\citet{2009ApJ...703..642C,2010ApJ...713....1C}.
As one example, we take the rate for $C + C \to C_2 + \gamma$
as the rate given by RA4 in Table 5 in \citet{2009ApJ...703..642C}, p. 649.

Our computational reaction network is {\em libnucnet}
\citep{2007M&PSA..42.5215M} modified to carry the chemical
rather than nuclear network.  This network code has been thoroughly tested
on a wide variety of reaction networks and problems.
We scrupulously tested our network answers by hand calculations capable of
exposing coding errors.

\section{The Function $n_{CO}(t)$}

The interior core of C and O resulting from completed He burning in massive
stars is a mix of C and O atoms having bulk C/O $<$ 1. Post explosive cooling of
such matter will attempt to associate C and O into CO molecules, with rate
coefficient $k_{CO}$=3.3x10-17cm3s-1 \citep{1990ApJ...358..262L}.
The reaction C+O → CO+ γ is one of the crucial reactions of chemical
astrophysics. Its rate $k_{CO}$ is intrinsically slow because quantum mechanics
requires not only rearrangement of electronic shells but also simultaneous
creation of a photon during the collision; nonetheless, the huge product
nCnO in the He-exhausted core ensures steady growth for the CO abundance
until it is reversed by radioactive dissociation.

Evidently the abundance of CO within that zone during expansion attempts to
balance these creation and destruction effects, doing so exactly at the
time of maximum nCO. \citet{2013ApJ...762....5C}
has discussed the shape of the function
nCO(t). His Eq.(1) approximates the growth of nCO by its leading terms:
\begin{equation}
\frac{dn_{CO}}{dt} = n_{C(g)} n_O k_{CO} - \frac{n_{CO}}{\tau_{CO}} = 0
\label{eq:dncodt}
\end{equation}
at $t = t_{max}$.
The maximum abundance reached by CO is in cgs units
\begin{equation}
n_{CO}(t_max) = n_C n_O k_{CO} \tau_{CO} 
\label{eq:comax}
\end{equation}

This amount is equal to that formed during its last mean lifetime $\tau_{CO}$
against dissociation. If $\tau_{CO}$ is taken to be $\tau_\gamma$ because
the dissociation of CO is dominated by thermal photons,
one obtains the expression for the abundance $n_{CO}^{\gamma eq}$ in thermal
equilibrium: $n_{CO}^{\gamma eq} = n_C n_O k_{CO} \tau_\gamma$,
and is also entered in Table 1.

Expressed instead in terms of number fractions $Y_{CO} = n_{CO} / n$
and $Y_C = n_C / n$ where $n$ is the number density of all atoms,
Eq. (\ref{eq:dncodt}) transforms to 
\begin{equation}
\frac{dY_{CO}}{dt} = Y_C Y_O n k_{CO} - \frac{Y_{CO}}{\tau_{CO}}	
\label{eq:dycodt}
\end{equation}
which is the form integrated by our network of coupled reactions.
The number density n is needed for the rate n(cm-3)$k_{CO}$(cm3s-1).
In our numerical example we take $n_O = 10^{10}$ cm$^{-3}$ and
$n_C = 10^9$ cm$^{-3}$ at t(6000K) as starting conditions for the
chemical network. Subsequent values are $n = 1.1 \times 10^{10}$ cm$^{-3}$
$[t(6000)/t]^3$, where the expansion factor reduces the initial number
density appropriately. Expansion factors are also in Table 1. Then
Eq. (\ref{eq:comax}) reads:
\begin{equation}
Y_{CO}(t_{max}) = Y_C Y_O n k_{CO} \tau_{CO}
\label{eq:ycomax}
\end{equation}

The lifetime of CO against dissociation is a composite of two physical
reactions. Letting $\tau_\gamma$ be the photodissociation lifetime owing
to thermal photons and $\tau_e$ be the dissociation lifetime owing to fast
Compton electrons, we have
\begin{equation}
\frac{1}{\tau_{CO}} = \frac{1}{\tau_\gamma} + \frac{1}{\tau_e}
\label{eq:tau_co}
\end{equation}
Which partial lifetime dominates the dissociation depends on the temperature.
The radioactive lifetime $\tau_e$ is taken to be
$\tau_e = 10^5\ {\rm s} \exp( ( t -10^6{\rm s}) / 111 {\rm d} )$,
but the thermal photodissociation lifetime $\tau_\gamma$
depends strongly on temperature
owing to the large binding energy of the CO molecule.
Table \ref{tab:quantities} displays a
short list of $\tau_\gamma$ at key temperatures as well as several related
quantities.

One sees from Table \ref{tab:quantities}
that $\tau_\gamma$ dominates Eq. (\ref{eq:tau_co}) for $T > 3500$ K,
whereas Compton
electron dissociation $\tau_e$
dominates below 3500 K. We start computation of our
chemical network at $T = 6000$ K,
so $n_{CO}(t)$ will initially be small and will
grow as temperature declines owing to the lengthening of $\tau_\gamma$ with
falling temperature. After $t=t_{max}$ the abundance of CO declines owing to
the destruction rate $1/\tau_e$ exceeding the creation rate in
Eq. (\ref{eq:dncodt})
while the gas cools to temperatures at which carbon chains can grow and
isomerize to rings \citep{1999Sci...283.1290C}. Such rings are taken to be
the nucleations upon which graphite grows.

Figure \ref{fig:nco}
compares our network calculation of the abundance of CO molecules
with the expectation of Eq.(2) when τγ dominates the destruction of CO.
Solid points display the equilibrium product nCOγeq calculated from the
factors shown in Table \ref{tab:quantities}
and from the number densities $n_C$ and $n_O$ after
their initial values at T=6000K have been reduced by the expansion factor
(t/t(6000K))-3. Tight agreement for $T > 3500$ K is immediately evident,
demonstrating that for $T > 3500$ K the abundance of CO is almost exactly in
thermal equilibrium. Below 3500K the abundance of CO becomes much less than
the expectation nCOγeq  of thermal equilibrium because the dissociation of CO
comes to be dominated by Compton electrons. The dashed vertical line at
T=3500K marks the approximate boundary between these two mechanisms for CO
dissociation. Notice carefully in Fig. \ref{fig:nco}
that nCO grows slowly, not reaching
its maximum until expansion has cooled to T=3500K.
At maximum nCO= 1.5x106cm-3, corresponding to YCO=0.7x10-3. The growth of nCO
shown in Fig. \ref{fig:nco} differs markedly from the results of
\citet{2009ApJ...703..642C}.
Their results (e.g. Fig. 11) show nCO climbing quickly near 6000K to a large
maximum number fraction near 0.1. That maximum would almost exhaust free
carbon. Our results in Fig. \ref{fig:nco}
so differ from theirs that the difference
must be resolved. \citet{2013ApJ...762....5C} has analyzed the expectation
of growth of nCO to a single maximum before declining, and our results are
in line with that expectation.

These features are further detailed in Fig. \ref{fig:flows},
which shows the reaction
currents (reactions per second per atom) into and out of CO. There exists a
near steady state in that the production of CO is almost balanced by the
two flows destroying CO. The destruction flow $n_{CO}/\tau_\gamma$
almost balances the
association flow above 4000K except for a tiny excess leading to the
slow growth of nCO evident in Fig. \ref{fig:nco}. In that temperature range the
production by C+O→ CO+γ is in equilibrium with the thermal radiation field,
as Fig. \ref{fig:nco} implied. The destruction flow nCO/τe almost balances the
creation flow below 3500K. The transition between destruction modes occurs
near 3500K. It is no coincidence that the maximum of nCO occurs when
Compton electrons begin to dominate CO dissociation, because nCO would
continue growing as long as thermal photons dominate CO dissociation.

\section{Abundances of $C_n$}

Figure \ref{fig:ncoc2} displays the number density $n_{C_2}$ along with
that of $n_{CO}$. At its maximum $n_{C_2} =0.1$ cm$^{-3}$ is only about
$10^{-7}$ of $n_{CO}$. The reason \ctwo\ is so rare is that its dissociation
rate by thermal photons is much faster than that for CO because the binding
energy of {\bf \ctwo\ CORRECT?} is
so much less than that for CO. This $n_{C_2}$
maximum differs greatly
from results in \citet{2009ApJ...703..642C}, where their Fig. 11 shows the
maximum atom fraction of $n_{C_2}$ to be near $10^{-5}$,
equal to about $10^5$ cm$^{-3}$, almost 1\% of $n_{CO}$ at that time.
And their maximum for \ctwo\ occurs near 7000 K, far too hot for \ctwo\ to
be abundant in the face of rapid dissociation. The huge differences between
these two computations require an explanation. We find it likely that
\cite{2009ApJ...703..642C} inadvertently omitted photodissociation by thermal
photons from their destruction rates.

Figure \ref{fig:yi}
shows the abundances $Y_i$ of each species in our small network as a
function of time t-t(6000K) after T=6000K. From Table \ref{tab:quantities},
start time is $t(6000K) =5.47x10^6$ s. To display each $Y_i$ on a figure with
reasonable ordinate resolution, we have scaled each $C_n$ by the factor
stated in the box. Many features are noteworthy: (1) C and O are constant
because their small depletion is negligible on the scale shown;
(2) maxima in CO and \ctwo\ occur at almost exactly the same time
$t-t(6000K)= 4 \times 10^6$ s, as in Fig. \ref{fig:ncoc2};
(3) \cthree\ has very small abundance, about $3 \times 10^{-8}$ of \ctwo
at the \ctwo\ maximum, although much later \cthree\ slowly grows modestly
relative to much more abundant \ctwo; (4) the rise shapes of \cfour
through \ceight\ are very similar because they are linked by a near steady
state; (5) the ringed carbon \ceightr\ has similar abundance shape vs. time,
but notice that it is actually much more abundant than C7-8 because it
accumulates from isomeric transitions of \ceight\ and unlike $C_n$ does not
suffer from fast oxidation \citep{1999Sci...283.1290C}. Each of these
features is understandable in terms of the flows into and out of each species.

Figure \ref{fig:cn} shows the shape of $C_n$ vs. $n$ for \cthree\ to
\ceight\ at two different temperatures near 2000K. As temperature declines,
the curve flattens because photoejection from $C_n$ by thermal photons
(or phonons) weakens. These abundance ratios are almost in a steady state,
but that steady state changes slightly as T falls. These patterns show
almost equal values for $Y(C_3)$ because that curve is relatively flat
with time near $t-t(6000K) = 10^7$ s (Fig. \ref{fig:yi}).
Table \ref{tab:flows} lists our computed reaction flows both in and out of
\csix\ at T = 2031K and T = 1802K. The reactions are specified there in the
compact notation target(in,out)residual. Fig. \ref{fig:cn} and
Table \ref{tab:flows} are made to be studied together.
Note that the abundances of \ceight\ are very small:
$Y(C_8)= 10^{-36}$ at T = 1802K. The isomeric transition from linear to
ringed \ceight, for which we estimate a lifetime $\tau = 10$ s,
provides the nucleations for graphite growth. Figure \ref{fig:ncoc2} showed
that $Y(C_{8}^r)$

We call attention to several conclusions to be drawn from Table \ref{tab:flows}.
Firstly, the strongest flows by a wide margin involving C6 are
$C_5 + C \to C_6$,
which is very fast ($k = 3 \times 10^{-10} cm^3 s^{-1}$)
because vibrational excitation of \csix\
obviates the need for creating a photon \citep{1999Sci...283.1290C},
and its inverse reaction which ejects a C atom. Furthermore, those flows
are equal to three significant figures, illustrating the near steady
state of the abundance pattern. Secondly, thermal dissociation of \csix\ is
very much faster than its oxidation, showing the small effect of oxidation
on the abundance pattern. The destroying flows from \csix\ to \cfive\
stand in the approximate ratio $C_6(\gamma,C)/C_6(O,CO) = 5 \times 10^5$
at $T = 2031$ K and $2 \times 10^4$ at $T = 1802$ K.
Photodissociation dominates. The smaller value for that ratio at T=1802K
occurs because oxidation maintains its effectiveness as T drops but
thermal disruption does not, being much more temperature sensitive.
For this reason the abundance pattern is flatter and C6 is approximately
3000 times more abundant at T=1802K than at T=2031K.
It is for that reason that destruction flows in Table \ref{tab:flows}
for C6 are
larger at the smaller temperature.
The steady state shifts to new ratios as T falls.
Thirdly, calculation of the rates will be illustrated for sake of clarity
by the flow $C_6 + O \to CO + C_5$.
From Fig. \ref{fig:cn}
one sees that at T=2031K the abundance $Y(C_6) = 10^{-33.3}$.
The value of $Y(O) = 10^{10} cm^{-3} / 1.1 \times 10^{10} cm^{-3} = 0.909$,
so the flow per atom per
second (e.g. Eq.3) is dY/dt= Y(C6)Y(O)n(2031K)k(C6O).
Expansion from T=6000K to T=2031K has diluted the total number
density n to 1.1x1010cm-3 (2031K/6000K)3= 4.27x108cm-3.
The fast oxidation reaction rate is  k(C6O)=3x10-10cm3s-1.
Gathering factors yields approximately 4x10-35 n-1s-1,
in good approximation to the Table \ref{tab:flows}
flow entry $3.61 \times 10^{-35} n^{-1}s^{-1}$.

Our calculations have shown clearly that producing \ctwo\ molecules near
5000K via the CO + C reaction \citep{2009ApJ...703..642C} is not a viable
prospect for condensation of carbon dust via linear carbon chains.
The abundance of CO is far too small for it to seed high-T \ctwo\ production.
The abundance of C8 rings grows much later (Fig. 4) near 2000K, as
\citet{1999Sci...283.1290C,2001ApJ...562..480C} had found.
These rings grew from \ctwo\ created by simple carbon association,
$C + C \to C_2 + \gamma$.
Furthermore, the abundance of \ctwo\ is very small near 5000K
(Fig. \ref{fig:ncoc2}),
primarily because its thermal dissociation rate is much too fast for
it to have significant abundance at that high T.
What little \ctwo\ is made at 5000K is immediately dissociated by
thermal photos. Therefore its small steady-state abundance is inadequate
for building abundances of \cthree\ and beyond.

\section{Contrast with \citet{2009ApJ...703..642C}}

The large numerical differences between the results of
\citet{1999Sci...283.1290C,2001ApJ...562..480C}
and those of \citet{2009ApJ...703..642C}
seem to be characterized by these differences:
\begin{enumerate}

\item Instead of growing large CO abundance near Y(CO)=0.1 at T=5500K
as in Fig. 11 of \citet{2009ApJ...703..642C}, we find that $Y(CO)$
builds to a maximum of only 10-3, which it achieves only slowly
(Fig. \ref{fig:ncoc2}), reaching that maximum only at T=3500K rather
than 5500K.

\item We find a maximum number density $n_{C_2} = 0.1$ cm$^{-3}$,
only about $10^{-7}$ of
$n_{CO}$. We find \ctwo\ to be rare at high temperature because its
dissociation rate by thermal photons is very much faster than for CO
owing to the smaller binding energy (6.3eV) of \ctwo. This $n_{C_2}$
maximum differs greatly from results in \citet{2009ApJ...703..642C},
where their Fig. 11 shows the maximum atom fraction of $n_{C_2}$ to be
near $10^{-5}$, equal to about $10^5$ cm$^{-3}$, almost 1\% of
$n_{CO}$ at that time. Our \ctwo/CO abundance ratio is,
in other words, only $10^{-5}$ of the same ratio calculated by
\citet{2009ApJ...703..642C}.

\end{enumerate}
We reasoned that these big differences could be understood if
\citet{2009ApJ...703..642C} had inadvertantly omitted the thermal
dissociation rates of small carbon molecules. Believing that to be the
cause for the discrepancy, we tested that hypothesis by performing our
own trial calculation involving only C, O, CO, \ctwo, and \cthree,
as they had done,
and omitted the $\tau_\gamma$ destruction terms.
Figure 6 displays the result.
The rapid rise of $Y(CO)$ to $10^{-2}$ at high temperature is very similar to
Fig. 11 of \citet{2009ApJ...703..642C}.
Similarity also describes $Y(C_2)$,
which grows quickly (Fig. 6) to 2x10-4 of Y(CO),
whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y(CO)$ to be
only $10^{-8}$ at T=5500K and, considerably later,
$Y(C_2)/Y(CO) = 10^{-7}$ at their maxima.

With photodissociation turned off, the destruction of \ctwo\ is primarily
by oxidation, $C_2+O \to CO + C$, whereas production of \ctwo is by
$CO + C \to C_2 + O$, the reaction we study in this work.
Those strive to balance, which if achieved establishes a steady state
ratio $Y(CO)/Y(C_2) = 3.5 \times 10^4$. Fig. 6 and their Fig. 11 do show
approximately that value, but $Y(C_2)$ declines faster than $Y(CO)$
because of declining production of \ctwo\ as T declines.

We could not expect detailed agreement, even if our hypothesis for the
cause of the discrepancy is correct. Our calculation used
O / C = 10 whereas they used O / C = 3 for the zone of their SNII model.
The temperature profiles also differ, we using T=3800/(t/100d) and they
T=18500/(t/100d)1.8.
We believe that their T is too hot owing to omission of CO cooling
(\citealp{1996ApJ...471..480L}, Fig. 5),
which we tried to accommodate roughly by
the choice T=3800K at t=100d, which is about 50% of the temperature
within published models which do omit CO cooling. And owing to the
factor $t^{-1.8}$, their T falls through a specified temperature drop
(say, 5000K to 3000K) more quickly than does our parameterization.
Nonetheless, any T profile declines though 5000K and reaches 3000K
somewhat later, so basically similar abundance results are expected.

Such detailed differences are small in comparison with inclusion of
thermal photodissociation. The similarity of Fig. 6 to their Fig.11,
and the huge differences of these figures from those of our network
amounts in our minds to a resolution of the discrepancy.

\acknowledgments

We are grateful.

\clearpage

\begin{figure}
\epsscale{.80}
%\plotone{f1.eps}
\caption{
Comparison of the density of CO molecules calculated by the numerical
network (curve) with the expectation nCOγeq = nCnO$k_{CO}$τγ for an abundance
nCO in thermal equilibrium (dots) with photons.
Above T=4000K the CO abundance is seen to be in an accurate thermal
equilibrium, but at lower temperature nCO is increasingly smaller than
thermal equilibrium would require. Instead of thermal photons,
the destruction of CO becomes increasingly dominated by
Compton electrons for $T < 3500$ K.
One see in Fig. \ref{fig:nco} that nCOmax occurs near 3500K,
which occurs near $10^7$ s (see Table \ref{tab:quantities})}. 
\label{fig:nco}
\end{figure}

\clearpage

\begin{figure}
\epsscale{.80}
%\plotone{f1.eps}
\caption{
Flows into and out of CO illustrate the near steady state between creation
and destruction and the transition region near 3500K between the two modes
of destruction of CO. The destruction flow nCOnC$k_{CO}$+C is only $3.27 \times
10^{-16}$ atom$^{-1}$s$^{-1}$, too small to be visible in Fig. \ref{fig:flows}. 
} \label{fig:flows}
\end{figure}

\clearpage

\begin{figure}
\epsscale{.80}
%\plotone{f1.eps}
\caption{
Number densities of CO and of \ctwo\ as functions of temperature.
The maximum density of \ctwo\ is 0.1 cm$^{-3}$.
Both abundances grow much more slowly than in the calculation by
\citet{2009ApJ...703..642C}.} \label{fig:ncoc2}
\end{figure}

\clearpage

\begin{figure}
\epsscale{.80}
%\plotone{f1.eps}
\caption{
The abundance (number per atom) of linear chains $C_n$ and of ringed isomer
\ceightr. We have scaled each $Y(C_n)$ by the factor stated in the box.}
\label{fig:yi}
\end{figure}

\clearpage

\begin{figure}
\epsscale{.80}
%\plotone{f1.eps}
\caption{
Shape of $Y(C_n)$ vs. n for \cthree to \ceight\ at two different temperatures
near 2000K. These shapes can be understood by the relative magnitudes of
flows into and out of $C_n$.
}
\label{fig:cn}
\end{figure}

\clearpage

\begin{deluxetable}{ccrrrrrrrrcrl}
\tabletypesize{\scriptsize}
\rotate
\tablecaption{Values of $\tau_\gamma$(CO) and related quantities at
selected $T$}
\label{tab:quantities}
\tablewidth{0pt}
\tablehead{
\colhead{POS} & \colhead{chip} & \colhead{ID} & \colhead{X} & \colhead{Y} &
\colhead{RA} & \colhead{DEC} & \colhead{IAU$\pm$ $\delta$ IAU} &
\colhead{IAP1$\pm$ $\delta$ IAP1} & \colhead{IAP2 $\pm$ $\delta$ IAP2} &
\colhead{star} & \colhead{E} & \colhead{Comment}
}
\startdata
0 & 2 & 1 & 1370.99 & 57.35    &   6.651120 &  17.131149 & 21.344$\pm$0.006  & 2
4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2
3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2
4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2
5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2
3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2
6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2
5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 & 22.189$\pm$0.011  & 2
4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 & edge \\
\enddata
\end{deluxetable}

%% If you use the table environment, please indicate horizontal rules using
%% \tableline, not \hline.
%% Do not put multiple tabular environments within a single table.
%% The optional \label should appear inside the \caption command.

\clearpage

\begin{table}
\begin{center}
\caption{Reaction Flows ($n^{-1}s^{-1}$) involving \csix\ at two temperatures.}
\label{tab:flows}
\begin{tabular}{crrrrrrrrrrr}
\tableline\tableline
Star & Height & $d_{x}$ & $d_{y}$ & $n$ & $\chi^2$ & $R_{maj}$ & $R_{min}$ &
\multicolumn{1}{c}{$P$\tablenotemark{a}} & $P R_{maj}$ & $P R_{min}$ &
\multicolumn{1}{c}{$\Theta$\tablenotemark{b}} \\
\tableline
1 &33472.5 &-0.1 &0.4  &53 &27.4 &2.065  &1.940 &3.900 &68.3 &116.2 &-27.639\\
2 &27802.4 &-0.3 &-0.2 &60 &3.7  &1.628  &1.510 &2.156 &6.8  &7.5 &-26.764\\
3 &29210.6 &0.9  &0.3  &60 &3.4  &1.622  &1.551 &2.159 &6.7  &7.3 &-40.272\\
4 &32733.8 &-1.2\tablenotemark{c} &-0.5 &41 &54.8 &2.282  &2.156 &4.313 &117.4 &78.2 &-35.847\\
5 & 9607.4 &-0.4 &-0.4 &60 &1.4  &1.669\tablenotemark{c}  &1.574 &2.343 &8.0  &8.9 &-33.417\\
6 &31638.6 &1.6  &0.1  &39 &315.2 & 3.433 &3.075 &7.488 &92.1 &25.3 &-12.052\\
\tableline
\end{tabular}
\end{center}
\end{table}

\bibliographystyle{apj}
\bibliography{clemson}

\end{document}

%%
%% End of file `sample.tex'.

### 2013-01-14 doc/ms.tex
Change to use some aliased commands.

@@
 
-\newcommand{\myemail}{skywalker@galaxy.far.far.away}
-\newcommand{\ctwo}{${\rm C}_2$}
-\newcommand{\cthree}{${\rm C}_3$}
-\newcommand{\cfour}{${\rm C}_4$}
-\newcommand{\cfive}{${\rm C}_5$}
-\newcommand{\csix}{${\rm C}_6$}
-\newcommand{\cseven}{${\rm C}_7$}
-\newcommand{\ceight}{${\rm C}_8$}
-\newcommand{\ceightr}{${\rm C}_8^r$}
+\newcommand{\ctwo}{{\rm C}_2}
+\newcommand{\cthree}{{\rm C}_3}
+\newcommand{\cfour}{{\rm C}_4}
+\newcommand{\cfive}{{\rm C}_5}
+\newcommand{\csix}{{\rm C}_6}
+\newcommand{\cseven}{{\rm C}_7}
+\newcommand{\ceight}{{\rm C}_8}
+\newcommand{\ceightr}{{\rm C}_8^r}
+\newcommand{\cenn}{{\rm C}_n}
+\newcommand{\cotoco}{${\rm C} + {\rm O} \to {\rm CO} + \gamma$}
+\newcommand{\twoctoctwo}{${\rm C} + {\rm C} \to \ctwo + \gamma$}
+\newcommand{\coctoctwo}{${\rm CO} + {\rm C} \to \ctwo + {\rm O}$}
+\newcommand{\ctowotococ}{$\ctwo + {\rm O} \to {\rm CO} + {\rm C}$}
 \newcommand{\nar}{New Astron. Rev.}
@@
 
-\shorttitle{Formation of ${\rm C}_n$ Molecules}
+\shorttitle{Formation of $\cenn$ Molecules}
 \shortauthors{Yu et al.}
@@
 
-\title{Formation of ${\rm C}_n$ Molecules in Oxygen-rich Interiors of Type II
+\title{Formation of $\cenn$ Molecules in Oxygen-rich Interiors of Type II
 Supernovae}
@@
 growth of precursor linear carbon chains are currently under debate. The first
-involved forming \ctwo\ molecules via radiative association of free C
-atoms; the second forms \ctwo\ molecules by the endoergic reaction
-${\rm CO} + {\rm C} \to {\rm C}_2 + O$. Both are
+involved forming $\ctwo$\ molecules via radiative association of free C
+atoms; the second forms $\ctwo$\ molecules by the endoergic reaction
+\coctoctwo. Both are
 followed by C captures until the linear chain eventually makes an isomeric
@@
 network that shows clearly that initiation by
-${\rm C} + {\rm C} \to {\rm CO} + \gamma$  is the dominant
+\twoctoctwo\ is the dominant
 pathway to carbon rings. We propose an explanation for why the second pathway
@@
 formation despite rapid oxidation of their molecular precursors, although
-oxidation does greatly reduce the abundance of those Cn chains. That initial
+oxidation does greatly reduce the abundance of those $\cenn$ chains.
+That initial
 theory has been amplified during the past decade by several studies
@@
 In basic agreement with this chemical model, \citet{2009ApJ...703..642C} raised
-questions about the most effective way of producing \ctwo\ molecules,
+questions about the most effective way of producing $\ctwo$\ molecules,
 which is the
@@
 reactions, \citet{2009ApJ...703..642C} discovered that the neutral-neutral
-reaction $CO + C \to C_2 + O$
+reaction \coctoctwo
 has a reasonably large cross section at temperatures near
 5000K despite being endothermic by 4.8eV. Although the CO target abundance for
-production of \ctwo\ in this manner must be calculated, they stated that at
+production of $\ctwo$\ in this manner must be calculated, they stated that at
 $T=5000$K the rate factor
 $\langle \sigma v \rangle = k_{CO,C} = 8.6 \times 10^{-14}$ cm$^3$ s$^{-1}$
-created \ctwo\ much more
-rapidly than the slow radiative reaction $C + C \to C_2 + \gamma$.
+created $\ctwo$\ much more
+rapidly than the slow radiative reaction \twoctoctwo.
 Sensing its significance,
@@
 of carbon chains is active in the O-rich mass zone of the unmixed ejecta and
-is identified as the CO conversion to \ctwo\ via collisions with C.''  They were
+is identified as the CO conversion to $\ctwo$\ via collisions with C.''  They were
 unable to evaluate its full quantitative consequences because their reaction
-network terminated at \cthree\
+network terminated at $\cthree$\
 and did not include the formation of linear carbon
-chains Cn and their isomerization to carbon rings. Doing so is one goal of our
+chains $\cenn$
+and their isomerization to carbon rings. Doing so is one goal of our
 study. But the overriding goal is to point out large abundance differences
@@
 Several important consequences for astronomy depend on careful
-analysis of this claim that the production of \ctwo\ owing to the reaction
-$C+C \to C_2 + \gamma$, as \citet{1999Sci...283.1290C,2001ApJ...562..480C}
+analysis of this claim that the production of $\ctwo$\ owing to the reaction
+\twoctoctwo, as \citet{1999Sci...283.1290C,2001ApJ...562..480C}
 had done, severely
-underestimates the abundances of linear carbon chains because much more \ctwo\
+underestimates the abundances of linear carbon chains because much more $\ctwo$\
 is made earlier \citep{2010ApJ...713....1C} near T=5000K. Testing this
@@
 pair is defined as the energy of primary electrons divided by the number of
-pairs produced. Liu and Victor (1994) calculated the mean energy per ion pair
-in pure CO gas and obtained the result ΔE=32.3 eV deposited per dissociated CO
+pairs produced. \citet{1994ApJ...435..909L}
+calculated the mean energy per ion pair
+in pure CO gas and obtained the result $\Delta E = 32.3$ eV
+deposited per dissociated CO
 pair, which agrees well with the measurement of 32.2 eV by
@@
 We use an intentionally limited set of chemical species because our goal is
-to study carbon chemistry: C, O, CO, \ctwo, \cthree, ... \ceight and
-\ceightr, the ringed isomer of \ceight, to which we give a lifetime
+to study carbon chemistry: C, O, CO, $\ctwo$, $\cthree$, ... $\ceight$\ and
+$\ceightr$, the ringed isomer of $\ceight$, to which we give a lifetime
 $\tau_8^r = 10$ s against thermal isomeric transition
-from linear \ceight to ringed \ceightr.
+from linear $\ceight$ to ringed $\ceightr$.
 Those ringed molecules are the seeds for carbon
 growth because their oxidation rates are much smaller than oxidation rates of
-linear Cn whereas its C capture rates are fast. We take ringed \ceightr to be
+linear $\cenn$
+whereas its C capture rates are fast. We take ringed $\ceightr$ to be
 indestructible, simply integrating their rate of production. Our strategy is
-to compute the number \ceightr remaining after expansion from two differing
-sources of \ctwo\ initiating the linear Cn chains. Those two source reactions
-are
+to compute the number $\ceightr$ remaining after expansion from two differing
+sources of $\ctwo$\ initiating the linear $\cenn$
+chains. Those two source reactions are
 \begin{itemize}
-\item $C + C \to C_2 + \gamma$ \citep{1999Sci...283.1290C}.
-\item $CO + C \to C_2 + O$  \citep{2009ApJ...703..642C,2010ApJ...713....1C}.
+\item \twoctoctwo\ \citep{1999Sci...283.1290C}.
+\item \coctoctwo\ \citep{2009ApJ...703..642C,2010ApJ...713....1C}.
 \end{itemize}
@@
 \citet{2009ApJ...703..642C,2010ApJ...713....1C}.
-As one example, we take the rate for $C + C \to C_2 + \gamma$
+As one example, we take the rate for \twoctoctwo\
 as the rate given by RA4 in Table 5 in \citet{2009ApJ...703..642C}, p. 649.
@@
 coefficient $k_{CO}$=3.3x10-17cm3s-1 \citep{1990ApJ...358..262L}.
-The reaction C+O → CO+ γ is one of the crucial reactions of chemical
+The reaction \cotoco\ is one of the crucial reactions of chemical
 astrophysics. Its rate $k_{CO}$ is intrinsically slow because quantum mechanics
@@
 compares our network calculation of the abundance of CO molecules
-with the expectation of Eq.(2) when τγ dominates the destruction of CO.
+with the expectation of Eq. (\ref{eq:comax}) when $\tau_\gamma$
+dominates the destruction of CO.
 Solid points display the equilibrium product nCOγeq calculated from the
@@
 slow growth of nCO evident in Fig. \ref{fig:nco}. In that temperature range the
-production by C+O→ CO+γ is in equilibrium with the thermal radiation field,
-as Fig. \ref{fig:nco} implied. The destruction flow nCO/τe almost balances the
+production by \cotoco\ in equilibrium with the thermal radiation field,
+as Fig. \ref{fig:nco} implied. The destruction flow $n_{CO}/\tau_e$
+almost balances the
 creation flow below 3500K. The transition between destruction modes occurs
@@
 
-\section{Abundances of $C_n$}
+\section{Abundances of $\cenn$}
 
-Figure \ref{fig:ncoc2} displays the number density $n_{C_2}$ along with
-that of $n_{CO}$. At its maximum $n_{C_2} =0.1$ cm$^{-3}$ is only about
-$10^{-7}$ of $n_{CO}$. The reason \ctwo\ is so rare is that its dissociation
+Figure \ref{fig:ncoc2} displays the number density $n_{\ctwo}$ along with
+that of $n_{CO}$. At its maximum $n_{\ctwo} =0.1$ cm$^{-3}$ is only about
+$10^{-7}$ of $n_{CO}$. The reason $\ctwo$\ is so rare is that its dissociation
 rate by thermal photons is much faster than that for CO because the binding
-energy of {\bf \ctwo\ CORRECT?} is
-so much less than that for CO. This $n_{C_2}$
+energy of {\bf $\ctwo$\ CORRECT?} is
+so much less than that for CO. This $n_{\ctwo}$
 maximum differs greatly
 from results in \citet{2009ApJ...703..642C}, where their Fig. 11 shows the
-maximum atom fraction of $n_{C_2}$ to be near $10^{-5}$,
+maximum atom fraction of $n_{\ctwo}$ to be near $10^{-5}$,
 equal to about $10^5$ cm$^{-3}$, almost 1\% of $n_{CO}$ at that time.
-And their maximum for \ctwo\ occurs near 7000 K, far too hot for \ctwo\ to
+And their maximum for $\ctwo$\ occurs near 7000 K, far too hot for $\ctwo$\ to
 be abundant in the face of rapid dissociation. The huge differences between
@@
 start time is $t(6000K) =5.47x10^6$ s. To display each $Y_i$ on a figure with
-reasonable ordinate resolution, we have scaled each $C_n$ by the factor
+reasonable ordinate resolution, we have scaled each $\cenn$\ by the factor
 stated in the box. Many features are noteworthy: (1) C and O are constant
 because their small depletion is negligible on the scale shown;
-(2) maxima in CO and \ctwo\ occur at almost exactly the same time
+(2) maxima in CO and $\ctwo$\ occur at almost exactly the same time
 $t-t(6000K)= 4 \times 10^6$ s, as in Fig. \ref{fig:ncoc2};
-(3) \cthree\ has very small abundance, about $3 \times 10^{-8}$ of \ctwo
-at the \ctwo\ maximum, although much later \cthree\ slowly grows modestly
-relative to much more abundant \ctwo; (4) the rise shapes of \cfour
-through \ceight\ are very similar because they are linked by a near steady
-state; (5) the ringed carbon \ceightr\ has similar abundance shape vs. time,
+(3) $\cthree$\ has very small abundance, about $3 \times 10^{-8}$ of $\ctwo$
+at the $\ctwo$\ maximum, although much later $\cthree$\ slowly grows modestly
+relative to much more abundant $\ctwo$; (4) the rise shapes of $\cfour$
+through $\ceight$\ are very similar because they are linked by a near steady
+state; (5) the ringed carbon $\ceightr$\ has similar abundance shape vs. time,
 but notice that it is actually much more abundant than C7-8 because it
-accumulates from isomeric transitions of \ceight\ and unlike $C_n$ does not
+accumulates from isomeric transitions of $\ceight$\ and unlike $\cenn$\ does not
 suffer from fast oxidation \citep{1999Sci...283.1290C}. Each of these
@@
 
-Figure \ref{fig:cn} shows the shape of $C_n$ vs. $n$ for \cthree\ to
-\ceight\ at two different temperatures near 2000K. As temperature declines,
-the curve flattens because photoejection from $C_n$ by thermal photons
+Figure \ref{fig:cn} shows the shape of $\cenn$\ vs. $n$ for $\cthree$\ to
+$\ceight$\ at two different temperatures near 2000K. As temperature declines,
+the curve flattens because photoejection from $\cenn$\ by thermal photons
 (or phonons) weakens. These abundance ratios are almost in a steady state,
 but that steady state changes slightly as T falls. These patterns show
-almost equal values for $Y(C_3)$ because that curve is relatively flat
+almost equal values for $Y(\cthree)$ because that curve is relatively flat
 with time near $t-t(6000K) = 10^7$ s (Fig. \ref{fig:yi}).
 Table \ref{tab:flows} lists our computed reaction flows both in and out of
-\csix\ at T = 2031K and T = 1802K. The reactions are specified there in the
+$\csix$\ at T = 2031K and T = 1802K. The reactions are specified there in the
 compact notation target(in,out)residual. Fig. \ref{fig:cn} and
 Table \ref{tab:flows} are made to be studied together.
-Note that the abundances of \ceight\ are very small:
+Note that the abundances of $\ceight$\ are very small:
 $Y(C_8)= 10^{-36}$ at T = 1802K. The isomeric transition from linear to
-ringed \ceight, for which we estimate a lifetime $\tau = 10$ s,
+ringed $\ceight$, for which we estimate a lifetime $\tau = 10$ s,
 provides the nucleations for graphite growth. Figure \ref{fig:ncoc2} showed
@@
 which is very fast ($k = 3 \times 10^{-10} cm^3 s^{-1}$)
-because vibrational excitation of \csix\
+because vibrational excitation of $\csix$
 obviates the need for creating a photon \citep{1999Sci...283.1290C},
@@
 are equal to three significant figures, illustrating the near steady
-state of the abundance pattern. Secondly, thermal dissociation of \csix\ is
+state of the abundance pattern. Secondly, thermal dissociation of $\csix$\ is
 very much faster than its oxidation, showing the small effect of oxidation
-on the abundance pattern. The destroying flows from \csix\ to \cfive\
+on the abundance pattern. The destroying flows from $\csix$\ to $\cfive$
 stand in the approximate ratio $C_6(\gamma,C)/C_6(O,CO) = 5 \times 10^5$
@@
 From Fig. \ref{fig:cn}
-one sees that at T=2031K the abundance $Y(C_6) = 10^{-33.3}$.
+one sees that at T=2031K the abundance $Y(\csix) = 10^{-33.3}$.
 The value of $Y(O) = 10^{10} cm^{-3} / 1.1 \times 10^{10} cm^{-3} = 0.909$,
@@
 
-Our calculations have shown clearly that producing \ctwo\ molecules near
+Our calculations have shown clearly that producing $\ctwo$\ molecules near
 5000K via the CO + C reaction \citep{2009ApJ...703..642C} is not a viable
 prospect for condensation of carbon dust via linear carbon chains.
-The abundance of CO is far too small for it to seed high-T \ctwo\ production.
-The abundance of C8 rings grows much later (Fig. 4) near 2000K, as
+The abundance of CO is far too small for it to seed high-T $\ctwo$\ production.
+The abundance of $\ceight$
+rings grows much later (Fig. \ref{fig:yi}) near 2000K, as
 \citet{1999Sci...283.1290C,2001ApJ...562..480C} had found.
-These rings grew from \ctwo\ created by simple carbon association,
-$C + C \to C_2 + \gamma$.
-Furthermore, the abundance of \ctwo\ is very small near 5000K
+These rings grew from $\ctwo$\ created by simple carbon association,
+\twoctoctwo.
+Furthermore, the abundance of $\ctwo$\ is very small near 5000K
 (Fig. \ref{fig:ncoc2}),
@@
 it to have significant abundance at that high T.
-What little \ctwo\ is made at 5000K is immediately dissociated by
+What little $\ctwo$\ is made at 5000K is immediately dissociated by
 thermal photos. Therefore its small steady-state abundance is inadequate
-for building abundances of \cthree\ and beyond.
+for building abundances of $\cthree$\ and beyond.
 
@@
 
-\item We find a maximum number density $n_{C_2} = 0.1$ cm$^{-3}$,
+\item We find a maximum number density $n_{\ctwo} = 0.1$ cm$^{-3}$,
 only about $10^{-7}$ of
-$n_{CO}$. We find \ctwo\ to be rare at high temperature because its
+$n_{CO}$. We find $\ctwo$\ to be rare at high temperature because its
 dissociation rate by thermal photons is very much faster than for CO
-owing to the smaller binding energy (6.3eV) of \ctwo. This $n_{C_2}$
+owing to the smaller binding energy (6.3eV) of $\ctwo$. This $n_{\ctwo}$
 maximum differs greatly from results in \citet{2009ApJ...703..642C},
-where their Fig. 11 shows the maximum atom fraction of $n_{C_2}$ to be
+where their Fig. 11 shows the maximum atom fraction of $n_{\ctwo}$ to be
 near $10^{-5}$, equal to about $10^5$ cm$^{-3}$, almost 1\% of
-$n_{CO}$ at that time. Our \ctwo/CO abundance ratio is,
+$n_{CO}$ at that time. Our $\ctwo$/CO abundance ratio is,
 in other words, only $10^{-5}$ of the same ratio calculated by
@@
 cause for the discrepancy, we tested that hypothesis by performing our
-own trial calculation involving only C, O, CO, \ctwo, and \cthree,
+own trial calculation involving only C, O, CO, $\ctwo$, and $\cthree$,
 as they had done,
@@
 Fig. 11 of \citet{2009ApJ...703..642C}.
-Similarity also describes $Y(C_2)$,
+Similarity also describes $Y(\ctwo)$,
 which grows quickly (Fig. 6) to 2x10-4 of Y(CO),
@@
 only $10^{-8}$ at T=5500K and, considerably later,
-$Y(C_2)/Y(CO) = 10^{-7}$ at their maxima.
+$Y(\ctwo)/Y(CO) = 10^{-7}$ at their maxima.
 
-With photodissociation turned off, the destruction of \ctwo\ is primarily
-by oxidation, $C_2+O \to CO + C$, whereas production of \ctwo is by
-$CO + C \to C_2 + O$, the reaction we study in this work.
+With photodissociation turned off, the destruction of $\ctwo$\ is primarily
+by oxidation, \ctowotococ, whereas production of $\ctwo$ is by
+\coctoctwo, the reaction we study in this work.
 Those strive to balance, which if achieved establishes a steady state
-ratio $Y(CO)/Y(C_2) = 3.5 \times 10^4$. Fig. 6 and their Fig. 11 do show
-approximately that value, but $Y(C_2)$ declines faster than $Y(CO)$
-because of declining production of \ctwo\ as T declines.
+ratio $Y(CO)/Y(\ctwo) = 3.5 \times 10^4$. Fig. 6 and their Fig. 11 do show
+approximately that value, but $Y(\ctwo)$ declines faster than $Y(CO)$
+because of declining production of $\ctwo$\ as T declines.
 
@@
 which we tried to accommodate roughly by
-the choice T=3800K at t=100d, which is about 50% of the temperature
+the choice T=3800K at t=100d, which is about 50\% of the temperature
 within published models which do omit CO cooling. And owing to the
@@
 \caption{
-Number densities of CO and of \ctwo\ as functions of temperature.
-The maximum density of \ctwo\ is 0.1 cm$^{-3}$.
+Number densities of CO and of $\ctwo$\ as functions of temperature.
+The maximum density of $\ctwo$\ is 0.1 cm$^{-3}$.
 Both abundances grow much more slowly than in the calculation by
@@
 \caption{
-The abundance (number per atom) of linear chains $C_n$ and of ringed isomer
-\ceightr. We have scaled each $Y(C_n)$ by the factor stated in the box.}
+The abundance (number per atom) of linear chains $\cenn$\ and of ringed isomer
+$\ceightr$. We have scaled each $Y(C_n)$ by the factor stated in the box.}
 \label{fig:yi}
@@
 \caption{
-Shape of $Y(C_n)$ vs. n for \cthree to \ceight\ at two different temperatures
+Shape of $Y(C_n)$ vs. n for $\cthree$\ to $\ceight$
+at two different temperatures
 near 2000K. These shapes can be understood by the relative magnitudes of
-flows into and out of $C_n$.
+flows into and out of $\cenn$.
 }
@@
 \begin{center}
-\caption{Reaction Flows ($n^{-1}s^{-1}$) involving \csix\ at two temperatures.}
+\caption{Reaction Flows ($n^{-1}s^{-1}$) involving $\csix$\
+at two temperatures.}
 \label{tab:flows}

### 2013-01-14 doc/ms.tex
Add tables and other edits.

@@
 \newcommand{\ctowotococ}{$\ctwo + {\rm O} \to {\rm CO} + {\rm C}$}
+\newcommand{\cfivectocsix}{$\cfive + {\rm C} \to \csix$}
+\newcommand{\csixotococfive}{${\rm C}_6 + {\rm O} \to {\rm CO} + {\rm C_5}$}
+\newcommand{\ncogeq}{n_{CO}^{\gamma eq}}
 \newcommand{\nar}{New Astron. Rev.}
@@
 
-\author{Tianhong Yu, Donald D. Clayton, and Bradley S. Meyer}
+\author{Tianhong Yu, Bradley S. Meyer, and Donald D. Clayton}
 \affil{Department of Physics and Astronomy, Clemson Universit, Clemson, SC 29634-0978}
@@
 
-\keywords{globular clusters: general --- globular clusters: individual(NGC 6397,
-NGC 6624, NGC 7078, Terzan 8}
+\keywords{atomic processes, ISM: abundances, ISM: general, meteorites, meteors, meteoroids, supernovae: general, supernovae: individual: SN 1987A}
 
@@
 reactions, \citet{2009ApJ...703..642C} discovered that the neutral-neutral
-reaction \coctoctwo
+reaction \coctoctwo\
 has a reasonably large cross section at temperatures near
@@
 
-Crucial to this task is the lifetime τCO of CO molecules. Their thermal
-dissociation lifetime τγ is calculated from detailed balance with the
+Crucial to this task is the lifetime $\tau_{CO}$ of CO molecules. Their thermal
+dissociation lifetime $\tau_\gamma$
+is calculated from detailed balance with the
 radiative association reaction, as in Section 2.1 of
@@
 $\tau_\gamma$ is very
-temperature sensitive.  For readers numerical ease we will tabulate
+temperature sensitive.  For readers' numerical ease we will tabulate
 $\tau_\gamma$ at
@@
 molecules against inelastic scattering dissociation by Compton electrons
-caused by the 56Co radioactivity. In a gas of pure CO the mean energy per ion
+caused by the $^{56}$Co
+radioactivity. In a gas of pure CO the mean energy per ion
 pair is defined as the energy of primary electrons divided by the number of
@@
 $t(6000K) = 5.47 \times 10^6$s. At
-subsequent times nO(t)=1010cm-3(t/t(6000))-3 owing to homologous expansion.
-Let N be the number in a comoving, expanding, initially 1cm3 volume at 6000K
-that held initially nO=1010cm-3 and nC=109cm-3. The only change of N during
-expansion occurs through chemical reactions. N may be expressed as atom
-fraction Y of the initial total number NO+NC= 1.10x1010 atoms. We
-intentionally choose an O-rich interior having NO/NC=10, so that no carbon at
+subsequent times $n_O(t) = 10^{10}{\rm cm}^{-3}(t/t(6000 {\rm K}))^{-3}$
+owing to homologous expansion.
+Let $N$ be the number in a comoving, expanding, initially 1 cm$^3$
+volume at 6000 K
+that held initially $n_O=10^{10}$ cm$^{-3}$ and $n_C = 10^9$ cm$^{-3}$.
+The only change of $N$ during
+expansion occurs through chemical reactions. $N$ may be expressed as atom
+fraction $Y$ of the initial total number
+$N_O + N_C = 1.10 \times 10^{10}$ atoms. We
+intentionally choose an O-rich interior having $N_O/N_C = 10$,
+so that no carbon at
 all would be able to condense if that interior were governed by chemical
@@
 destruction mechanism. For that rate we use
-$\tau_e = 10^5$s $\exp( (t-10^6{\rm s}) / 111 {\rm d} )$,
+$\tau_e (s) = 10^5 \exp( (t-10^6{\rm s}) / 111 {\rm d} )$,
 not fit to any specific model but with plausibility for SN1987A.
@@
 Our computational reaction network is {\em libnucnet}
-\citep{2007M&PSA..42.5215M} modified to carry the chemical
-rather than nuclear network.  This network code has been thoroughly tested
+(\citealp{2007M&PSA..42.5215M}--see also
+\url{http://sourceforge.net/projects/libnucnet/}) modified to follow
+the chemical rather than nuclear reactions.
+This network code has been thoroughly tested
 on a wide variety of reaction networks and problems.
@@
 balance these creation and destruction effects, doing so exactly at the
-time of maximum nCO. \citet{2013ApJ...762....5C}
+time of maximum $n_{CO}$. \citet{2013ApJ...762....5C}
 has discussed the shape of the function
-nCO(t). His Eq.(1) approximates the growth of nCO by its leading terms:
+$n_{CO}$(t). His Eq.(1) approximates the growth of $n_{CO}$ by its leading terms:
 \begin{equation}
@@
 \begin{equation}
-n_{CO}(t_max) = n_C n_O k_{CO} \tau_{CO} 
+n_{CO}(t_{max}) = n_C n_O k_{CO} \tau_{CO} 
 \label{eq:comax}
@@
 dominates the destruction of CO.
-Solid points display the equilibrium product nCOγeq calculated from the
+Solid points display the equilibrium product $\ncogeq$ calculated from the
 factors shown in Table \ref{tab:quantities}
@@
 thermal equilibrium. Below 3500K the abundance of CO becomes much less than
-the expectation nCOγeq  of thermal equilibrium because the dissociation of CO
+the expectation $\ncogeq$ of thermal equilibrium because the dissociation of CO
 comes to be dominated by Compton electrons. The dashed vertical line at
@@
 dissociation. Notice carefully in Fig. \ref{fig:nco}
-that nCO grows slowly, not reaching
+that $n_{CO}$ grows slowly, not reaching
 its maximum until expansion has cooled to T=3500K.
-At maximum nCO= 1.5x106cm-3, corresponding to YCO=0.7x10-3. The growth of nCO
+At maximum $n_{CO} = 1.5 \times 10^6$ cm$^{-3}$,
+corresponding to $Y(CO) = 0.7 \times 10^{-3}$. The growth of $n_{CO}$
 shown in Fig. \ref{fig:nco} differs markedly from the results of
 \citet{2009ApJ...703..642C}.
-Their results (e.g. Fig. 11) show nCO climbing quickly near 6000K to a large
+Their results (e.g. Fig. 11) show $n_{CO}$ climbing quickly near 6000K to a large
 maximum number fraction near 0.1. That maximum would almost exhaust free
@@
 must be resolved. \citet{2013ApJ...762....5C} has analyzed the expectation
-of growth of nCO to a single maximum before declining, and our results are
+of growth of $n_{CO}$ to a single maximum before declining, and our results are
 in line with that expectation.
@@
 association flow above 4000K except for a tiny excess leading to the
-slow growth of nCO evident in Fig. \ref{fig:nco}. In that temperature range the
+slow growth of $n_{CO}$ evident in Fig. \ref{fig:nco}. In that temperature range the
 production by \cotoco\ in equilibrium with the thermal radiation field,
@@
 creation flow below 3500K. The transition between destruction modes occurs
-near 3500K. It is no coincidence that the maximum of nCO occurs when
-Compton electrons begin to dominate CO dissociation, because nCO would
+near 3500K. It is no coincidence that the maximum of $n_{CO}$ occurs when
+Compton electrons begin to dominate CO dissociation, because $n_{CO}$ would
 continue growing as long as thermal photons dominate CO dissociation.
@@
 Note that the abundances of $\ceight$\ are very small:
-$Y(C_8)= 10^{-36}$ at T = 1802K. The isomeric transition from linear to
+$Y(\ceight)= 10^{-36}$ at T = 1802K. The isomeric transition from linear to
 ringed $\ceight$, for which we estimate a lifetime $\tau = 10$ s,
 provides the nucleations for graphite growth. Figure \ref{fig:ncoc2} showed
-that $Y(C_{8}^r)$
+that $Y(\ceightr)$
 
 We call attention to several conclusions to be drawn from Table \ref{tab:flows}.
-Firstly, the strongest flows by a wide margin involving C6 are
-$C_5 + C \to C_6$,
+Firstly, the strongest flows by a wide margin involving $\csix$\ are
+\cfivectocsix,
 which is very fast ($k = 3 \times 10^{-10} cm^3 s^{-1}$)
@@
 on the abundance pattern. The destroying flows from $\csix$\ to $\cfive$
-stand in the approximate ratio $C_6(\gamma,C)/C_6(O,CO) = 5 \times 10^5$
+stand in the approximate ratio
+${\rm C}_6(\gamma,{\rm C})/{\rm C_6}({\rm O},{\rm CO}) = 5 \times 10^5$
 at $T = 2031$ K and $2 \times 10^4$ at $T = 1802$ K.
@@
 thermal disruption does not, being much more temperature sensitive.
-For this reason the abundance pattern is flatter and C6 is approximately
+For this reason the abundance pattern is flatter and $\csix$\ is approximately
 3000 times more abundant at T=1802K than at T=2031K.
 It is for that reason that destruction flows in Table \ref{tab:flows}
-for C6 are
+for $\csix$\ are
 larger at the smaller temperature.
@@
 Thirdly, calculation of the rates will be illustrated for sake of clarity
-by the flow $C_6 + O \to CO + C_5$.
+by the flow
+\csixotococfive.
 From Fig. \ref{fig:cn}
-one sees that at T=2031K the abundance $Y(\csix) = 10^{-33.3}$.
+one sees that at $T = 2031$ K the abundance $Y(\csix) = 10^{-33.3}$.
 The value of $Y(O) = 10^{10} cm^{-3} / 1.1 \times 10^{10} cm^{-3} = 0.909$,
 so the flow per atom per
-second (e.g. Eq.3) is dY/dt= Y(C6)Y(O)n(2031K)k(C6O).
+second (e.g., Eq. \ref{eq:dycodt}) is $dY/dt= Y(\csix)Y(O)n(2031K)k(C6O)$.
 Expansion from T=6000K to T=2031K has diluted the total number
@@
 Comparison of the density of CO molecules calculated by the numerical
-network (curve) with the expectation nCOγeq = nCnO$k_{CO}$τγ for an abundance
-nCO in thermal equilibrium (dots) with photons.
+network (curve) with the expectation $\ncogeq = n_C n_O k_{CO} \tau_\gamma$
+for an abundance
+$n_{CO}$ in thermal equilibrium (dots) with photons.
 Above T=4000K the CO abundance is seen to be in an accurate thermal
-equilibrium, but at lower temperature nCO is increasingly smaller than
+equilibrium, but at lower temperature $n_{CO}$ is increasingly smaller than
 thermal equilibrium would require. Instead of thermal photons,
@@
 Compton electrons for $T < 3500$ K.
-One see in Fig. \ref{fig:nco} that nCOmax occurs near 3500K,
+One see in Fig. \ref{fig:nco} that $n_{CO}$max occurs near 3500K,
 which occurs near $10^7$ s (see Table \ref{tab:quantities})}. 
@@
 and destruction and the transition region near 3500K between the two modes
-of destruction of CO. The destruction flow nCOnC$k_{CO}$+C is only $3.27 \times
+of destruction of CO. The destruction flow $n_{CO}$nC$k_{CO}$+C is only $3.27 \times
 10^{-16}$ atom$^{-1}$s$^{-1}$, too small to be visible in Fig. \ref{fig:flows}. 
@@
 
-\begin{deluxetable}{ccrrrrrrrrcrl}
-\tabletypesize{\scriptsize}
-\rotate
-\tablecaption{Values of $\tau_\gamma$(CO) and related quantities at
-selected $T$}
+\begin{table}
+\begin{center}
+\caption{Values of $\tau_\gamma$(CO) and related quantities at
+selected time $t$ and temperature $T$}
 \label{tab:quantities}
-\tablewidth{0pt}
-\tablehead{
-\colhead{POS} & \colhead{chip} & \colhead{ID} & \colhead{X} & \colhead{Y} &
-\colhead{RA} & \colhead{DEC} & \colhead{IAU$\pm$ $\delta$ IAU} &
-\colhead{IAP1$\pm$ $\delta$ IAP1} & \colhead{IAP2 $\pm$ $\delta$ IAP2} &
-\colhead{star} & \colhead{E} & \colhead{Comment}
-}
-\startdata
-0 & 2 & 1 & 1370.99 & 57.35    &   6.651120 &  17.131149 & 21.344$\pm$0.006  & 2
-4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
-0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2
-3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
-0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2
-4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
-0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2
-5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
-0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2
-3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
-0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2
-6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
-0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2
-5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
-0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 & 22.189$\pm$0.011  & 2
-4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 & edge \\
-\enddata
-\end{deluxetable}
-
-%% If you use the table environment, please indicate horizontal rules using
-%% \tableline, not \hline.
-%% Do not put multiple tabular environments within a single table.
-%% The optional \label should appear inside the \caption command.
+\begin{tabular}{ccccccc}
+\tableline\tableline
+$t$ (s) & $t - t(6000 {\rm K})$ (s) & $\left(t / t(6000 {\rm K} \right)^{-3}$ & $T$ (K) & $\tau_\gamma$ (s) & $k_{CO}$ (cm$^{-3}$ s$^{-1}$) & $\ncogeq$ (cm$^{-3}$) \\
+\tableline
+$5.47 \times 10^6$ &
+  0 &
+  1 &
+  6000 &
+  $4.22 \times 10^{-2}$ &
+  $3.13 \times 10^{-17}$ &
+  $1.32 \times 10^1$ \\
+$5.97 \times 10^6$ &
+  $4.97 \times 10^5$ &
+  0.769 &
+  5500 &
+  $3.54 \times 10^{-1}$ &
+  $2.99 \times 10^{-17}$ &
+  $6.27 \times 10^1$ \\
+$6.57 \times 10^6$ &
+  $1.09 \times 10^6$ &
+  0.578 &
+  5000 &
+  $4.46 \times 10^{0}$ &
+  $2.83 \times 10^{-17}$ &
+  $4.24 \times 10^2$ \\
+$7.30 \times 10^6$ &
+  $1.82 \times 10^6$ &
+  0.422 &
+  4500 &
+  $9.70 \times 10^{1}$ &
+  $2.67 \times 10^{-17}$ &
+  $4.61 \times 10^3$ \\
+$8.21 \times 10^6$ &
+  $2.74 \times 10^6$ &
+  0.296 &
+  4000 &
+  $4.43 \times 10^{3}$ &
+  $2.48 \times 10^{-17}$ &
+  $9.67 \times 10^4$ \\
+$9.38 \times 10^6$ &
+  $3.91 \times 10^6$ &
+  0.198 &
+  3500 &
+  $5.86 \times 10^{5}$ &
+  $2.28 \times 10^{-17}$ &
+  $5.26 \times 10^6$ \\
+$1.09 \times 10^7$ &
+  $5.47 \times 10^6$ &
+  0.125 &
+  3000 &
+  $3.77 \times 10^{8}$ &
+  $2.05 \times 10^{-17}$ &
+  $1.21 \times 10^9$ \\
+\tableline
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 \begin{center}
-\caption{Reaction Flows ($n^{-1}s^{-1}$) involving $\csix$\
-at two temperatures.}
+\caption{Reaction Flows involving $\csix$\ at two temperatures.  {\bf UNITS
+ON FLOWS RIGHT?}}
 \label{tab:flows}
-\begin{tabular}{crrrrrrrrrrr}
+\begin{tabular}{ccc}
 \tableline\tableline
-Star & Height & $d_{x}$ & $d_{y}$ & $n$ & $\chi^2$ & $R_{maj}$ & $R_{min}$ &
-\multicolumn{1}{c}{$P$\tablenotemark{a}} & $P R_{maj}$ & $P R_{min}$ &
-\multicolumn{1}{c}{$\Theta$\tablenotemark{b}} \\
-\tableline
-1 &33472.5 &-0.1 &0.4  &53 &27.4 &2.065  &1.940 &3.900 &68.3 &116.2 &-27.639\\
-2 &27802.4 &-0.3 &-0.2 &60 &3.7  &1.628  &1.510 &2.156 &6.8  &7.5 &-26.764\\
-3 &29210.6 &0.9  &0.3  &60 &3.4  &1.622  &1.551 &2.159 &6.7  &7.3 &-40.272\\
-4 &32733.8 &-1.2\tablenotemark{c} &-0.5 &41 &54.8 &2.282  &2.156 &4.313 &117.4 &78.2 &-35.847\\
-5 & 9607.4 &-0.4 &-0.4 &60 &1.4  &1.669\tablenotemark{c}  &1.574 &2.343 &8.0  &8.9 &-33.417\\
-6 &31638.6 &1.6  &0.1  &39 &315.2 & 3.433 &3.075 &7.488 &92.1 &25.3 &-12.052\\
+& \multicolumn{2}{c}{Flow (${\rm atom}^{-1} {\rm s}^{-1}$)} \\
+\cline{2-3}
+Reaction & $T = 2031 {\rm K}$ & $T = 1802 {\rm K}$ \\
+$\cfive({\rm C},\gamma)\csix$ &
+  $1.67 \times 10^{-29}$ &
+  $4.79 \times 10^{-28}$\\
+$\csix(\gamma,{\rm C})\cfive$ &
+  $1.67 \times 10^{-29}$ &
+  $4.79 \times 10^{-28}$\\
+$\csix({\rm C},\gamma)\cseven$ &
+  $2.41 \times 10^{-39}$ &
+  $2.12 \times 10^{-32}$\\
+$\cseven(\gamma,{\rm C})\csix$ &
+  $1.26 \times 10^{-40}$ &
+  $7.27 \times 10^{-40}$\\
+$\csix({\rm O},{\rm CO})\cfive$ &
+  $3.61 \times 10^{-31}$ &
+  $2.90 \times 10^{-32}$\\
 \tableline

### 2013-01-14 doc/ms.tex
Add more edits.

@@
 \author{Tianhong Yu, Bradley S. Meyer, and Donald D. Clayton}
-\affil{Department of Physics and Astronomy, Clemson Universit, Clemson, SC 29634-0978}
+\affil{Department of Physics and Astronomy, Clemson University, Clemson, SC 29634-0978}
 
@@
 transitions from linear carbon chains to carbon rings are not accurately known.
-Their paper provided an existence proof that carbon can condense in O-rich gas.
+Their paper provided an {\em existence proof}
+that carbon can condense in O-rich gas.
 Its calculations showed that rare carbon-ring molecules were not prevented from
@@
 production of $\ctwo$\ in this manner must be calculated, they stated that at
-$T=5000$K the rate factor
+$T=5000$ K the rate factor
 $\langle \sigma v \rangle = k_{CO,C} = 8.6 \times 10^{-14}$ cm$^3$ s$^{-1}$
@@
 underestimates the abundances of linear carbon chains because much more $\ctwo$\
-is made earlier \citep{2010ApJ...713....1C} near T=5000K. Testing this
+is made earlier \citep{2010ApJ...713....1C} near $T = 5000$ K. Testing this
 competition is essential for understanding of dust condensation within
@@
 Because our goal is to study the chemistry, we can take a very simple physical
-model of the expansion; namely, temperature T=3800/(t/100d)=3.30x1010Ks/t(s),
-where t is the time elapsed since core collapse and nO=1010cm-3 and
-$n_C = 10^9$ cm$^{-3}$
-at the starting time t=t(6000K) for our chemical network at
-T=6000K. From our model choice for T(t) we get
+model of the expansion; namely, temperature
+$T = 3800 / (t({\rm s}) / 100 {\rm d}) =
+3.30 \times 10^{10} {\rm K} / t({\rm s})$,
+where t is the time elapsed since core collapse and $n_O = 10^{10}$ cm$^{-3}$
+and $n_C = 10^9$ cm$^{-3}$
+at the starting time $t = t(6000 {\rm K})$ for our chemical network at
+$T=6000$ K. From our model choice for $T(t)$ we get
 $t(6000K) = 5.47 \times 10^6$s. At
@@
 The rate for the second reaction is indeed
-much greater than that of the first reaction above T=3000K;
-but it becomes increasingly the smaller of the two below T=2500K.
+much greater than that of the first reaction above $T=3000$ K;
+but it becomes increasingly the smaller of the two below $T=2500$ K.
 We include the thermal inverse reaction of every reaction,
@@
 such matter will attempt to associate C and O into CO molecules, with rate
-coefficient $k_{CO}$=3.3x10-17cm3s-1 \citep{1990ApJ...358..262L}.
+coefficient $k_{CO} = 3.3 \times 10^{-17}$ cm$^3$ s$^{-1}$
+\citep{1990ApJ...358..262L}.
 The reaction \cotoco\ is one of the crucial reactions of chemical
@@
 creation of a photon during the collision; nonetheless, the huge product
-nCnO in the He-exhausted core ensures steady growth for the CO abundance
+$n_C n_O$ in the He-exhausted core ensures steady growth for the CO abundance
 until it is reversed by radioactive dissociation.
@@
 \end{equation}
-at $t = t_{max}$.
+at $t = t_{max}$.  ({\bf WHAT IS C(g)?})
 The maximum abundance reached by CO is in cgs units
@@
 which is the form integrated by our network of coupled reactions.
-The number density n is needed for the rate n(cm-3)$k_{CO}$(cm3s-1).
+The number density $n$ is needed for the rate
+$n({\rm cm}^{-3}) k_{CO}({\rm cm}^3{\rm s}^{-1})$.
 In our numerical example we take $n_O = 10^{10}$ cm$^{-3}$ and
-$n_C = 10^9$ cm$^{-3}$ at t(6000K) as starting conditions for the
+$n_C = 10^9$ cm$^{-3}$ at $t(6000 {\rm K})$ as starting conditions for the
 chemical network. Subsequent values are $n = 1.1 \times 10^{10}$ cm$^{-3}$
-$[t(6000)/t]^3$, where the expansion factor reduces the initial number
+$[t(6000 {\rm K})/t]^3$, where the expansion factor reduces the initial number
 density appropriately. Expansion factors are also in Table 1. Then
@@
 The radioactive lifetime $\tau_e$ is taken to be
-$\tau_e = 10^5\ {\rm s} \exp( ( t -10^6{\rm s}) / 111 {\rm d} )$,
+$\tau_e ({\rm s}) = 10^5 \exp( ( t -10^6{\rm s}) / 111 {\rm d} )$,
 but the thermal photodissociation lifetime $\tau_\gamma$
@@
 and from the number densities $n_C$ and $n_O$ after
-their initial values at T=6000K have been reduced by the expansion factor
-(t/t(6000K))-3. Tight agreement for $T > 3500$ K is immediately evident,
+their initial values at $T=6000$ K have been reduced by the expansion factor
+$(t/t(6000 {\rm K}))^{-3}$.
+Tight agreement for $T > 3500$ K is immediately evident,
 demonstrating that for $T > 3500$ K the abundance of CO is almost exactly in
-thermal equilibrium. Below 3500K the abundance of CO becomes much less than
+thermal equilibrium. Below 3500 K the abundance of CO becomes much less than
 the expectation $\ncogeq$ of thermal equilibrium because the dissociation of CO
 comes to be dominated by Compton electrons. The dashed vertical line at
-T=3500K marks the approximate boundary between these two mechanisms for CO
+$T=3500$ K marks the approximate boundary between these two mechanisms for CO
 dissociation. Notice carefully in Fig. \ref{fig:nco}
 that $n_{CO}$ grows slowly, not reaching
-its maximum until expansion has cooled to T=3500K.
+its maximum until expansion has cooled to $T=3500$ K.
 At maximum $n_{CO} = 1.5 \times 10^6$ cm$^{-3}$,
@@
 \citet{2009ApJ...703..642C}.
-Their results (e.g. Fig. 11) show $n_{CO}$ climbing quickly near 6000K to a large
+Their results (e.g. Fig. 11) show $n_{CO}$ climbing quickly near 6000 K
+to a large
 maximum number fraction near 0.1. That maximum would almost exhaust free
@@
 slow growth of $n_{CO}$ evident in Fig. \ref{fig:nco}. In that temperature range the
-production by \cotoco\ in equilibrium with the thermal radiation field,
+production by \cotoco\ is in equilibrium with the thermal radiation field,
 as Fig. \ref{fig:nco} implied. The destruction flow $n_{CO}/\tau_e$
 almost balances the
-creation flow below 3500K. The transition between destruction modes occurs
-near 3500K. It is no coincidence that the maximum of $n_{CO}$ occurs when
+creation flow below 3500 K. The transition between destruction modes occurs
+near 3500 K. It is no coincidence that the maximum of $n_{CO}$ occurs when
 Compton electrons begin to dominate CO dissociation, because $n_{CO}$ would
@@
 rate by thermal photons is much faster than that for CO because the binding
-energy of {\bf $\ctwo$\ CORRECT?} is
+energy of $\ctwo$\ is
 so much less than that for CO. This $n_{\ctwo}$
@@
 shows the abundances $Y_i$ of each species in our small network as a
-function of time t-t(6000K) after T=6000K. From Table \ref{tab:quantities},
-start time is $t(6000K) =5.47x10^6$ s. To display each $Y_i$ on a figure with
+function of time $t-t(6000 {\rm K})$ after $T=6000$ K.
+From Table \ref{tab:quantities},
+start time is $t(6000K) =5.47 \times 10^6$ s.
+To display each $Y_i$ on a figure with
 reasonable ordinate resolution, we have scaled each $\cenn$\ by the factor
@@
 state; (5) the ringed carbon $\ceightr$\ has similar abundance shape vs. time,
-but notice that it is actually much more abundant than C7-8 because it
-accumulates from isomeric transitions of $\ceight$\ and unlike $\cenn$\ does not
+but notice that it is actually much more abundant than $\cseven$ and
+$\ceight$ because it accumulates from isomeric transitions of $\ceight$\
+and unlike $\cenn$\ does not
 suffer from fast oxidation \citep{1999Sci...283.1290C}. Each of these
@@
 Figure \ref{fig:cn} shows the shape of $\cenn$\ vs. $n$ for $\cthree$\ to
-$\ceight$\ at two different temperatures near 2000K. As temperature declines,
+$\ceight$\ at two different temperatures near 2000 K. As temperature declines,
 the curve flattens because photoejection from $\cenn$\ by thermal photons
@@
 Table \ref{tab:flows} lists our computed reaction flows both in and out of
-$\csix$\ at T = 2031K and T = 1802K. The reactions are specified there in the
+$\csix$\ at $T = 2031$ K and $T = 1802$ K.
+The reactions are specified there in the
 compact notation target(in,out)residual. Fig. \ref{fig:cn} and
@@
 Note that the abundances of $\ceight$\ are very small:
-$Y(\ceight)= 10^{-36}$ at T = 1802K. The isomeric transition from linear to
+$Y(\ceight)= 10^{-36}$ at $T = 1802$ K.
+The isomeric transition from linear to
 ringed $\ceight$, for which we estimate a lifetime $\tau = 10$ s,
@@
 \cfivectocsix,
-which is very fast ($k = 3 \times 10^{-10} cm^3 s^{-1}$)
+which is very fast ($k = 3 \times 10^{-10} {\rm cm}^3 {\rm s}^{-1}$)
 because vibrational excitation of $\csix$
@@
 at $T = 2031$ K and $2 \times 10^4$ at $T = 1802$ K.
-Photodissociation dominates. The smaller value for that ratio at T=1802K
-occurs because oxidation maintains its effectiveness as T drops but
+Photodissociation dominates. The smaller value for that ratio at $T=1802$ K
+occurs because oxidation maintains its effectiveness as $T$ drops but
 thermal disruption does not, being much more temperature sensitive.
 For this reason the abundance pattern is flatter and $\csix$\ is approximately
-3000 times more abundant at T=1802K than at T=2031K.
+3000 times more abundant at $T=1802$ K than at $T=2031$ K.
 It is for that reason that destruction flows in Table \ref{tab:flows}
@@
 larger at the smaller temperature.
-The steady state shifts to new ratios as T falls.
+The steady state shifts to new ratios as $T$ falls.
 Thirdly, calculation of the rates will be illustrated for sake of clarity
@@
 so the flow per atom per
-second (e.g., Eq. \ref{eq:dycodt}) is $dY/dt= Y(\csix)Y(O)n(2031K)k(C6O)$.
-Expansion from T=6000K to T=2031K has diluted the total number
-density n to 1.1x1010cm-3 (2031K/6000K)3= 4.27x108cm-3.
-The fast oxidation reaction rate is  k(C6O)=3x10-10cm3s-1.
-Gathering factors yields approximately 4x10-35 n-1s-1,
+second (e.g., Eq. \ref{eq:dycodt}) is
+$dY/dt= Y(\csix)Y(O)n(2031K)k(\csix + {\rm O})$.
+Expansion from $T=6000$ K to $T=2031$ K has diluted the total number
+density $n$ to $1.1 \times 10^{10}{\rm cm}^{-3}
+(2031 {\rm K}/6000 {\rm K})^3 = 4.27 \times 10^8{\rm cm}^{-3}$.
+The fast oxidation reaction rate is
+$k(\csix + {\rm O}) = 3 \times 10^{-10} {\rm cm}^3{\rm s}^{-1}$.
+Gathering factors yields approximately $4 \times 10^{-35} {atoms}^{-1}
+{\rm s}^{-1}$ ({\bf UNITS??????}),
 in good approximation to the Table \ref{tab:flows}
@@
 Our calculations have shown clearly that producing $\ctwo$\ molecules near
-5000K via the CO + C reaction \citep{2009ApJ...703..642C} is not a viable
+5000 K via the CO + C reaction \citep{2009ApJ...703..642C} is not a viable
 prospect for condensation of carbon dust via linear carbon chains.
@@
 \twoctoctwo.
-Furthermore, the abundance of $\ctwo$\ is very small near 5000K
+Furthermore, the abundance of $\ctwo$\ is very small near 5000 K
 (Fig. \ref{fig:ncoc2}),
 primarily because its thermal dissociation rate is much too fast for
-it to have significant abundance at that high T.
-What little $\ctwo$\ is made at 5000K is immediately dissociated by
+it to have significant abundance at that high $T$.
+What little $\ctwo$\ is made at 5000 K is immediately dissociated by
 thermal photos. Therefore its small steady-state abundance is inadequate
@@
 
-\item Instead of growing large CO abundance near Y(CO)=0.1 at T=5500K
+\item Instead of growing large CO abundance near $Y(CO)=0.1$ at $T=5500$ K
 as in Fig. 11 of \citet{2009ApJ...703..642C}, we find that $Y(CO)$
-builds to a maximum of only 10-3, which it achieves only slowly
-(Fig. \ref{fig:ncoc2}), reaching that maximum only at T=3500K rather
-than 5500K.
+builds to a maximum of only $10^{-3}$, which it achieves only slowly
+(Fig. \ref{fig:ncoc2}), reaching that maximum only at $T=3500$ K rather
+than 5500 K.
 
@@
 and omitted the $\tau_\gamma$ destruction terms.
-Figure 6 displays the result.
+Figure \ref{fig:no_gamma} displays the result.
 The rapid rise of $Y(CO)$ to $10^{-2}$ at high temperature is very similar to
@@
 Similarity also describes $Y(\ctwo)$,
-which grows quickly (Fig. 6) to 2x10-4 of Y(CO),
+which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y(CO)$,
 whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y(CO)$ to be
-only $10^{-8}$ at T=5500K and, considerably later,
+only $10^{-8}$ at $T=5500$ K and, considerably later,
 $Y(\ctwo)/Y(CO) = 10^{-7}$ at their maxima.
@@
 Those strive to balance, which if achieved establishes a steady state
-ratio $Y(CO)/Y(\ctwo) = 3.5 \times 10^4$. Fig. 6 and their Fig. 11 do show
+ratio $Y(CO)/Y(\ctwo) = 3.5 \times 10^4$. Fig. \ref{fig:no_gamma}
+and their Fig. 11 do show
 approximately that value, but $Y(\ctwo)$ declines faster than $Y(CO)$
@@
 O / C = 10 whereas they used O / C = 3 for the zone of their SNII model.
-The temperature profiles also differ, we using T=3800/(t/100d) and they
-T=18500/(t/100d)1.8.
-We believe that their T is too hot owing to omission of CO cooling
+The temperature profiles also differ, we using $T=3800 {\rm K}/(t/100d)$
+and they $T=18500 {\rm K}/(t/100d)^{1.8}$.
+We believe that their $T$ is too hot owing to omission of CO cooling
 (\citealp{1996ApJ...471..480L}, Fig. 5),
 which we tried to accommodate roughly by
-the choice T=3800K at t=100d, which is about 50\% of the temperature
+the choice $T=3800$ K at $t=100 {\rm d}$,
+which is about 50\% of the temperature
 within published models which do omit CO cooling. And owing to the
-factor $t^{-1.8}$, their T falls through a specified temperature drop
-(say, 5000K to 3000K) more quickly than does our parameterization.
-Nonetheless, any T profile declines though 5000K and reaches 3000K
+factor $t^{-1.8}$, their $T$ falls through a specified temperature drop
+(say, 5000 K to 3000 K) more quickly than does our parameterization.
+Nonetheless, any $T$ profile declines though 5000 K and reaches 3000 K
 somewhat later, so basically similar abundance results are expected.
@@
 Such detailed differences are small in comparison with inclusion of
-thermal photodissociation. The similarity of Fig. 6 to their Fig.11,
+thermal photodissociation. The similarity of Fig. \ref{fig:no_gamma}
+to their Fig.11,
 and the huge differences of these figures from those of our network
@@
 
-We are grateful.
+T. Y. gratefully acknowledges the support of
+a NASA Earth and Space Science Fellowship.
+This work was also supported by NASA grant NNX10AH78G.
 
@@
 \begin{figure}
-\epsscale{.80}
-%\plotone{f1.eps}
+\plotone{figures/ncoeq.pdf}
 \caption{
@@
 \begin{figure}
-\epsscale{.80}
-%\plotone{f1.eps}
+\plotone{figures/co_flows.pdf}
 \caption{
@@
 and destruction and the transition region near 3500K between the two modes
-of destruction of CO. The destruction flow $n_{CO}$nC$k_{CO}$+C is only $3.27 \times
+of destruction of CO.
+The destruction flow $n_{CO} n_C k_{CO+C}$ is only $3.27 \times
 10^{-16}$ atom$^{-1}$s$^{-1}$, too small to be visible in Fig. \ref{fig:flows}. 
@@
 \begin{figure}
-\epsscale{.80}
-%\plotone{f1.eps}
+\plotone{figures/nco.pdf}
 \caption{
@@
 \begin{figure}
-\epsscale{.80}
-%\plotone{f1.eps}
+\plotone{figures/Yi.pdf}
 \caption{
@@
 \begin{figure}
-\epsscale{.80}
-%\plotone{f1.eps}
+\plotone{figures/cn.pdf}
 \caption{
@@
 \label{fig:cn}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\plotone{figures/no_gamma.pdf}
+\caption{
+Abundances for network containing only C, O, CO, $\ctwo$, and $\cthree$
+when photodissociation of molecules is omitted. Rapid rise of $Y(CO)$
+to $10^{-2}$ near 5500 K and the ratio $Y(CO)/Y(CO)$ near $10^4$ are
+similar to Fig. 11 of \citet{2009ApJ...703..642C}.
+}
+\label{fig:no_gamma}
 \end{figure}

### 2013-01-17 doc/ms.tex
Add figures.  Add Don's edits.

@@
 model of the expansion; namely, temperature
-$T = 3800 / (t({\rm s}) / 100 {\rm d}) =
+$T = 3800 K / (t / 100 {\rm d}) =
 3.30 \times 10^{10} {\rm K} / t({\rm s})$,
@@
 linear $\cenn$
-whereas its C capture rates are fast. We take ringed $\ceightr$ to be
-indestructible, simply integrating their rate of production. Our strategy is
+whereas their C capture rates are fast. We take ringed $\ceightr$ to be
+indestructible, simply integrating their rate of production.
+We cannot allege that $\ceight$\ is the key isomerizing chain, nor that
+$\tau_8^r = 10$ s is its lifetime, but those assumptions are adequate for
+comparing models for formation for $\ctwo$.
+Our strategy is
 to compute the number $\ceightr$ remaining after expansion from two differing
@@
 We also include in our network dissociation of CO by Compton electrons.
-CO is the only molecule for which thermal photodissociation is the dominant
+CO is the only molecule for which electron dissociation can be the dominant
 destruction mechanism. For that rate we use
@@
 has discussed the shape of the function
-$n_{CO}$(t). His Eq.(1) approximates the growth of $n_{CO}$ by its leading terms:
+$n_{CO}$(t). His Eq.(1), which is valid at constant density,
+approximates the growth of $n_{CO}$ by its leading terms:
 \begin{equation}
-\frac{dn_{CO}}{dt} = n_{C(g)} n_O k_{CO} - \frac{n_{CO}}{\tau_{CO}} = 0
+\frac{dn_{CO}}{dt} = n_C n_O k_{CO} - \frac{n_{CO}}{\tau_{CO}} = 0
 \label{eq:dncodt}
 \end{equation}
-at $t = t_{max}$.  ({\bf WHAT IS C(g)?})
+at $t = t_{max}$.
 The maximum abundance reached by CO is in cgs units
@@
 against dissociation. If $\tau_{CO}$ is taken to be $\tau_\gamma$ because
-the dissociation of CO is dominated by thermal photons,
+the dissociation of CO is dominated for $T > 3500$ K by thermal photons,
 one obtains the expression for the abundance $n_{CO}^{\gamma eq}$ in thermal
@@
 \end{equation}
+which is valid during expansions.
 
@@
 compares our network calculation of the abundance of CO molecules
-with the expectation of Eq. (\ref{eq:comax}) when $\tau_\gamma$
-dominates the destruction of CO.
+with the expectation of Eq. (\ref{eq:comax}) with $\tau_{CO} = \tau_\gamma$
+dominating the destruction of CO.
 Solid points display the equilibrium product $\ncogeq$ calculated from the
@@
 $(t/t(6000 {\rm K}))^{-3}$.
-Tight agreement for $T > 3500$ K is immediately evident,
-demonstrating that for $T > 3500$ K the abundance of CO is almost exactly in
-thermal equilibrium. Below 3500 K the abundance of CO becomes much less than
+Tight agreement for $T > 4000$ K is immediately evident,
+demonstrating that for $T > 4000$ K the abundance of CO is almost exactly in
+thermal equilibrium. Below 3500 K the abundance of CO becomes much smaller than
 the expectation $\ncogeq$ of thermal equilibrium because the dissociation of CO
@@
 dissociation. Notice carefully in Fig. \ref{fig:nco}
-that $n_{CO}$ grows slowly, not reaching
-its maximum until expansion has cooled to $T=3500$ K.
-At maximum $n_{CO} = 1.5 \times 10^6$ cm$^{-3}$,
-corresponding to $Y(CO) = 0.7 \times 10^{-3}$. The growth of $n_{CO}$
+that $n_{CO}$ grows slowly as $T$ falls, not reaching
+its final maximum until expansion has cooled to $T=3500$ K.
+Although it is obvious that equilbrium CO increases as $T$ falls,
+assuming that to occur begs the question of achieving equilibrium.
+Our kinetic results demonstrate that CO does quickly achieve its
+equilibrium abundance above $T = 4000$ K, and Eq. (\ref{eq:dycodt})
+shows that equilibrium to increase as $\tau_\gamma$ lengthens.
+At its final maximum $n_{CO} = 1.5 \times 10^6$ cm$^{-3}$,
+corresponding to $Y(CO) = 0.7 \times 10^{-3}$. The slow growth of $n_{CO}$
 shown in Fig. \ref{fig:nco} differs markedly from the results of
@@
 near steady state in that the production of CO is almost balanced by the
-two flows destroying CO. The destruction flow $n_{CO}/\tau_\gamma$
+two flows destroying CO. The destruction flow $Y_{CO}/\tau_\gamma$
 almost balances the
@@
 Figure \ref{fig:ncoc2} displays the number density $n_{\ctwo}$ along with
-that of $n_{CO}$. At its maximum $n_{\ctwo} =0.1$ cm$^{-3}$ is only about
+that of $n_{CO}$.
+Our examination of flows into $\ctwo$\ shows that the reaction
+\coctoctwo\ competes with the reaction \twoctoctwo\ only in the
+range 3400 K $< T < 3900$ K, but falls steeply for greater or lesser
+temperature.  At higher $T$ the abundance of CO is too small to create
+$\ctwo$\ in this way, and at smaller $T$ the cross section for \coctoctwo\
+declines too precipitously.  \citet{2009ApJ...703..642C} missed that
+because their calculated abundance of CO was much too large.
+At its maximum $n_{\ctwo} =0.1$ cm$^{-3}$ is only about
 $10^{-7}$ of $n_{CO}$. The reason $\ctwo$\ is so rare is that its dissociation
@@
 energy of $\ctwo$\ is
-so much less than that for CO. This $n_{\ctwo}$
+so much less than that for CO.
+The smaller value of $\tau_\gamma$ causes the steady stat with thermal
+radiation for $\ctwo$, as in Eq. (\ref{eq:dycodt}), to be much smaller that for
+CO, so $n_{\ctwo}$ grows much more slowly than $n_{CO}$.  The Compton
+electron lifetime $\tau_e$ never plays a role for $\ctwo$, but the
+lifetime against oxidation becomes faster that $\tau_\gamma$ when $T$
+falls below 3500 K.  That transition establishes the maximum in
+Fig. \ref{fig:ncoc2}.
+This $n_{\ctwo}$
 maximum differs greatly
@@
 maximum atom fraction of $n_{\ctwo}$ to be near $10^{-5}$,
-equal to about $10^5$ cm$^{-3}$, almost 1\% of $n_{CO}$ at that time.
+equal to about $10^5$ cm$^{-3}$, almost 1\% of their $n_{CO}$ at that time.
 And their maximum for $\ctwo$\ occurs near 7000 K, far too hot for $\ctwo$\ to
-be abundant in the face of rapid dissociation. The huge differences between
+be abundant in the face of rapid photodissociation. The huge differences between
 these two computations require an explanation. We find it likely that
@@
 (2) maxima in CO and $\ctwo$\ occur at almost exactly the same time
-$t-t(6000K)= 4 \times 10^6$ s, as in Fig. \ref{fig:ncoc2};
+$t-t(6000K)= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
 (3) $\cthree$\ has very small abundance, about $3 \times 10^{-8}$ of $\ctwo$
@@
 
+One sees from Fig. \ref{fig:cn} that the \coctoctwo\ reaction plays no
+role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
+$t - t(6000 {\rm K}) > 1.5 \times 10^7$ s, corresponding to $T < 2000$ K,
+despite $\ctwo$\ and $\cthree$\ rising at much earlier times.
+Whatsoever $\ctwo$\ is made earlier plays no role in $\ceightr$\ production
+because there ejection of C atoms from $\cenn$\ at higher $T$ prevents the
+flow to $\ceight$.  Only at $T < 2000$ K do those photodissociation reactions
+become so slow that $\ceight$\ can grow, which it does from the $\ctwo$\
+recently
+formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:cn} also shows
+that $Y(\ceightr)$
+grows quickly to $10^{-16}$.  Since available C is $Y_C = 0.1$,
+the ratio gives $10^{-15}$ C/ring.  This is enough to grow very large
+graphite.
+
 Figure \ref{fig:cn} shows the shape of $\cenn$\ vs. $n$ for $\cthree$\ to
@@
 (or phonons) weakens. These abundance ratios are almost in a steady state,
-but that steady state changes slightly as T falls. These patterns show
+but that steady state changes slightly as $T$ falls. These patterns show
 almost equal values for $Y(\cthree)$ because that curve is relatively flat
@@
 ringed $\ceight$, for which we estimate a lifetime $\tau = 10$ s,
-provides the nucleations for graphite growth. Figure \ref{fig:ncoc2} showed
-that $Y(\ceightr)$
+provides the nucleations for graphite growth.
 
@@
 $k(\csix + {\rm O}) = 3 \times 10^{-10} {\rm cm}^3{\rm s}^{-1}$.
-Gathering factors yields approximately $4 \times 10^{-35} {atoms}^{-1}
-{\rm s}^{-1}$ ({\bf UNITS??????}),
+Gathering factors yields approximately $4 \times 10^{-35}$ per atom
+per second
 in good approximation to the Table \ref{tab:flows}
-flow entry $3.61 \times 10^{-35} n^{-1}s^{-1}$.
+flow entry $3.61 \times 10^{-35}$ per atom per second.
 
@@
 
-\section{Contrast with \citet{2009ApJ...703..642C}}
+\section{Contrast with \citet{2009ApJ...703..642C,2010ApJ...713....1C}}
 
@@
 \citet{1999Sci...283.1290C,2001ApJ...562..480C}
-and those of \citet{2009ApJ...703..642C}
+and those of \citet{2009ApJ...703..642C,2010ApJ...713....1C}
 seem to be characterized by these differences:
@@
 \end{enumerate}
-We reasoned that these big differences could be understood if
+We reason that these big differences can be understood if
 \citet{2009ApJ...703..642C} had inadvertantly omitted the thermal
@@
 Fig. 11 of \citet{2009ApJ...703..642C}.
-Similarity also describes $Y(\ctwo)$,
+Similar also is $Y(\ctwo)$,
 which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y(CO)$,
@@
 
-With photodissociation turned off, the destruction of $\ctwo$\ is primarily
+With photodissociation turned off, the destruction of $\ctwo$\ occurs primarily
 by oxidation, \ctowotococ, whereas production of $\ctwo$ is by
 \coctoctwo, the reaction we study in this work.
-Those strive to balance, which if achieved establishes a steady state
+Those reactions strive to balance, which if achieved would
+establish a steady state
 ratio $Y(CO)/Y(\ctwo) = 3.5 \times 10^4$. Fig. \ref{fig:no_gamma}
@@
 
-We could not expect detailed agreement, even if our hypothesis for the
+We could not expect detailed agreement with \citet{2009ApJ...703..642C},
+even if our hypothesis for the
 cause of the discrepancy is correct. Our calculation used
-O / C = 10 whereas they used O / C = 3 for the zone of their SNII model.
+O/C = 10 whereas they used O/C = 3 for the zone of their SNII model.
 The temperature profiles also differ, we using $T=3800 {\rm K}/(t/100d)$
@@
 the choice $T=3800$ K at $t=100 {\rm d}$,
-which is about 50\% of the temperature
-within published models which do omit CO cooling. And owing to the
+which is about 50\% of the temperatures
+published within models that do omit CO cooling. And owing to the
 factor $t^{-1.8}$, their $T$ falls through a specified temperature drop
@@
 Such detailed differences are small in comparison with inclusion of
-thermal photodissociation. The similarity of Fig. \ref{fig:no_gamma}
-to their Fig.11,
+thermal photodissociation. The similarity of our Fig. \ref{fig:no_gamma}
+to Fig. 11 of \citet{2009ApJ...703..642C},
 and the huge differences of these figures from those of our network
@@
 when photodissociation of molecules is omitted. Rapid rise of $Y(CO)$
-to $10^{-2}$ near 5500 K and the ratio $Y(CO)/Y(CO)$ near $10^4$ are
+to $10^{-2}$ near 5500 K and the ratio $Y(CO)/Y(\ctwo)$ near $10^4$ are
 similar to Fig. 11 of \citet{2009ApJ...703..642C}.
@@
 \begin{center}
-\caption{Reaction Flows involving $\csix$\ at two temperatures.  {\bf UNITS
-ON FLOWS RIGHT?}}
+\caption{Reaction Flows involving $\csix$\ at two temperatures.}
 \label{tab:flows}

### 2013-01-17 doc/ms.tex
Fix keywords.  Remove comments.

@@
-%%
-%% Beginning of file 'sample.tex'
-%%
-%% Modified 2005 December 5
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v5.x LaTeX 2e macros.
-
-%% The first piece of markup in an AASTeX v5.x document
-%% is the \documentclass command. LaTeX will ignore
-%% any data that comes before this command.
-
-%% The command below calls the preprint style
-%% which will produce a one-column, single-spaced document.
-%% Examples of commands for other substyles follow. Use
-%% whichever is most appropriate for your purposes.
-%%
-%%\documentclass[12pt,preprint]{aastex}
-
-%% manuscript produces a one-column, double-spaced document:
-
 \documentclass[manuscript]{aastex}
-
-%% preprint2 produces a double-column, single-spaced document:
-
-%% \documentclass[preprint2]{aastex}
-
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
-
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-%% If you are submitting to a journal that translates manuscripts
-%% into SGML, you need to follow certain guidelines when preparing
-%% your macros. See the AASTeX v5.x Author Guide
-%% for information.
 
@@
 
-%% You can insert a short comment on the title page using the command below.
-
-%\slugcomment{Not to appear in Nonlearned J., 45.}
-
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-%% The left head contains a list of authors,
-%% usually a maximum of three (otherwise use et al.).  The right
-%% head is a modified title of up to roughly 44 characters.
-%% Running heads will not print in the manuscript style.
-
 \shorttitle{Formation of $\cenn$ Molecules}
@@
 
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
-
 \begin{document}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire.
 
@@
 
-%% Use \author, \affil, and the \and command to format
-%% author and affiliation information.
-%% Note that \email has replaced the old \authoremail command
-%% from AASTeX v4.0. You can use \email to mark an email address
-%% anywhere in the paper, not just in the front matter.
-%% As in the title, use \\ to force line breaks.
-
 \author{Tianhong Yu, Bradley S. Meyer, and Donald D. Clayton}
 \affil{Department of Physics and Astronomy, Clemson University, Clemson, SC 29634-0978}
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
 
@@
 
-%% Keywords should appear after the \end{abstract} command. The uncommented
-%% example has been keyed in ApJ style. See the instructions to authors
-%% for the journal to which you are submitting your paper to determine
-%% what keyword punctuation is appropriate.
-
-\keywords{atomic processes, ISM: abundances, ISM: general, meteorites, meteors, meteoroids, supernovae: general, supernovae: individual: SN 1987A}
+\keywords{atomic processes --- ISM: abundances --- ISM: general --- meteorites, meteors, meteoroids --- supernovae: general --- supernovae: individual (SN 1987A)}
 
@@
 \end{document}
-
-%%
-%% End of file `sample.tex'.

### 2013-01-23 doc/ms.tex
Update figures.
Update black and white figure for no_gamma.pdf. Update text. Update idl files.

@@
 as they had done,
-and omitted the $\tau_\gamma$ destruction terms.
+and omitted the $\tau_\gamma$ destruction terms and the oxidation of $\cthree$.
 Figure \ref{fig:no_gamma} displays the result.
-The rapid rise of $Y(CO)$ to $10^{-2}$ at high temperature is very similar to
-Fig. 11 of \citet{2009ApJ...703..642C}.
+The rapid rise of $Y(CO)$ to about $10^{-2}$ at high temperature is very 
+similar to Fig. 11 of \citet{2009ApJ...703..642C}.
 Similar also is $Y(\ctwo)$,

### 2013-01-23 doc/submit/ms.tex
Add submit/. The eps files may be useful in the future.

--- 2013-01-23 doc/ms.tex
@@
 \begin{figure}
-\plotone{figures/ncoeq.pdf}
+\plotone{ncoeq}
 \caption{
@@
 \begin{figure}
-\plotone{figures/co_flows.pdf}
+\plotone{co_flows}
 \caption{
@@
 \begin{figure}
-\plotone{figures/nco.pdf}
+\plotone{nco}
 \caption{
@@
 \begin{figure}
-\plotone{figures/Yi.pdf}
+\plotone{Yi}
 \caption{
@@
 \begin{figure}
-\plotone{figures/cn.pdf}
+\plotone{cn}
 \caption{
@@
 \begin{figure}
-\plotone{figures/no_gamma.pdf}
+\plotone{no_gamma}
 \caption{
@@
 
-\bibliographystyle{apj}
-\bibliography{clemson}
+\begin{thebibliography}{14}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Cherchneff} \& {Dwek}(2009)}]{2009ApJ...703..642C}
+{Cherchneff}, I. \& {Dwek}, E. 2009, \apj, 703, 642
+
+\bibitem[{{Cherchneff} \& {Dwek}(2010)}]{2010ApJ...713....1C}
+---. 2010, \apj, 713, 1
+
+\bibitem[{{Clayton}(2011)}]{2011NewAR..55..155C}
+{Clayton}, D.~D. 2011, \nar, 55, 155
+
+\bibitem[{{Clayton}(2013)}]{2013ApJ...762....5C}
+---. 2013, \apj, 762, 5
+
+\bibitem[{{Clayton} {et~al.}(2001){Clayton}, {Deneault}, \&
+  {Meyer}}]{2001ApJ...562..480C}
+{Clayton}, D.~D., {Deneault}, E.~A.-N., \& {Meyer}, B.~S. 2001, \apj, 562, 480
+
+\bibitem[{{Clayton} {et~al.}(1999){Clayton}, {Liu}, \&
+  {Dalgarno}}]{1999Sci...283.1290C}
+{Clayton}, D.~D., {Liu}, W., \& {Dalgarno}, A. 1999, Science, 283, 1290
+
+\bibitem[{{Clayton} \& {The}(1991)}]{1991ApJ...375..221C}
+{Clayton}, D.~D. \& {The}, L.-S. 1991, \apj, 375, 221
+
+\bibitem[{{Deneault} {et~al.}(2003){Deneault}, {Clayton}, \&
+  {Heger}}]{2003ApJ...594..312D}
+{Deneault}, E.~A.-N., {Clayton}, D.~D., \& {Heger}, A. 2003, \apj, 594, 312
+
+\bibitem[{{Deneault} {et~al.}(2006){Deneault}, {Clayton}, \&
+  {Meyer}}]{2006ApJ...638..234D}
+{Deneault}, E.~A.-N., {Clayton}, D.~D., \& {Meyer}, B.~S. 2006, \apj, 638, 234
+
+\bibitem[{{Klots}(1968)}]{1968...Klots}
+{Klots}, C.~E. 1968, in Fundamental Processes in Radiation Chemistry, ed.
+  P.~{Ausloos} (New York: Interscience)
+
+\bibitem[{{Lepp} {et~al.}(1990){Lepp}, {Dalgarno}, \&
+  {McCray}}]{1990ApJ...358..262L}
+{Lepp}, S., {Dalgarno}, A., \& {McCray}, R. 1990, \apj, 358, 262
+
+\bibitem[{{Liu} \& {Dalgarno}(1996)}]{1996ApJ...471..480L}
+{Liu}, W. \& {Dalgarno}, A. 1996, \apj, 471, 480
+
+\bibitem[{{Liu} \& {Victor}(1994)}]{1994ApJ...435..909L}
+{Liu}, W. \& {Victor}, G.~A. 1994, \apj, 435, 909
+
+\bibitem[{{Meyer} \& {Adams}(2007)}]{2007M&PSA..42.5215M}
+{Meyer}, B.~S. \& {Adams}, D.~C. 2007, 70th Annual Meteoritical Society
+  Meeting, held in August 13-17, 2007, Tucson, Arizona.~Meteoritics and
+  Planetary Science Supplement, Vol.~42, p.5215, 42, 5215
+
+\end{thebibliography}
 

### 2013-01-30 doc/submit/ms.tex
Update text.

@@
 This amount is equal to that formed during its last mean lifetime $\tau_{CO}$
-against dissociation. If $\tau_{CO}$ is taken to be $\tau_\gamma$ because
+against dissociation. Eq. (\ref{eq:comax}) is also highly accurate in
+circumstances where the time derivative in Eq. (\ref{eq:dncodt}) is but a
+small difference between much larger creation and destruction terms. Such
+balance is often set up as an abundance approaches it true maximum. 
+If $\tau_{CO}$ is taken to be $\tau_\gamma$ because
 the dissociation of CO is dominated for $T > 3500$ K by thermal photons,
@@
 demonstrating that for $T > 4000$ K the abundance of CO is almost exactly in
-thermal equilibrium. Below 3500 K the abundance of CO becomes much smaller than
+thermal equilibrium. Eq (\ref{eq:comax}) validly describes the black dots in
+Fig. \ref{fig:nco} because creation and destruction terms are very nearly
+balanced while T > 4000K.
+Below 3500 K the abundance of CO becomes much smaller than
 the expectation $\ncogeq$ of thermal equilibrium because the dissociation of CO
@@
 association flow above 4000K except for a tiny excess leading to the
-slow growth of $n_{CO}$ evident in Fig. \ref{fig:nco}. In that temperature range the
+slow growth of $n_{CO}$ evident in Fig. \ref{fig:nco}. In that temperature 
+range the
 production by \cotoco\ is in equilibrium with the thermal radiation field,
-as Fig. \ref{fig:nco} implied. The destruction flow $n_{CO}/\tau_e$
-almost balances the
+as Fig. \ref{fig:nco} implied. The decline of the flow creating CO occurs owing
+to expansion. The destruction flow $n_{CO}/\tau_e$ almost balances the
 creation flow below 3500 K. The transition between destruction modes occurs
@@
 continue growing as long as thermal photons dominate CO dissociation. 
+Fig. \ref{fig:flows} also shows the destructive flow by inelastic electrons
+to slightly exceed the production flow for $T < 3500$ K. That modest difference
+causes CO to decline following it maximum.
 
@@
 at $T = 2031$ K and $2 \times 10^4$ at $T = 1802$ K.
-Photodissociation dominates. The smaller value for that ratio at $T=1802$ K
+Dissociation by thermally excited vibrations dominates oxidation. What we here
+label ($\gamma,{\rm C}$) is actually radiationless. Note that oxidation of
+$\cenn$ molecules is not faster than C-ejection reactions. This unusual
+situation occurs because the C-capture reactions proceeded by exciting 
+vibrations of the $\csix$ molecule. That residual vibrational energy makes
+capture reactions fast rather than slow, but also makes the inverse C-ejection
+reactions caused by thermally excited vibrations to be much faster. Detailed
+balance gets the ratio right. The smaller value for that ratio at $T=1802$ K
 occurs because oxidation maintains its effectiveness as $T$ drops but
@@
 One see in Fig. \ref{fig:nco} that $n_{CO}$max occurs near 3500K,
-which occurs near $10^7$ s (see Table \ref{tab:quantities})}. 
+which occurs near $10^7$ s (see Table \ref{tab:quantities}).} 
 \label{fig:nco}

### 2013-01-30 doc/submit/ms.tex
Update text.

@@
 small difference between much larger creation and destruction terms. Such
-balance is often set up as an abundance approaches it true maximum. 
+balance is often set up as an abundance approaches its true maximum. 
 If $\tau_{CO}$ is taken to be $\tau_\gamma$ because
@@
 demonstrating that for $T > 4000$ K the abundance of CO is almost exactly in
-thermal equilibrium. Eq (\ref{eq:comax}) validly describes the black dots in
+thermal equilibrium. Eq. (\ref{eq:comax}) validly describes the black dots in
 Fig. \ref{fig:nco} because creation and destruction terms are very nearly
-balanced while T > 4000K.
+balanced while $T > 4000$ K.
 Below 3500 K the abundance of CO becomes much smaller than
@@
 $\cenn$ molecules is not faster than C-ejection reactions. This unusual
-situation occurs because the C-capture reactions proceeded by exciting 
+situation occurs because the C-capture reactions proceed by exciting 
 vibrations of the $\csix$ molecule. That residual vibrational energy makes

### 2013-01-30 doc/submit/ms.tex
Fix typoes.

@@
 so much less than that for CO.
-The smaller value of $\tau_\gamma$ causes the steady stat with thermal
-radiation for $\ctwo$, as in Eq. (\ref{eq:dycodt}), to be much smaller that for
-CO, so $n_{\ctwo}$ grows much more slowly than $n_{CO}$.  The Compton
+The smaller value of $\tau_\gamma$ causes the steady state with thermal
+radiation for $\ctwo$, as in Eq. (\ref{eq:dycodt}), to be much smaller than 
+that for CO, so $n_{\ctwo}$ grows much more slowly than $n_{CO}$.  The Compton
 electron lifetime $\tau_e$ never plays a role for $\ctwo$, but the
@@
 
-One sees from Fig. \ref{fig:cn} that the \coctoctwo\ reaction plays no
+One sees from Fig. \ref{fig:Yi} that the \coctoctwo\ reaction plays no
 role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
@@
 recently
-formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:cn} also shows
+formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:Yi} also shows
 that $Y(\ceightr)$

### 2013-01-30 data/make_co_data.sh
Update plot C2 flows.

@@ -1,5 +1,4 @@
 ../../../libnucnet/create_nuc_xml_from_text ../data/co_nuc.txt ../data/co_nuc.xml 
 ../../../libnucnet/create_reac_xml_from_text ../data/co_reac.txt ../data/co_reac.xml 
 ../../../libnucnet/merge_net ../data/co_nuc.xml ../data/co_reac.xml ../data/co_net.xml 
-../../../libnucnet/merge_full ../data/co_net.xml ../data/co_zone.xml ../data/co_full.xml
 

### 2013-01-30 make_figure_data.sh

@@ -4,7 +4,10 @@ FILE=out
 
 print_properties ${FILE} time t9 rho > idl/prop
 print_mass_fractions_in_zones ${FILE} n h1 h2 he2 li3 be4 b5 c6 n7 o8C o8R > idl/mass_fractions
-print_carbon_flows ${FILE} '' "[(product = 'he2' and product = 'gamma') or (product = 'he2' and product = 'n')]" > idl/c2_flows
+print_carbon_flows ${FILE} '' "[product = 'he2' and product = 'gamma']" > idl/c2_flows1
+print_carbon_flows ${FILE} '' "[product = 'he2' and product = 'n']" > idl/c2_flows2
+print_carbon_flows ${FILE} '' "[reactant = 'he2' and reactant = 'gamma']" > idl/c2_flows3
+print_carbon_flows ${FILE} '' "[reactant = 'he2' and reactant = 'n']" > idl/c2_flows4
 print_carbon_flows ${FILE} '' "[(product = 'h2' and product = 'gamma') or (reactant = 'h2' and reactant = 'gamma') or (reactant = 'h2' and reactant = 'electron')]" > idl/co_flows
 
 compute_carbon_flows ${FILE} '' > flows

### 2013-03-12 doc/submit/ms.tex
Update for the referees review.

@@
 
-The problem historically of condensing carbon SUNOCONs in the interiors of
-expanding Type II supernovae is that most of the synthesized carbon is bathed
-in more abundant oxygen and was long presumed to be oxidized by it. This
-changed when \citet{1999Sci...283.1290C} introduced a kinetic theory by
-which carbon can condense thermally in gas having more abundant oxygen.
-That theory is noteworthy in having every chemical reaction from the initial
-O $>$ C gas to macroscopic graphite included in a kinetic network, even though
-most of the cross sections for those reactions and the rates of isomeric
-transitions from linear carbon chains to carbon rings are not accurately known.
-Their paper provided an {\em existence proof}
-that carbon can condense in O-rich gas.
-Its calculations showed that rare carbon-ring molecules were not prevented from
-formation despite rapid oxidation of their molecular precursors, although
-oxidation does greatly reduce the abundance of those $\cenn$ chains.
-That initial
-theory has been amplified during the past decade by several studies
+Whether carbon dust can or can not condense in the interiors of expanding 
+Type II supernovae is an important question for astronomy. Many have 
+assumed, guided by chemical equilibrium, that carbon condensation can 
+not occur unless carbon is more abundant than oxygen. That assumption 
+limits C condensation to the He-burning shell of SNII. This rule-of-thumb 
+was challenged when \citet{1999Sci...283.1290C}
+introduced a non-equilibrium kinetic theory by which carbon can 
+condense thermally in gas having more abundant oxygen, opening the 
+possibility of C condensation throughout the O-rich core. That 
+initial theory has been amplified by several studies 
 \citep{2001ApJ...562..480C,2003ApJ...594..312D,2006ApJ...638..234D,
-2009ApJ...703..642C,2010ApJ...713....1C,2011NewAR..55..155C,
-2013ApJ...762....5C}.
+2011NewAR..55..155C, 2013ApJ...762....5C}.
+Within their chemical model \citet{2009ApJ...703..642C,2010ApJ...713....1C}
+raised questions about the most effective way of producing $\ctwo$\ molecules, 
+which is the first step to linear carbon chains. They discovered that 
+the neutral-neutral reaction \coctoctwo\ has a reasonably large cross section 
+$\langle \sigma v \rangle = k_{CO,C} = 8.6 \times 10^{-14}$ cm$^3$ s$^{-1}$
+at temperatures near 5000K despite being endothermic by 4.8eV. 
+Although the CO target abundance for production of $\ctwo$\ in this 
+manner must be calculated, they stated that in their model 
+at $T = 5000$ K it created $\ctwo$\ much more rapidly than the slow radiative 
+reaction \twoctoctwo. Sensing high importance of this reaction for astronomy, 
+they claimed in their list of conclusions; 2. A new pathway to the 
+formation of carbon chains is active in the O-rich mass zone of the 
+unmixed ejecta and is identified as the CO conversion to $\ctwo$\ via 
+collisions with C. \citet{2009ApJ...703..642C} were unable to evaluate 
+the quantitative consequences because their reaction network 
+terminated at $\cthree$\ and did not include the formation of linear 
+carbon chains $\cenn$\ and their isomerization to carbon rings. 
+\citet{2010ApJ...713....1C} subsequently did include 
+linear chains to $n=10$, which they took to isomerize instantly 
+to ringed structure, following the published 
+model \citet{1999Sci...283.1290C, 2001ApJ...562..480C}.
 
-In basic agreement with this chemical model, \citet{2009ApJ...703..642C} raised
-questions about the most effective way of producing $\ctwo$\ molecules,
-which is the
-first step to linear carbon chains. Using a large network of chemical
-reactions, \citet{2009ApJ...703..642C} discovered that the neutral-neutral
-reaction \coctoctwo\
-has a reasonably large cross section at temperatures near
-5000K despite being endothermic by 4.8eV. Although the CO target abundance for
-production of $\ctwo$\ in this manner must be calculated, they stated that at
-$T=5000$ K the rate factor
-$\langle \sigma v \rangle = k_{CO,C} = 8.6 \times 10^{-14}$ cm$^3$ s$^{-1}$
-created $\ctwo$\ much more
-rapidly than the slow radiative reaction \twoctoctwo.
-Sensing its significance,
-they claimed in their list of conclusions: ``2. A new pathway to the formation
-of carbon chains is active in the O-rich mass zone of the unmixed ejecta and
-is identified as the CO conversion to $\ctwo$\ via collisions with C.''  They were
-unable to evaluate its full quantitative consequences because their reaction
-network terminated at $\cthree$\
-and did not include the formation of linear carbon
-chains $\cenn$
-and their isomerization to carbon rings. Doing so is one goal of our
-study. But the overriding goal is to point out large abundance differences
-between the computations of these two groups and to resolve them if possible.
+Testing their calculated abundances for $\cenn$\ is but a secondary 
+goal of the present study. Its overriding goal is to point out 
+abundance differences of several orders of magnitude for the CO 
+and $\ctwo$\ molecules between the computations of these two groups 
+and to resolve those differences if possible. This test has 
+important consequences for condensation of carbon dust, changing 
+prior expectations if the production of $\ctwo$\ owing to the reaction 
+\twoctoctwo\ severely underestimates the subsequent abundances of 
+linear carbon chains. \citet{2010ApJ...713....1C} harbored that 
+expectation owing to their belief that much more $\ctwo$\ is 
+made earlier near $T = 5000$ K and survives. Dust created by 
+supernova expansions is currently under intense study owing to three 
+types of astronomical observations: (1) of dust observed in single 
+supernova remnants; (2) of dust observed in early low-metallicity 
+galaxies; (3) of supernova-condensed carbon dust (SUNOCONs) 
+extracted from meteorites. Each of these topics depends sensitively on 
+how much carbon, both numbers and sizes, is able to condense in 
+cooling SNII interiors. Therefore we study this competition carefully.
 
-Several important consequences for astronomy depend on careful
-analysis of this claim that the production of $\ctwo$\ owing to the reaction
-\twoctoctwo, as \citet{1999Sci...283.1290C,2001ApJ...562..480C}
-had done, severely
-underestimates the abundances of linear carbon chains because much more $\ctwo$\
-is made earlier \citep{2010ApJ...713....1C} near $T = 5000$ K. Testing this
-competition is essential for understanding of dust condensation within
-supernovae. Dust created by supernova expansions is currently under intense
-study owing to three types of astronomical observations: (1) of dust observed
-in single supernova remnants; (2) of dust observed in early low-metallicity
-galaxies; (3) of supernova-condensed carbon dust (SUNOCONs) extracted from
-meteorites. Each of these topics depends sensitively on how much carbon,
-both numbers and sizes, is able to condense in cooling SNII interiors.
-Therefore we study this competition carefully.
-
-Crucial to this task is the lifetime $\tau_{CO}$ of CO molecules. Their thermal
-dissociation lifetime $\tau_\gamma$
-is calculated from detailed balance with the
-radiative association reaction, as in Section 2.1 of
-\citet{2001ApJ...562..480C}.
-Because of the large 11.1eV binding energy of the CO molecule,
-$\tau_\gamma$ is very
-temperature sensitive.  For readers' numerical ease we will tabulate
-$\tau_\gamma$ at
-selected key temperatures in Table \ref{tab:quantities} to follow.
-The flux and spectrum of newly
-injected Compton electrons \citep{1991ApJ...375..221C} yields the lifetime
-$\tau_e$ of CO
-molecules against inelastic scattering dissociation by Compton electrons
-caused by the $^{56}$Co
-radioactivity. In a gas of pure CO the mean energy per ion
-pair is defined as the energy of primary electrons divided by the number of
-pairs produced. \citet{1994ApJ...435..909L}
-calculated the mean energy per ion pair
-in pure CO gas and obtained the result $\Delta E = 32.3$ eV
-deposited per dissociated CO
-pair, which agrees well with the measurement of 32.2 eV by
-\citet{1968...Klots}.
-So the efficiency of energetic electrons for dissociating CO seems well
-established. A lifetime $\tau_{CO}$ near one week is typical in SN 1987A, but
-would be longer in SNII synthesizing less $^{56}$Co and at times greater than
-about 8 months.
+Crucial to this task is the lifetime $\tau_{CO}$ of CO molecules. 
+Thermal dissociation of CO is dominated by thermal photons because 
+radiative association of C and O dominates other reactions for 
+the formation of CO at the densities within SNII. Each reaction 
+and its inverse is subject to the quantum principle of detailed 
+balance. The thermal photodissociation lifetime $\tau_\gamma$ is 
+calculated from detailed balance with the radiative association reaction, as in 
+Section 2.1 of \citet{2001ApJ...562..480C}. Because of the large 11.1eV 
+binding energy of the CO molecule, $\tau_\gamma$ is very temperature sensitive. 
+For readers’ numerical ease we will tabulate $\tau_\gamma$ at selected key 
+temperatures in Table 1 to follow. The flux and spectrum of newly 
+injected Compton electrons \citep{1991ApJ...375..221C} yields the 
+lifetime $\tau_e$ of CO molecules against inelastic scattering dissociation by 
+Compton electrons caused by the $^{56}$Co radioactivity. In a gas of pure 
+CO the mean energy per ion pair is defined as the energy of primary 
+electrons divided by the number of pairs produced. 
+\citet{1994ApJ...435..909L} calculated the mean energy per ion pair 
+in pure CO gas and obtained the result $\Delta E = 32.3$ eV deposited 
+per dissociated CO pair, agreeing with the measurement of 32.2 eV 
+by \citet{1968...Klots}. So the efficiency of energetic electrons for 
+dissociating CO seems well established. A lifetime $\tau_{CO}$ near one 
+week is typical in SN 1987A, but would be longer in SNII 
+synthesizing less $^{56}$Co and at times greater than about 8 months.
 
@@
 $T = 3800 K / (t / 100 {\rm d}) =
-3.30 \times 10^{10} {\rm K} / t({\rm s})$,
-where t is the time elapsed since core collapse and $n_O = 10^{10}$ cm$^{-3}$
+3.30 \times 10^{10} / t({\rm s})\ {\rm K}$,
+where t is the time elapsed since core collapse.
+We chooose $n_O = 10^{10}$ cm$^{-3}$
 and $n_C = 10^9$ cm$^{-3}$
-at the starting time $t = t(6000 {\rm K})$ for our chemical network at
-$T=6000$ K. From our model choice for $T(t)$ we get
+at the starting time $t = t(6000 {\rm K})$ 
+at $T=6000$ K for our chemical network . From our model choice for $T(t)$ we get
 $t(6000K) = 5.47 \times 10^6$s. At
@@
 owing to homologous expansion.
-Let $N$ be the number in a comoving, expanding, initially 1 cm$^3$
-volume at 6000 K
-that held initially $n_O=10^{10}$ cm$^{-3}$ and $n_C = 10^9$ cm$^{-3}$.
+Let $N$ be the number of any specific molecular species
+in a comoving, expanding, initially 1 cm$^3$ volume at 6000 K.
 The only change of $N$ during
@@
 We use an intentionally limited set of chemical species because our goal is
-to study carbon chemistry: C, O, CO, $\ctwo$, $\cthree$, ... $\ceight$\ and
+to study the controversy over the correct 
+carbon chemistry pathway to the ringed isomers.
+We limit the present study to C, O, CO, $\ctwo$, $\cthree$, ... $\ceight$\ and
 $\ceightr$, the ringed isomer of $\ceight$, to which we give a lifetime
@@
 from linear $\ceight$ to ringed $\ceightr$.
+In a sense the $n = 8$ ring is a dummy standing for all rings; but it is also
+reasonable in being the smallest ring that is widely expected 
+(e.g. \citealt{doi:10.1021/j100374a025}).
 Those ringed molecules are the seeds for carbon
@@
 linear $\cenn$
-whereas their C capture rates are fast. We take ringed $\ceightr$ to be
-indestructible, simply integrating their rate of production.
-We cannot allege that $\ceight$\ is the key isomerizing chain, nor that
-$\tau_8^r = 10$ s is its lifetime, but those assumptions are adequate for
-comparing models for formation for $\ctwo$.
+whereas their C capture rates are fast. 
+For purposes of this study we take ringed $\ceightr$ to be
+indestructible, simply integrating its rate of production.
+%We cannot allege that $\ceight$\ is the key isomerizing chain, nor that
+%$\tau_8^r = 10$ s is its lifetime, but those assumptions are adequate for
+%comparing models for formation for $\ctwo$.
 Our strategy is
@@
 balance these creation and destruction effects, doing so exactly at the
-time of maximum $n_{CO}$. \citet{2013ApJ...762....5C}
+time $t = t_{max}$ of maximum $n_{CO}$. \citet{2013ApJ...762....5C}
 has discussed the shape of the function
@@
 To display each $Y_i$ on a figure with
-reasonable ordinate resolution, we have scaled each $\cenn$\ by the factor
-stated in the box. Many features are noteworthy: (1) C and O are constant
+reasonable ordinate resolution, we have scaled each $Y_n$\ by the factor
+stated in the box. Many features are noteworthy: (1) $Y_C$ and $Y_O$ 
+are constant
 because their small depletion is negligible on the scale shown;
-(2) maxima in CO and $\ctwo$\ occur at almost exactly the same time
+(2) maxima of $Y_{CO}$ and $Y_2$\ occur at almost exactly the same time
 $t-t(6000K)= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
-(3) $\cthree$\ has very small abundance, about $3 \times 10^{-8}$ of $\ctwo$
-at the $\ctwo$\ maximum, although much later $\cthree$\ slowly grows modestly
-relative to much more abundant $\ctwo$; (4) the rise shapes of $\cfour$
-through $\ceight$\ are very similar because they are linked by a near steady
-state; (5) the ringed carbon $\ceightr$\ has similar abundance shape vs. time,
-but notice that it is actually much more abundant than $\cseven$ and
-$\ceight$ because it accumulates from isomeric transitions of $\ceight$\
+(3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$\
+at the $Y_2$\ maximum, although much later $Y_3$\ slowly grows modestly
+relative to much more abundant $\ctwo$; (4) the rise shapes of $Y_4$
+through $Y_8$\ are very similar because they are linked by a near steady
+state; (5) the ringed carbon $Y(\ceightr$) has similar abundance shape vs. time,
+but notice that it is actually much more abundant than lineaer $C_{7-8}$ and
+because it accumulates from isomeric transitions of $\ceight$\
 and unlike $\cenn$\ does not
@@
 
-One sees from Fig. \ref{fig:Yi} that the \coctoctwo\ reaction plays no
+One sees from Fig. \ref{fig:yi} that the \coctoctwo\ reaction plays no
 role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
@@
 Whatsoever $\ctwo$\ is made earlier plays no role in $\ceightr$\ production
-because there ejection of C atoms from $\cenn$\ at higher $T$ prevents the
+because the ejection of C atoms from $\cenn$\ at higher $T$ prevents the
 flow to $\ceight$.  Only at $T < 2000$ K do those photodissociation reactions
@@
 recently
-formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:Yi} also shows
+formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:yi} also shows
 that $Y(\ceightr)$
@@
 the curve flattens because photoejection from $\cenn$\ by thermal photons
-(or phonons) weakens. These abundance ratios are almost in a steady state,
+(or vibrations) weakens. These abundance ratios are almost in a steady state,
 but that steady state changes slightly as $T$ falls. These patterns show
@@
 The reactions are specified there in the
-compact notation target(in,out)residual. Fig. \ref{fig:cn} and
+compact notation target(in,out)residual. 
+We tabulate the flow magnitudes for $\csix$ to aid readers checking our
+numerical results. Fig. \ref{fig:cn} and
 Table \ref{tab:flows} are made to be studied together.
@@
 obviates the need for creating a photon \citep{1999Sci...283.1290C},
-and its inverse reaction which ejects a C atom. Furthermore, those flows
-are equal to three significant figures, illustrating the near steady
+and its inverse reaction which ejects a C atom. Furthermore, those two flows
+are equal to each other to three significant figures, illustrating the near 
+steady
 state of the abundance pattern. Secondly, thermal dissociation of $\csix$\ is
@@
 (2031 {\rm K}/6000 {\rm K})^3 = 4.27 \times 10^8{\rm cm}^{-3}$.
-The fast oxidation reaction rate is
+The fast oxidation reaction rate factor is
 $k(\csix + {\rm O}) = 3 \times 10^{-10} {\rm cm}^3{\rm s}^{-1}$.
@@
 \tableline\tableline
-$t$ (s) & $t - t(6000 {\rm K})$ (s) & $\left(t / t(6000 {\rm K} \right)^{-3}$ & $T$ (K) & $\tau_\gamma$ (s) & $k_{CO}$ (cm$^{-3}$ s$^{-1}$) & $\ncogeq$ (cm$^{-3}$) \\
+$t$ (s) & $\left[t / t(6000 {\rm K}) \right]^{-3}$ & $T$ (K) & $\tau_\gamma$ (s) & $k_{CO}$ (cm$^{-3}$ s$^{-1}$) & $\ncogeq$ (cm$^{-3}$) \\
 \tableline
 $5.47 \times 10^6$ &
-  0 &
   1 &
@@
 $5.97 \times 10^6$ &
-  $4.97 \times 10^5$ &
   0.769 &
@@
 $6.57 \times 10^6$ &
-  $1.09 \times 10^6$ &
   0.578 &
@@
 $7.30 \times 10^6$ &
-  $1.82 \times 10^6$ &
   0.422 &
@@
 $8.21 \times 10^6$ &
-  $2.74 \times 10^6$ &
   0.296 &
@@
 $9.38 \times 10^6$ &
-  $3.91 \times 10^6$ &
   0.198 &
@@
 $1.09 \times 10^7$ &
-  $5.47 \times 10^6$ &
   0.125 &
@@
 
+\bibitem[{Takai {et~al.}(1990)Takai, Lee, Halicioglu, \&
+  Tiller}]{doi:10.1021/j100374a025}
+Takai, T., Lee, C., Halicioglu, T., \& Tiller, W.~A. 1990, The Journal of
+  Physical Chemistry, 94, 4480
+
 \end{thebibliography}

### 2013-03-14 doc/submit/ms.tex
Minor text change.

@@
 $t-t(6000K)= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
-(3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$\
-at the $Y_2$\ maximum, although much later $Y_3$\ slowly grows modestly
+(3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$, 
+although much later $Y_3$\ slowly grows modestly
 relative to much more abundant $\ctwo$; (4) the rise shapes of $Y_4$
@@
 \bibitem[{{Cherchneff} \& {Dwek}(2009)}]{2009ApJ...703..642C}
-{Cherchneff}, I. \& {Dwek}, E. 2009, \apj, 703, 642
+{Cherchneff}, I. \& {Dwek}, E. 2009, \apjl, 703, 642
 

### 2013-04-01 doc/submit/ms.tex
Modify text for RefReport2.

@@
 \documentclass[manuscript]{aastex}
+\usepackage{CJK}
 
@@
 \begin{document}
+\begin{CJK*}{UTF8}{gbsn}
 
@@
 
-\author{Tianhong Yu, Bradley S. Meyer, and Donald D. Clayton}
+\author{Tianhong Yu (喻天弘), Bradley S. Meyer, and Donald D. Clayton}
 \affil{Department of Physics and Astronomy, Clemson University, Clemson, SC 29634-0978}
@@
 and $n_C = 10^9$ cm$^{-3}$
-at the starting time $t = t(6000 {\rm K})$ 
+at the starting time $t = t_{6000 {\rm K} }$ 
 at $T=6000$ K for our chemical network . From our model choice for $T(t)$ we get
-$t(6000K) = 5.47 \times 10^6$s. At
-subsequent times $n_O(t) = 10^{10}{\rm cm}^{-3}(t/t(6000 {\rm K}))^{-3}$
+$t_{6000 {\rm K} } = 5.47 \times 10^6$s. At
+subsequent times $n_O(t) = 10^{10}{\rm cm}^{-3}(t/t_{6000 {\rm K}})^{-3}$
 owing to homologous expansion.
@@
 stars is a mix of C and O atoms having bulk C/O $<$ 1. Post explosive cooling of
-such matter will attempt to associate C and O into CO molecules, with rate
-coefficient $k_{CO} = 3.3 \times 10^{-17}$ cm$^3$ s$^{-1}$
+such matter will attempt to associate C and O into CO molecules 
 \citep{1990ApJ...358..262L}.
@@
 In our numerical example we take $n_O = 10^{10}$ cm$^{-3}$ and
-$n_C = 10^9$ cm$^{-3}$ at $t(6000 {\rm K})$ as starting conditions for the
+$n_C = 10^9$ cm$^{-3}$ at $t_{6000 {\rm K}}$ as starting conditions for the
 chemical network. Subsequent values are $n = 1.1 \times 10^{10}$ cm$^{-3}$
-$[t(6000 {\rm K})/t]^3$, where the expansion factor reduces the initial number
+$[t_{6000 {\rm K}}/t]^3$, where the expansion factor reduces the initial number
 density appropriately. Expansion factors are also in Table 1. Then
@@
 their initial values at $T=6000$ K have been reduced by the expansion factor
-$(t/t(6000 {\rm K}))^{-3}$.
+$(t/t_{6000 {\rm K}})^{-3}$.
 Tight agreement for $T > 4000$ K is immediately evident,
@@
 At its final maximum $n_{CO} = 1.5 \times 10^6$ cm$^{-3}$,
-corresponding to $Y(CO) = 0.7 \times 10^{-3}$. The slow growth of $n_{CO}$
+corresponding to $Y_{CO} = 0.7 \times 10^{-3}$. The slow growth of $n_{CO}$
 shown in Fig. \ref{fig:nco} differs markedly from the results of
@@
 shows the abundances $Y_i$ of each species in our small network as a
-function of time $t-t(6000 {\rm K})$ after $T=6000$ K.
+function of time $t-t_{6000 {\rm K}}$ after $T=6000$ K.
 From Table \ref{tab:quantities},
-start time is $t(6000K) =5.47 \times 10^6$ s.
+start time is $t_{6000 {\rm K}} =5.47 \times 10^6$ s.
 To display each $Y_i$ on a figure with
@@
 (2) maxima of $Y_{CO}$ and $Y_2$\ occur at almost exactly the same time
-$t-t(6000K)= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
+$t-t_{6000K}= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
 (3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$, 
@@
 through $Y_8$\ are very similar because they are linked by a near steady
-state; (5) the ringed carbon $Y(\ceightr$) has similar abundance shape vs. time,
+state; (5) the ringed carbon abundance $Y_8^r$ has similar abundance shape 
+vs. time,
 but notice that it is actually much more abundant than lineaer $C_{7-8}$ and
@@
 role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
-$t - t(6000 {\rm K}) > 1.5 \times 10^7$ s, corresponding to $T < 2000$ K,
+$t - t_{6000 {\rm K}} > 1.5 \times 10^7$ s, corresponding to $T < 2000$ K,
 despite $\ctwo$\ and $\cthree$\ rising at much earlier times.
@@
 formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:yi} also shows
-that $Y(\ceightr)$
+that $Y_8^r$
 grows quickly to $10^{-16}$.  Since available C is $Y_C = 0.1$,
-the ratio gives $10^{-15}$ C/ring.  This is enough to grow very large
+the ratio gives $10^{15}$ C/ring.  This is enough to grow very large
 graphite.
@@
 but that steady state changes slightly as $T$ falls. These patterns show
-almost equal values for $Y(\cthree)$ because that curve is relatively flat
-with time near $t-t(6000K) = 10^7$ s (Fig. \ref{fig:yi}).
+almost equal values for $Y_3$ because that curve is relatively flat
+with time near $t-t_{6000 {\rm K}} = 10^7$ s (Fig. \ref{fig:yi}).
 Table \ref{tab:flows} lists our computed reaction flows both in and out of
@@
 Note that the abundances of $\ceight$\ are very small:
-$Y(\ceight)= 10^{-36}$ at $T = 1802$ K.
+$Y_8= 10^{-36}$ at $T = 1802$ K.
 The isomeric transition from linear to
@@
 From Fig. \ref{fig:cn}
-one sees that at $T = 2031$ K the abundance $Y(\csix) = 10^{-33.3}$.
-The value of $Y(O) = 10^{10} cm^{-3} / 1.1 \times 10^{10} cm^{-3} = 0.909$,
+one sees that at $T = 2031$ K the abundance $Y_6 = 10^{-33.3}$.
+The value of $Y_O = 10^{10} cm^{-3} / 1.1 \times 10^{10} cm^{-3} = 0.909$,
 so the flow per atom per
 second (e.g., Eq. \ref{eq:dycodt}) is
-$dY/dt= Y(\csix)Y(O)n(2031K)k(\csix + {\rm O})$.
+$dY/dt= Y_6 Y_O n(2031K)k(\csix + {\rm O})$.
 Expansion from $T=6000$ K to $T=2031$ K has diluted the total number
@@
 
-\item Instead of growing large CO abundance near $Y(CO)=0.1$ at $T=5500$ K
-as in Fig. 11 of \citet{2009ApJ...703..642C}, we find that $Y(CO)$
+\item Instead of growing large CO abundance near $Y_{CO}=0.1$ at $T=5500$ K
+as in Fig. 11 of \citet{2009ApJ...703..642C}, we find that $Y_{CO}$
 builds to a maximum of only $10^{-3}$, which it achieves only slowly
@@
 Figure \ref{fig:no_gamma} displays the result.
-The rapid rise of $Y(CO)$ to about $10^{-2}$ at high temperature is very 
+The rapid rise of $Y_{CO}$ to about $10^{-2}$ at high temperature is very 
 similar to Fig. 11 of \citet{2009ApJ...703..642C}.
-Similar also is $Y(\ctwo)$,
-which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y(CO)$,
-whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y(CO)$ to be
+Similar also is $Y_2$,
+which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y_{CO}$,
+whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y_{CO}$ to be
 only $10^{-8}$ at $T=5500$ K and, considerably later,
-$Y(\ctwo)/Y(CO) = 10^{-7}$ at their maxima.
+$Y_2/Y_{CO} = 10^{-7}$ at their maxima.
 
@@
 establish a steady state
-ratio $Y(CO)/Y(\ctwo) = 3.5 \times 10^4$. Fig. \ref{fig:no_gamma}
+ratio $Y_{CO}/Y_2 = 3.5 \times 10^4$. Fig. \ref{fig:no_gamma}
 and their Fig. 11 do show
-approximately that value, but $Y(\ctwo)$ declines faster than $Y(CO)$
+approximately that value, but $Y_2$ declines faster than $Y_{CO}$
 because of declining production of $\ctwo$\ as T declines.
@@
 Compton electrons for $T < 3500$ K.
-One see in Fig. \ref{fig:nco} that $n_{CO}$max occurs near 3500K,
+One see in Fig. \ref{fig:nco} that $n_{CO,max}$ occurs near 3500K,
 which occurs near $10^7$ s (see Table \ref{tab:quantities}).} 
@@
 The abundance (number per atom) of linear chains $\cenn$\ and of ringed isomer
-$\ceightr$. We have scaled each $Y(C_n)$ by the factor stated in the box.}
+$\ceightr$. We have scaled each $Y_n$ by the factor stated in the box.}
 \label{fig:yi}
@@
 \caption{
-Shape of $Y(C_n)$ vs. n for $\cthree$\ to $\ceight$
+Shape of $\log10(Y_n)$ vs. n for $\cthree$\ to $\ceight$
 at two different temperatures
@@
 Abundances for network containing only C, O, CO, $\ctwo$, and $\cthree$
-when photodissociation of molecules is omitted. Rapid rise of $Y(CO)$
-to $10^{-2}$ near 5500 K and the ratio $Y(CO)/Y(\ctwo)$ near $10^4$ are
+when photodissociation of molecules is omitted. Rapid rise of $Y_{CO}$
+to $10^{-2}$ near 5500 K and the ratio $Y_{CO}/Y_2$ near $10^4$ are
 similar to Fig. 11 of \citet{2009ApJ...703..642C}.
@@
 \tableline\tableline
-$t$ (s) & $\left[t / t(6000 {\rm K}) \right]^{-3}$ & $T$ (K) & $\tau_\gamma$ (s) & $k_{CO}$ (cm$^{-3}$ s$^{-1}$) & $\ncogeq$ (cm$^{-3}$) \\
+$t$ (s) & $\left[t / t_{6000 {\rm K}} \right]^{-3}$ & $T$ (K) & $\tau_\gamma$ (s) & $k_{CO}$ (cm$^{-3}$ s$^{-1}$) & $\ncogeq$ (cm$^{-3}$) \\
 \tableline
@@
 
+\end{CJK*}
 \end{document}

### 2013-07-07 doc/condensation.tex
Add description of the condensation calculation.

\documentclass{article}

\begin{document}

\section{Abundance Change}

For a reaction:
\[
1 + 2 \longleftrightarrow 3 + \gamma
\]
we can write the number density change of species 1 as:
\begin{equation}
\frac{{\rm d}n_1}{{\rm d}t} = 
  -k \, n_1 n_2 + \lambda_\gamma n_3
\label{eq:number_density}
\end{equation}
where $k$ is the reaction rate in the unit of $cm^3s^{-1}$ and 
$\lambda_\gamma$ is the photodissociation rate of species 3 with the unit of
$s^{-1}$.

In a expanding or a collapsing system the number densities change with volume. 
We'd like to study a quantity that does not depend on volume directly so that
we use the fraction of each species in number instead of number density:
\[
Y_i \equiv n_i / n_{total}
\]
where $Y_i$ is called the abundance of species i, $n_i$ is the number density
of species i and $n_{total}$ is the number density of the unit particles, here
the number density of total atoms. So $Y_i$ here indicates the number
of species i per atom. And
\[
n_{total} = n_{atom} = n_{baryon} \times Y_{atom} 
\]
where $n_{baryon} = \rho N_A$ is the baryon number density and $Y_{atom}$ is
the atom fraction, i.e. number of atoms per baryon. Take pure $^{12}$C for 
example, $Y_{atom} = 1 / 12$. So Eq.\ref{eq:number_density} can be rewrite as
\begin{equation}
\frac{{\rm d}Y_1}{{\rm d}t} = 
  -k n_{atom} =
  -k \rho N_A Y_{atom} Y_1 Y_2 + \lambda_\gamma Y_3
\label{eq:abundance}
\end{equation}
where $\rho$ is the mass density and $N_A$ is the Avogadro number. Then what
we need to study is how the abundances of each species change with time.

\section{Condensation Effective Rates}

For a single kind of atom, we study the effective condensation rate here.
The condensation here means one atom attaches to an existing multi-atom
particle:
\begin{equation}
P_1 + P_i \longleftrightarrow P_{i+1} + \gamma
\label{eq:reaction}
\end{equation} 
where $P_i$ denotes a particle with $i$ atoms in it.

Let's assume that the condensation rate is proportional to the surface area
(or cross section) of the larger particle, which goes like $n^{2/3}$, i.e.
\[
k \propto A \propto n^{2/3}
\]
where $k$ is the rate, $A$ is the surface area and $n$ is the number of atoms
in the particle.

To make the calculation of a large atom number particle possible, we introduce
the ``bin" after a continuous size increment. In a bin we neglect the details 
of the single particles and focus on the
two ends of the bin. For example if we start the bin from size $a$ and the bin 
size is 10, the particles we care about after size $a$
are just $P_a$, $P_{10a}$, $P_{100a}$, etc. 
And we just calculate the effective reaction rates between these particles.

From graph theory we know that for a series of vertices 1, 2, ..., N, the
effective rate between 1 and N is like:
\[
k_{1,N}^{eff} \Delta t = \frac 
  { k_{1,2}k_{2,3}...k_{N-1,N}\Delta t^{N-1} }
  { 
    k_{2,3}k_{3,4}...k_{N-1,N}\Delta t^{N-2} +
    k_{1,2}k_{3,4}...k_{N-1,N}\Delta t^{N-2} +
    ...
    k_{1,2}...k_{N-2,N-1}\Delta t^{N-2}
  }
\]

\[
k_{1,N}^{eff} = \frac {1}
  { 
    \frac{1}{k_{1,2}} +
    \frac{1}{k_{2,3}} +
    ...
    \frac{1}{k_{N-1,N}}
  }
\]

Back to the problem we are looking at(Eq.\ref{eq:reaction}), we can write
\[
k_{i,i+1} \equiv k_i = k_1 i^{2/3}
\]
If we start from $p_a$, for the bin size of $b$ we can write the effective
reaction as:
\[
P_a + a\times (b-1) P_1 \to P_{a\times b}
\]
And the effective rate is
\[
k^{eff} = \frac {1}
  {
    \frac {1} {k_{a}} +
    \frac {1} {k_{a+1}} +
    ...
    \frac {1} {k_{a\times b}}
  }
\]
\[
\frac {1} {k_{eff}} =
  \sum_{i=a}^{a\times b} \frac {1} {k_i} =
  \frac{1}{k_1} \sum_{i=a}^{a\times b} \frac {1} {i^{2/3}} \approx
  \frac{1}{k_1} \int_a^{a\times b} x^{-2/3} {\rm d} x =
  \frac{1}{k_1} \cdot 3 \cdot [(a\times b)^{1/3} - a^{1/3}]
\]
\[
k^{eff} = \frac{k_1}{3} 
  \frac{1}{ (a\times b)^{1/3} - a^{1/3} }
\]

If we denote the atom number at the beginning of a bin as $N_{begin}$ and
the one at the end as $N_{end}$, then we can write the effective rate as:
\begin{equation}
k^{eff} = \frac{k_1}{3} 
  \frac{1}{ N_{end}^{1/3} - N_{begin}^{1/3} }
\label{eq:rate}
\end{equation}

We estimate $k_1$ as two single atoms collide together with thermal velocity
and the transverse section.
\begin{equation}
k_1 = \: <\! \sigma_1 v\! > \: = \pi R^2 \sqrt{3k_BT/m}
\label{eq:k1}
\end{equation}
where $\sigma_1$ is the cross section for a single atom and $R$ is the radius
of a single atom, $v$ is the thermal velocity which is taken to be the average
value in 3 dimensions, $k_B$ is the Boltzmann constant, $T$ is the temperature
and $m$ is the mass of a single atom.

\section{Atom Conservation}

The abundance change rates of $P_{begin}$, $P_{end}$ and $P_1$ due to 
reaction $P_{begin} + X P_1 \longleftrightarrow P_{end} + \gamma$ are
\[
\frac{{\rm d}Y_{begin}}{{\rm d}t} =
  -k^{eff} Y_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end}  
\]
\[
\frac{{\rm d}Y_{end}}{{\rm d}t} =
  k^{eff} Y_{atom} Y_{begin} Y_1 - \lambda_\gamma^{eff} Y_{end}  
\]
\[
\frac{{\rm d}Y_1}{{\rm d}t} =
  X( -k^{eff} Y_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end} )
\]
where $\lambda_\gamma^{eff}$ is the effective photodissociation rate which
will be discussed later and $X$ is the factor to be determined that ensure
the total atom number conserved. Atom conservation requires
\[
N_{begin} \times \frac{{\rm d}Y_{begin}}{{\rm d}t} +
N_{end} \times \frac{{\rm d}Y_{end}}{{\rm d}t} +
\frac{{\rm d}Y_1}{{\rm d}t} = 0.
\] 
So we have
\[
X = N_{end} - N_{begin}
\]

\end{document}

### 2013-07-14 doc/condensation.tex
Add bins as zone properties and the effective rates docs.

@@
 \frac{{\rm d}Y_1}{{\rm d}t} = 
-  -k n_{atom} =
+  -k n_{atom} Y_1 Y_2 + \lambda_\gamma Y_3 =
   -k \rho N_A Y_{atom} Y_1 Y_2 + \lambda_\gamma Y_3
@@
 \frac{{\rm d}Y_{begin}}{{\rm d}t} =
-  -k^{eff} Y_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end}  
+  -k^{eff} n_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end}  
 \]
@@
 \frac{{\rm d}Y_{end}}{{\rm d}t} =
-  k^{eff} Y_{atom} Y_{begin} Y_1 - \lambda_\gamma^{eff} Y_{end}  
+  k^{eff} n_{atom} Y_{begin} Y_1 - \lambda_\gamma^{eff} Y_{end}  
 \]
@@
 \frac{{\rm d}Y_1}{{\rm d}t} =
-  X( -k^{eff} Y_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end} )
+  X( -k^{eff} n_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end} )
 \]
@@
 
+\section{Network Matrix}
+Let's look at the reaction between the last species in the continuous network
+and the first bin, and neglect the photodissociation here:
+\[
+P_{last} + XP_1 \to P_{b1}
+\]
+The abundance change rates are then (using $n_a$ to denote $n_{atom}$)
+\[
+\frac{{\rm d}Y_{last}}{{\rm d}t} =
+  -k^{eff}_{last} \, n_a Y_{last} Y_1
+\]
+\[
+\frac{{\rm d}Y_{b1}}{{\rm d}t} =
+  k^{eff}_{last} \, n_a Y_{last} Y_1
+\]
+\[
+\frac{{\rm d}Y_1}{{\rm d}t} =
+  ( -k^{eff}_{last} \, n_a Y_{last} Y_1 )(N_{b1} - N_{last})
+\]
+Then the changes of the root-finding functions are (how to call them?)
+\[
+f_{last} \: +\!\!= \: k^{eff}_{last} \, n_a Y_{last} Y_1
+\]
+\[
+f_{1} \: +\!\!= \: (k^{eff}_{last} \, n_a Y_{last} Y_1) (N_{b1} - N_{last})
+\]
+To find the abundance changes in the continuous network, we need to solve the
+matrix
+\[
+AX=B
+\]
+The matrix element changes due to this reaction are
+\[
+A_{last,last} \: +\!\!= \: k^{eff}_{last} \, n_a Y_1
+\]
+\[
+A_{last,1} \: +\!\!= \: k^{eff}_{last} \, n_a Y_{last}
+\]
+\[
+A_{1,last} \: +\!\!= \: (k^{eff}_{last} \, n_a Y_1)(N_{b1} - N_{last})
+\]
+\[
+A_{1,1} \: +\!\!= \: (k^{eff}_{last} \, n_a Y_{last})(N_{b1} - N_{last})
+\]
+The right-hand-side vector changes are
+\[
+B_{last} \: +\!\!= \: -f_{last} = -k^{eff}_{last} \, n_a Y_{last} Y_1 
+\]
+\[
+B_1 \:+\!\!=\: -f_1 = -(k^{eff}_{last}\,n_a Y_{last} Y_1)(N_{b1}-N_{last})
+\]
+
+Now let's look at the reactions between bins. $P_{bi} + XP_1 \to P_{b(i+1)}$,
+where $i$ goes from 1 to $N-1$ with $N$ as the number of bins.
+\[
+\left( \frac{{\rm d}Y_1}{{\rm d}t}\right) _i =
+  ( -k^{eff}_{bi} \, n_a Y_{bi} Y_1 )(N_{b(i+1)} - N_{bi})
+\]
+\[
+(f_{1})_i \: +\!\!= \: 
+  (k^{eff}_{bi} \, n_a Y_{bi} Y_1) (N_{b(i+1)} - N_{bi})
+\]
+\[
+(A_{1,1})_i \: +\!\!= \: 
+  (k^{eff}_{bi} \, n_a Y_{bi}) (N_{b(i+1)} - N_{bi})
+\]
+\[
+(B_1)_i \:+\!\!=\: -(f_1)_i = 
+  -(k^{eff}_{bi} \, n_a Y_{bi} Y_1) (N_{b(i+1)} - N_{bi})
+\]
+We first solve the matrix equation for current $Y_{bi}$, and then compute
+the abundance changes in bins using the new abundances in the network.
+Then feed the new bin abundances back to the matrix. Iterate until converge.
+
+\section{Bin Abundances Change}
+
+Now let's look at the abundance changes in bins for each reaction discussed
+above. We are going to solve these changes implicitly. For $Y_{b1}$,
+\[
+\frac {Y_{b1}(t+\Delta t) - Y_{b1}(t)} {\Delta t} =
+  k^{eff}_{last} \, n_a Y_{last}(t+\Delta t) Y_1(t+\Delta t) -
+  k^{eff}_{b1} \, n_a Y_{b1}(t+\Delta t) Y_1(t+\Delta t)
+\]
+\[
+Y_{b1}(t+\Delta t) = \frac
+  {k^{eff}_{last} \, n_a Y_{last}(t+\Delta t) Y_1(t+\Delta t) \Delta t +
+    Y_{b1}(t)}
+  {1 + k^{eff}_{b1} \, n_a Y_1(t+\Delta t) \Delta t}
+\]
+Similarly for $Y_{bi}$ as $i$ goes from 2 to $N-1$:
+\[
+Y_{bi}(t+\Delta t) = \frac
+  {k^{eff}_{b(i-1)} \, n_a Y_{b(i-1)}(t+\Delta t) Y_1(t+\Delta t) \Delta t +
+    Y_{bi}(t)}
+  {1 + k^{eff}_{bi} \, n_a Y_1(t+\Delta t) \Delta t}
+\]
+For $Y_{bN}$ we don't have any destructive terms for now,
+\[
+Y_{bN}(t+\Delta t) = 
+  k^{eff}_{b(N-1)} \, n_a Y_{b(N-1)}(t+\Delta t) Y_1(t+\Delta t) \Delta t +
+    Y_{bi}(t)
+\]
+
 \end{document}

### 2013-07-14 carbon_evolve.cpp

@@ -1,5 +1,5 @@
-//////////////////////////////////////////////////////////////////////////////
-// This file was originally written by Bradley S. Meyer.
+////////////////////////////////////////////////////////////////////////////////
+// This file was originally written by Bradley S. Meyer and Tianhong Yu.
 //
 // This is free software; you can redistribute it and/or modify it
 // under the terms of the GNU General Public License as published by
@@ -24,13 +24,6 @@
 
 #include "carbon_evolve.h"
 
-/**
- * @brief A namespace for user-defined functions.
- */
-
-namespace my_user
-{
-
 //##############################################################################
 // evolve()
 //##############################################################################
@@ -45,6 +38,7 @@ evolve(
   gsl_vector *p_y_old, *p_rhs, *p_sol, *p_work;
   double d_dt;
   std::pair<double,double> check;
+  double check_bin = 0;
   
   //==========================================================================
   // Evolve NSE + weak rates, if appropriate.
@@ -81,6 +75,17 @@ evolve(
 
   p_y_old = Libnucnet__Zone__getAbundances( zone.getNucnetZone() );
 
+  //==========================================================================
+  // Save the old bin abundances.
+  //==========================================================================
+    
+  std::vector<double> v_bin_old;
+
+  if( 
+    zone.hasProperty( "run bin" ) && zone.getProperty( "run bin" ) == "yes"
+  )
+    v_bin_old = get_bin_abundances( zone );
+
   //============================================================================
   // Newton-Raphson Iterations.
   //============================================================================
@@ -92,17 +97,7 @@ evolve(
     //--------------------------------------------------------------------------
 
     boost::tie( p_matrix, p_rhs ) = 
-      user::get_evolution_matrix_and_vector( zone );
-
-    //--------------------------------------------------------------------------
-    // Update decade rates. 
-    //--------------------------------------------------------------------------
-
-    if( 
-      zone.hasProperty( S_RUN_DECADE ) &&
-      zone.getProperty( S_RUN_DECADE ) == "yes"
-    ) 
[…]

### 2013-07-14 carbon_evolve.h

@@ -27,44 +27,35 @@
 #include "carbon_rate_functions.h"
 #include "carbon_hydro.h"
 
-/**
- * @brief A namespace for user-defined rate functions.
- */
-namespace my_user
-{
-
 int
 evolve( nnt::Zone& );
 
-void
-update_102_rates(
-  WnMatrix *,
-  gsl_vector *,
-  nnt::Zone &
+double
+compute_effective_rate(
+  nnt::Zone &, double, double
 );
 
 void
-update_decade_rates(
-  WnMatrix *,
-  gsl_vector *,
-  nnt::Zone &
+update_bin_rates(
+  nnt::Zone &, WnMatrix *, gsl_vector *
 );
 
-size_t
-get_gsl_vector_index_for_species(
-  unsigned int,
-  unsigned int
-);
-
-unsigned int
-get_matrix_row_index_for_species(
-  unsigned int,
-  unsigned int
+void
+evolve_bin( 
+  nnt::Zone &, std::vector<double> &
 );
 
 double
-compute_effective_rate(
-  double, double, double
+check_bin_change(
+  nnt::Zone &
 );
 
-} // namespace my_user
+std::vector<double>
+get_bin_abundances(
+  nnt::Zone &
+);
+
+std::pair<WnMatrix *, gsl_vector *>
+get_evolution_matrix_and_vector( 
+  nnt::Zone &
+);

### 2013-07-14 carbon_hydro.cpp

@@ -148,87 +148,6 @@ get_nucnet( int argc, char **argv )
 
   Libnucnet__assignZoneDataFromXml( p_nucnet, argv[2], NULL );
 
-  //============================================================================
-  // Create decade molecules and reactions if desired. 
-  //============================================================================
-
-  nnt::Zone zone;
-
-  if( !Libnucnet__getZoneByLabels( p_nucnet, "0", "0", "0" ) )
-  {
-    std::cerr << "Zone not found!" << std::endl;
-    return 0;
-  }
-
-  zone.setNucnetZone(
-    Libnucnet__getZoneByLabels( p_nucnet, "0", "0", "0" )
-  );
-
-  if( 
-    zone.hasProperty( S_RUN_DECADE ) &&
-    zone.getProperty( S_RUN_DECADE ) == "yes"
-  )
-  {
-
-    unsigned int i_exp_start = 
-      boost::lexical_cast<unsigned int>( zone.getProperty( S_EXP_START ) );
-    unsigned int i_exp = 
-      boost::lexical_cast<unsigned int>( zone.getProperty( S_EXP ) );
-    unsigned int i_base = 
-      boost::lexical_cast<unsigned int>( zone.getProperty( S_BASE ) );
-    unsigned int i_photon_end = 
-      boost::lexical_cast<unsigned int>( zone.getProperty( S_PHOTON_END ) );
-
-    Libnucnet__free( p_nucnet );
-
-    p_nucnet = Libnucnet__new();
-
-    my_user::add_molecules_to_nuc(
-      Libnucnet__Net__getNuc( Libnucnet__getNet( p_nucnet ) ),
-      1, 
-      i_exp_start
-    );
-
-    my_user::add_reactions_to_net(
-      Libnucnet__getNet( p_nucnet ),
-      1,
-      i_photon_end
-    ); 
-  
-    my_user::add_forward_reactions_to_net(
-      Libnucnet__getNet( p_nucnet ),
-      i_photon_end,
-      i_exp_start
-    ); 
-
-    for( 
-      unsigned int i = 1; 
-      i <= i_exp; 
-      i++
-    )
-    {
-  
-      unsigned int i_index =
-        i_exp_start *
-        (unsigned int) pow( 
-          i_base,
-          i
-        ); 
-        
-      my_user::add_molecules_to_nuc(
-        Libnucnet__Net__getNuc( Libnucnet__getNet( p_nucnet ) ),
-        i_index,
-        i_index
-      );
-  
-    }
-
[…]

### 2013-07-14 carbon_hydro.h

@@ -34,8 +34,7 @@
 
 #include "user/network_utilities.h"
 
-#include "my_molecule_utilities.h"
-#include "my_reaction_utilities.h"
+#include "my_network_utilities.h"
 
 //##############################################################################
 // Defines.
@@ -43,12 +42,6 @@
 
 #define S_POWER                    "power"   // Temperature cooling power. 
 #define S_OUTPUT_XML_FILE          "output xml file"
-
-#define S_RUN_DECADE               "run decade"
-#define S_EXP_START                "exp start"
-#define S_BASE                     "base"
-#define S_EXP                      "exp"
-#define S_PHOTON_END               "photon end"
 
 //##############################################################################
 // Validation.  "no" = no validation, "yes" = validation.
@@ -69,5 +62,7 @@ void update_zone_properties( nnt::Zone& );
 int set_zone( Libnucnet *, nnt::Zone&, char ** );
 
 void get_trajectory_data( char * );
+
+double compute_carbon_k1( nnt::Zone & );
 
 #endif // CARBON_HYDRO

### 2013-07-14 create_my_network.cpp

@@ -1,51 +1,0 @@
-////////////////////////////////////////////////////////////////////////////////
-// This file was originally written by Tianhong Yu.
-//
-// This is free software; you can redistribute it and/or modify it
-// under the terms of the GNU General Public License as published by
-// the Free Software Foundation; either version 2 of the License, or
-// (at your option) any later version.
-//
-// This software is distributed in the hope that it will be useful,
-// but WITHOUT ANY WARRANTY; without even the implied warranty of
-// MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-// GNU General Public License for more details.
-//
-////////////////////////////////////////////////////////////////////////////////
-
-////////////////////////////////////////////////////////////////////////////////
-//! \file
-//! \brief Example code to create carbon network. 
-////////////////////////////////////////////////////////////////////////////////
-
-#include "my_molecule_utilities.h"
-#include "my_reaction_utilities.h"
-
-int main()
-{
-
-  unsigned int i_max = 10000;
-
-  Libnucnet__Net * p_net;
-
-  p_net = Libnucnet__Net__new();
-
-  my_user::add_molecules_to_nuc( 
-    Libnucnet__Net__getNuc( p_net ),
-    1,
-    i_max
-  );
-
-  my_user::add_reactions_to_net( p_net, 1, 10 );
-  my_user::add_forward_reactions_to_net( p_net, 10, i_max );
-
-  Libnucnet__Net__writeToXmlFile( 
-    p_net,
-    "data/my_net.xml" 
-  );
-
-  Libnucnet__Net__free( p_net );
-
-  return EXIT_SUCCESS;
-
-}

### 2013-07-14 my_molecule_utilities.cpp

@@ -1,118 +1,0 @@
-////////////////////////////////////////////////////////////////////////////////
-// This file was originally written by Tianhong Yu.
-//
-// This is free software; you can redistribute it and/or modify it
-// under the terms of the GNU General Public License as published by
-// the Free Software Foundation; either version 2 of the License, or
-// (at your option) any later version.
-//
-// This software is distributed in the hope that it will be useful,
-// but WITHOUT ANY WARRANTY; without even the implied warranty of
-// MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-// GNU General Public License for more details.
-//
-////////////////////////////////////////////////////////////////////////////////
-
-////////////////////////////////////////////////////////////////////////////////
-//! \file
-//! \brief Carbon molecule utility code. 
-////////////////////////////////////////////////////////////////////////////////
-
-#include "my_molecule_utilities.h"
-
-namespace my_user
-{
-
-//##############################################################################
-// add_default_molecules_to_nuc().
-//##############################################################################
-
-void
-add_default_molecules_to_nuc( 
-  Libnucnet__Nuc * p_nuc
-)
-{
-
-  add_molecules_to_nuc( p_nuc, 1, 100 );
-
-}
-
-//##############################################################################
-// add_molecules_to_nuc().
-//##############################################################################
-
-void
-add_molecules_to_nuc(
-  Libnucnet__Nuc * p_nuc,
-  unsigned int i_lo,
-  unsigned int i_hi
-)
-{
-
-  gsl_vector * p_t9, * p_log10_partf;
-  std::string s_state;
-
-  p_t9 = gsl_vector_alloc( 1 );
-  p_log10_partf = gsl_vector_alloc( 1 );
-
-  gsl_vector_set( p_t9, 0, 1. );
-  gsl_vector_set( p_log10_partf, 0, 0. );
-
-  //============================================================================
-  // Add Carbon and neutron. 
-  //============================================================================
-
-  s_state = "";
-
-  for( unsigned int i = i_lo; i <= i_hi; i++ )
-    add_molecule_to_nuc( p_nuc, i, i, s_state, p_t9, p_log10_partf );
-
-  add_molecule_to_nuc( p_nuc, 0, 1, s_state, p_t9, p_log10_partf );
-
[…]

### 2013-07-14 my_molecule_utilities.h

@@ -1,55 +1,0 @@
-////////////////////////////////////////////////////////////////////////////////
-// This file was originally written by Tianhong Yu.
-//
-// This is free software; you can redistribute it and/or modify it
-// under the terms of the GNU General Public License as published by
-// the Free Software Foundation; either version 2 of the License, or
-// (at your option) any later version.
-//
-// This software is distributed in the hope that it will be useful,
-// but WITHOUT ANY WARRANTY; without even the implied warranty of
-// MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-// GNU General Public License for more details.
-//
-////////////////////////////////////////////////////////////////////////////////
-
-////////////////////////////////////////////////////////////////////////////////
-//! \file
-//! \brief A header file for the carbon molecule utilities file.
-////////////////////////////////////////////////////////////////////////////////
-
-//##############################################################################
-// Includes.
-//##############################################################################
-
-#include <iostream>
-#include <Libnucnet.h>
-
-namespace my_user
-{
-
-//##############################################################################
-// Prototypes.
-//##############################################################################
-
-void
-add_default_molecules_to_nuc(
-  Libnucnet__Nuc *
-);
-
-void
-add_molecules_to_nuc(
-  Libnucnet__Nuc *, unsigned int, unsigned int
-);
-
-void
-add_molecule_to_nuc(
-  Libnucnet__Nuc *, 
-  unsigned int, 
-  unsigned int, 
-  std::string, 
-  gsl_vector *,
-  gsl_vector *
-);
-
-}

### 2013-07-14 my_network_utilities.cpp

@@ -1,4 +1,4 @@
-//////////////////////////////////////////////////////////////////////////////
+////////////////////////////////////////////////////////////////////////////////
 // This file was originally written by Tianhong Yu.
 //
 // This is free software; you can redistribute it and/or modify it
@@ -15,13 +15,105 @@
 
 ////////////////////////////////////////////////////////////////////////////////
 //! \file
-//! \brief My utility code. 
+//! \brief Carbon molecule utility code. 
 ////////////////////////////////////////////////////////////////////////////////
 
-#include "my_reaction_utilities.h"
+#include "my_network_utilities.h"
 
 namespace my_user
 {
+
+//##############################################################################
+// add_default_molecules_to_nuc().
+//##############################################################################
+
+void
+add_default_molecules_to_nuc( 
+  Libnucnet__Nuc * p_nuc
+)
+{
+
+  add_molecules_to_nuc( p_nuc, 1, 10 );
+
+}
+
+//##############################################################################
+// add_molecules_to_nuc().
+//##############################################################################
+
+void
+add_molecules_to_nuc(
+  Libnucnet__Nuc * p_nuc,
+  unsigned int i_lo,
+  unsigned int i_hi
+)
+{
+
+  gsl_vector * p_t9, * p_log10_partf;
+  std::string s_state;
+
+  p_t9 = gsl_vector_alloc( 1 );
+  p_log10_partf = gsl_vector_alloc( 1 );
+
+  gsl_vector_set( p_t9, 0, 1. );
+  gsl_vector_set( p_log10_partf, 0, 0. );
+
+  //============================================================================
+  // Add Carbon and neutron. 
+  //============================================================================
+
+  s_state = "";
+
+  for( unsigned int i = i_lo; i <= i_hi; i++ )
+    add_molecule_to_nuc( p_nuc, i, i, s_state, p_t9, p_log10_partf );
+
+  //add_molecule_to_nuc( p_nuc, 0, 1, s_state, p_t9, p_log10_partf );
+
+  gsl_vector_free( p_t9 );
+  gsl_vector_free( p_log10_partf );
+
+}
+
+//##############################################################################
+// add_molecule_to_nuc().
[…]

### 2013-07-14 my_network_utilities.h

@@ -15,7 +15,7 @@
 
 ////////////////////////////////////////////////////////////////////////////////
 //! \file
-//! \brief A header file for the carbon utilities file.
+//! \brief A header file for my network utilities file.
 ////////////////////////////////////////////////////////////////////////////////
 
 //##############################################################################
@@ -28,9 +28,40 @@
 #include <Libnucnet.h>
 #include <boost/foreach.hpp>
 #include <boost/lexical_cast.hpp>
+#include "nnt/auxiliary.h"
 
 namespace my_user
 {
+
+#define S_PHOTON_END               "photon end"
+#define S_RUN_BIN                  "run bin"
+#define S_BIN_START                "bin start"
+#define S_BIN_SIZE                 "bin size"
+#define S_BIN_NUMBER               "bin number"
+
+//##############################################################################
+// Prototypes.
+//##############################################################################
+
+void
+add_default_molecules_to_nuc(
+  Libnucnet__Nuc *
+);
+
+void
+add_molecules_to_nuc(
+  Libnucnet__Nuc *, unsigned int, unsigned int
+);
+
+void
+add_molecule_to_nuc(
+  Libnucnet__Nuc *, 
+  unsigned int, 
+  unsigned int, 
+  std::string, 
+  gsl_vector *,
+  gsl_vector *
+);
 
 struct ReactionData {
 
@@ -43,10 +74,6 @@ struct ReactionData {
   std::vector<std::pair<std::string,std::string> > vUserRateData;
 
 };
-
-//##############################################################################
-// Prototypes.
-//##############################################################################
 
 void
 add_default_reactions_to_net( Libnucnet__Net * );
@@ -72,4 +99,9 @@ add_reaction_to_net(
   ReactionData &
 );
 
-}
+int
+update_bin_net(
+  Libnucnet *
+);
+
+} // my_user

### 2013-07-14 run_carbon.cpp

@@ -44,13 +44,22 @@
 #define D_Y_MIN_DT     1.e-10       // Smallest y for dt update
 #define S_SOLVER       nnt::s_ARROW // Solver type: ARROW or GSL
 
-#define S_IDL_PRINT    "idl print"
-
 void
 my_print_abundances( nnt::Zone & );
 
 int
 print_abundance( Libnucnet__Species *, Libnucnet__Zone * );
+
+int
+print_bin_abundances( nnt::Zone & ); 
+
+double
+compute_bin_sum( nnt::Zone & );
+
+void
+bin_update_timestep(
+  nnt::Zone &, double &, double, double, double
+);
 
 //##############################################################################
 // main().
@@ -117,12 +126,10 @@ int main( int argc, char * argv[] ) {
   else
   {
     d_t = 0;
-
     zone.updateProperty(
       nnt::s_TIME,
       boost::lexical_cast<std::string>( d_t )
     );
-
   }
 
   //============================================================================
@@ -185,14 +192,16 @@ int main( int argc, char * argv[] ) {
       )
     ) << std::endl;
 
-  while ( d_t < boost::lexical_cast<double>( zone.getProperty( nnt::s_TEND ) ) )
+  while ( 
+    d_t < boost::lexical_cast<double>( zone.getProperty( nnt::s_TEND ) )
+  )
   {
 
     d_t += d_dt;
 
-  //============================================================================
-  // Set dt and t.
-  //============================================================================
+    //==========================================================================
+    // Set dt and t.
+    //==========================================================================
 
     zone.updateProperty(
       nnt::s_DTIME,
@@ -204,36 +213,35 @@ int main( int argc, char * argv[] ) {
       boost::lexical_cast<std::string>( d_t )
     );
 
-  //============================================================================
-  // Update temperature and density.  Update dt and time again in case
-  // changed in update_zone_properties.
-  // Also update Ya, number of atoms per nucleon.
-  //============================================================================
+    //==========================================================================
+    // Update temperature and density.
+    //==========================================================================
 
[…]

### 2013-07-19 doc/HeShell.tex
Add to repository.

\documentclass[manuscript]{aastex}

\newcommand{\cenn}{{\rm C}_n}
\newcommand{\cnr}{{\rm C}_n^r}
\newcommand{\hep}{{\rm He}^+}

\newcommand{\ctwo}{{\rm C}_2}
\newcommand{\cthree}{{\rm C}_3}
\newcommand{\cfour}{{\rm C}_4}
\newcommand{\cfive}{{\rm C}_5}
\newcommand{\csix}{{\rm C}_6}
\newcommand{\cseven}{{\rm C}_7}
\newcommand{\ceight}{{\rm C}_8}
\newcommand{\ceightr}{{\rm C}_8^r}
\newcommand{\cotoco}{${\rm C} + {\rm O} \to {\rm CO} + \gamma$}
\newcommand{\twoctoctwo}{${\rm C} + {\rm C} \to \ctwo + \gamma$}
\newcommand{\coctoctwo}{${\rm CO} + {\rm C} \to \ctwo + {\rm O}$}
\newcommand{\ctowotococ}{$\ctwo + {\rm O} \to {\rm CO} + {\rm C}$}
\newcommand{\cfivectocsix}{$\cfive + {\rm C} \to \csix$}
\newcommand{\csixotococfive}{${\rm C}_6 + {\rm O} \to {\rm CO} + {\rm C_5}$}
\newcommand{\ncogeq}{n_{CO}^{\gamma eq}}
\newcommand{\nar}{New Astron. Rev.}

\shorttitle{Formation of $\cenn$ Molecules}
\shortauthors{Clayton et al.}

\begin{document}

\title{CARBON CONDENSATION NEAR THE HE SHELL IN SUPERNOVAE}

\author{Donald D. Clayton, Bradley S. Meyer, Lih-Sin The and Tianhong Yu}
\affil{Department of Physics and Astronomy, Clemson University, Clemson, SC 29634-0978}

\begin{abstract}
\end{abstract}

\keywords{atomic processes --- ISM: abundances --- ISM: general --- meteorites, meteors, meteoroids --- supernovae: general --- supernovae: individual (SN 1987A)}

\section{Introduction}

A strategy for this study is to compare the growth of carbon grains from 
three zones near the He-burning shell of Type II supernovae. That shell 
has long drawn attention because incomplete He burning synthesizes more 
carbon than oxygen (Clayton 1968, Ch. 5), yielding throughout the He 
convection zone an abundance ratio C/O $>$ 1 (e.g. Woosley and Weaver 1995) 
that has long been speculated to be of significance for carbon condensation; 
moreover, explosive burning subsequent to the core-collapse shock wave 
yields isotopic features ($e.g. ^{15}$N, $^{18}$O, $^{26}$Al) 
that present important diagnostic clues to the provenance of measured 
isotopic ratios in the large supernova grains extracted from meoteorites 
($e.g.$ Zinner 1998; Clayton and Nittler 2004). 
In fact, this He shell would be the only zone of SNII wherein C condensation 
would be possible if one were to adhere to thermal-equilibrium condensation.

The rapidly changing supernova environment makes equilibrium condensation 
doubtful and seems to necessitate a kinetic theory. In this study we 
will employ the kinetic theory of carbon nucleation and growth by 
Clayton, Liu and Dalgarno (1999), which has been augmented by 
several subsequent studies (Clayton, Denealt and Meyer 2001; 
Deneault, Heger and Clayton 2003; Deneault, 
Clayton and Meyer 2006; Clayton 2013; 
Yu, Meyer and Clayton 2013). 
That kinetic model of nucleation involves (1) a nearly steady-state 
concentration of linear carbon chains $\cenn$ in the expanding gas, 
(2) transitions of sufficiently long $\cenn$ to ringed isomers, $\cnr$, 
and (3) kinetic capture of free C atoms by ringed $\cnr$. All occur within 
the rapidly expanding and cooling environment. This kinetic model was 
initially proposed to demonstrate that condensation of carbon within 
oxygen-rich gas (C/O $<$ 1) is possible, even inevitable, but it is also a 
reasonable model within C-rich gas. In this work we will apply that model 
within three nearby zones in the supernovae: (1) in the He-exhausted CO core 
just beneath the He-burning shell; (2) in the He-burning shell; (3) above the 
He-burning convective shell. These experience comparable Compton-electron 
fluxes (which we will calculate) but differ significantly in internal 
C/O abundance ratio: in (1) C/O $<$ 1; in (2) C/O $>>$ 1; in (3) C/O is near 
unity but with much smaller concentrations of both C and O.

Condensation studies have shown that if C/O $<$ 1 oxidation of carbon chains 
reduces their concentration but does not consume them 
(e.g. Clayton, Deneault and Meyer 2001, Fig.2). 
Their abundances $Y_n$ establish a nearly steady state in which reproduction 
by free C balances the oxidation losses. Consequently the number of free 
C atoms per $\cnr$ ring increases with decreasing C/O bulk ratio, so that 
larger but scarcer graphite grains may result. This startling finding, 
which may explain scarcity of graphite SUNOCONs in comparison with 
bulk supernova carbon, was given the name “population control” 
(Clayton, Deneault and Meyer 2001; Deneault, Clayton and Meyer 2006; 
Clayton 2011). 
To examine its relevance to the three zones described above, we will 
calculate grain growth to terminal size within them and compare results.

A second goal is to understand consequences of the time dependence of the 
fluxes of Compton electrons in these three zones. The buildup locally of 
the intensity of the flux of scattered gamma rays depends on the optical 
depth between the field point and the distribution of radioactive $^{56}$Co. 
The most significant chemical consequences of these energetic electrons lie 
in the creation of $\hep$ and the direct dissociation of CO molecules. These 
chemical effects are time dependent. To study this time dependence we 
calculate the energy deposition by the resulting Compton electrons as a 
function of time in three differing models of the postsupernova that 
differ in their degree of outward transport of radioactive $^{56}$Ni, so 
that the lifetimes of He and of CO can be treated in a time-dependent 
manner within the chemical network. The $\hep$ ion dissociates molecules 
owing to the energetic charge exchange when $\hep$ is neutralized during 
collisions with them. The dissociation of CO molecules by both $\hep$ and 
Compton electrons provides an ongoing source of free carbon that maintains 
the abundances of Cn against oxidation and also feeds the growth of 
larger carbon grains.

\section{The Compton Electron Flux and the Lifetimes of He and CO}

To calculate the lifetimes of He and CO against energetic Compton electrons 
we employ the gamma-ray transport code constructed by 
The, Burrows and Bussard (1990) to obtain the energy deposition 
rate in Compton electrons $\epsilon(t)$ as a function of position and of time 
in the supernova. We then calculate the lifetimes of He and of CO using the 
concept of $energy$ $per$ $ion$ $pair$. The lifetimes are inserted into 
our chemical 
reaction network (Yu, Meyer and Clayton 2013), providing time-dependent source 
terms for the abundance of $\hep$ and for dissociation of CO; namely,
\begin{equation}
\frac {{\rm d}Y(\hep)} {{\rm d}t} =
  \frac {Y(He)}{\tau_e(He)} - {\rm destruction\ rate\ of\ }Y(\hep)
\end{equation}
\begin{equation}
\frac {{\rm d}Y(CO)} {{\rm d}t} =
  -\frac {Y(CO)}{\tau_e(CO)} - 
  \frac {Y(CO)}{\tau_\hep(CO)} + 
  {\rm production\ rate\ of\ }Y(CO)
\end{equation}
where $\tau_e(CO)$ is the lifetime of CO against Compton electrons and 
$\tau_\hep(CO)$ is the lifetime of CO against $\hep$. These lifetimes are 
calculated by us from the radioactive energy deposition rates in three 
models of SNII that differ only in their degree of central confinement of 
radioactive $^{56}$Ni. Our standard SNII is represented by model w10hmm of 
SN1987A (Pinto and Woosley 1988). That model mixed radioactive 
56Ni outward between $M_r$=2 and $M_r$=15 with a declining radial 
concentration in such a way as to reproduce the observed early emergence of 
hard X rays from the surface of SN87A.

We take the spherically symmetric decline with increasing radius of 
the radial  density of $^{56}$Co radioactivity mixed outward to represent 
Pinto and Woosley’s (1988)  spherically symmetric approximation 
of the gamma-ray transport effects of several non spherical fingers of 
$^{56}$Co that were transposed with overlying gas in the radial outward flow. 
The energetic 10-30keV X rays were measured by Japan satellite $Ginga$ 
(Dotani et al. (1987)) in early July 1987, about five months following 
SN87A. Their measurements showed the flux to grow throughout that summer, 
leveling off in September. By mid August the Russian $Mir-Kvant$ observatory 
had detected harder 20-300keV X rays with phoswitch detectors 
(Sunyaev et al. (1987)). These detections agree except below 10keV, 
although emphasizing different portions of the spectrum. Taken together they 
suggest that the hard X ray flux from Compton scattering grew steadily in 
SN87A for the first six months (say from $5\times 10^6$s to $1.5\times 10^7$s). 
Using the w10hmm mixing model enables us to compute $\epsilon(t)$ at the He 
shell as a function of time for that supernova model.

We compare the energy deposition rate in model w10hmm with those from 
otherwise identical models in which $^{56}$Ni concentration has the same 
radial profile out only to $M_r=3.5$, slightly beneath the He burning shell 
(w10hmm3.5), and another in which 56Ni remains confined to central 
$M_r=2.0$ (w10hmmc). The extent of radial mixing governs the rise time 
for energy deposition in the He burning shell. These alterations of 
the mixing profile illustrate models of SNII that differ plausibly from 
SN87A. In each of those three models of SNII we calculate the energy 
deposition rates $\epsilon(t)$ in the three zones of SNII described above. 
Those rates of energy deposition as energies of Compton electrons provide 
$\epsilon(t)$ at the He shell as a function of time. Thus 
$\tau_e(He)$ will also be a 
function of time. That means that $\hep$/He will also be a function of time. 
Because $\hep$ has some important chemical reactions (such as dissociating CO), 
the chemical network takes on a new time dependence that did not exist in 
Yu et al. (2013). We fit, approximately, $\epsilon(t)$ for 10hmm to a simple 
function of time at the He shell. Then $\tau_e(He)$ will express as the same 
function of time, as will also $Y(\hep$). These values can be read into the 
network from the analytic fit. Then we then compare $Y_8^r$ in three 
neighboring 
zones: $M_r=3.8$ just under He-burning shell, $M_r=4.2$ in He-burning shell, 
and $M_r=6.1$ above He-burning shell. These differ interestingly in 
elemental and isotopic compositions. Table (ref1) lists the initial 
compositions of the important chemical elements in these three zones. 
We include N and Ne despite their absence from the current version of our 
chemical network:

That composition lists only five elements, He, C, O, N and Ne. The first 
three are the only elements in our current chemical network 
(Yu et al. 2013), because those three elements govern the formation of 
linear $\cenn$. When performing our chemical network calculations for the 
number of rings $Y_8^r$ formed in those zones, we use the unmixed composition 
of each zone, although Pinto and Woosley (1988, see their Fig. ref1) 
actually mixed the supernova with a prescribed radial concentration 
gradient using spherical symmetry befitting the intended gamma-ray 
propagation code. But we calculate molecular reactions in the unmixed zones 
on the expectation that most of the mass of the zones remains unmixed 
chemically. Our paper will focus on the molecular differences among these 
three zones in the attempt to understand the effects of differing chemical 
compositions and of time-dependent $\tau_e$.

Characteristic values from our calculations with model 10hmm are given in 
Table ref2:

Our calculations displayed in Fig. ref1 show that $\epsilon(t)$ varies with 
time in proportion to the rate of $^{56}$Co decay, namely exp(-t/111d). 
That exponential line is plotted also in Fig. ref1 through the value 
1.870E+07 ergs/g/s at t=100d:  therefore, at $M_r=5.90$, 
$\epsilon(t)$=1.870E+7exp(-(t-100d)/111d) ergs/g/s. The fit is excellent, 
confirming that no other time dependences are significant in this time range. 
Similar fits are obtained for the two other zones. The absence of 
other time dependences reflects that fact that w10hmm mixed $^{56}$Co 
substantially to beyond the He shell, so that the gamma flux is 
immediately present. The rate of increase of $\epsilon(t)$ at (t=100d) 
between CO 
core and He shell is approximately d$\epsilon(t)$/d$M_r$ = -1.0E+07 ergs/g/s 
per solar mass. These values can be used to calculate the lifetimes 
$\tau_e(He)$ 
and $\tau_e(CO)$ as functions of time and radial mass zone. The rising values 
of $\epsilon(t)$ for t$<$50d are due to still live $^{56}$Ni mixed out to 
these zones; but we can ignore that time dependence because for t$<$50d the 
model temperature is too hot for stable molecules.

\acknowledgments

T. Y. gratefully acknowledges the support of
a NASA Earth and Space Science Fellowship.
This work was also supported by NASA grant NNX10AH78G.

\end{document}

### 2013-07-27 doc/condensation.tex
Modify text.

--- 2013-07-07 doc/condensation.tex
@@
 \frac{{\rm d}n_1}{{\rm d}t} = 
-  -k \, n_1 n_2 + \lambda_\gamma n_3
+  -\lambda_{12} \, n_1 n_2 + \lambda_\gamma n_3
 \label{eq:number_density}
 \end{equation}
-where $k$ is the reaction rate in the unit of $cm^3s^{-1}$ and 
+where $\lambda_{12}$ is the reaction rate in the unit of $cm^3s^{-1}$ and 
 $\lambda_\gamma$ is the photodissociation rate of species 3 with the unit of
@@
 \frac{{\rm d}Y_1}{{\rm d}t} = 
-  -k n_{atom} =
-  -k \rho N_A Y_{atom} Y_1 Y_2 + \lambda_\gamma Y_3
+  -\lambda_{12} n_{atom} Y_1 Y_2 + \lambda_\gamma Y_3 =
+  -\lambda_{12} \rho N_A Y_{atom} Y_1 Y_2 + \lambda_\gamma Y_3
 \label{eq:abundance}
@@
 \begin{equation}
-P_1 + P_i \longleftrightarrow P_{i+1} + \gamma
+P_1 + P_i \to P_{i+1} + \gamma
 \label{eq:reaction}
 \end{equation} 
-where $P_i$ denotes a particle with $i$ atoms in it.
+where $P_i$ denotes a particle with $i$ atoms in it. Here we are neglecting
+the photodissociation for large stable particles.
 
 Let's assume that the condensation rate is proportional to the surface area
-(or cross section) of the larger particle, which goes like $n^{2/3}$, i.e.
+(or cross section) of the larger particle, which goes like $N^{2/3}$, i.e.
 \[
-k \propto A \propto n^{2/3}
+\lambda \propto A \propto N^{2/3}
 \]
-where $k$ is the rate, $A$ is the surface area and $n$ is the number of atoms
-in the particle.
+or
+\[
+\lambda_i = \lambda_1 N_i^{2/3}
+\]
+where $\lambda$ is the rate, $A$ is the surface area and $N$ is the number 
+of atoms in the particle.
 
-To make the calculation of a large atom number particle possible, we introduce
-the ``bin" after a continuous size increment. In a bin we neglect the details 
-of the single particles and focus on the
-two ends of the bin. For example if we start the bin from size $a$ and the bin 
-size is 10, the particles we care about after size $a$
-are just $P_a$, $P_{10a}$, $P_{100a}$, etc. 
-And we just calculate the effective reaction rates between these particles.
-
-From graph theory we know that for a series of vertices 1, 2, ..., N, the
-effective rate between 1 and N is like:
+To make the calculation of particles with a large atom number possible, we 
+introduce
+the ``bin" after a continuous network. There will a number of particles in a 
+bin and we assume \textbf{steady state} within a bin.
+The rate out of a bin is like
 \[
-k_{1,N}^{eff} \Delta t = \frac 
-  { k_{1,2}k_{2,3}...k_{N-1,N}\Delta t^{N-1} }
-  { 
-    k_{2,3}k_{3,4}...k_{N-1,N}\Delta t^{N-2} +
-    k_{1,2}k_{3,4}...k_{N-1,N}\Delta t^{N-2} +
-    ...
-    k_{1,2}...k_{N-2,N-1}\Delta t^{N-2}
-  }
-\]
-
-\[
-k_{1,N}^{eff} = \frac {1}
-  { 
-    \frac{1}{k_{1,2}} +
-    \frac{1}{k_{2,3}} +
-    ...
-    \frac{1}{k_{N-1,N}}
-  }
-\]
-
-Back to the problem we are looking at(Eq.\ref{eq:reaction}), we can write
-\[
-k_{i,i+1} \equiv k_i = k_1 i^{2/3}
-\]
-If we start from $p_a$, for the bin size of $b$ we can write the effective
-reaction as:
-\[
-P_a + a\times (b-1) P_1 \to P_{a\times b}
-\]
-And the effective rate is
-\[
-k^{eff} = \frac {1}
-  {
-    \frac {1} {k_{a}} +
-    \frac {1} {k_{a+1}} +
-    ...
-    \frac {1} {k_{a\times b}}
-  }
+\lambda_{bin,last}Y_{bin,last} = \lambda^{eff}_{bin}Y_{bin}
 \]
 \[
-\frac {1} {k_{eff}} =
-  \sum_{i=a}^{a\times b} \frac {1} {k_i} =
-  \frac{1}{k_1} \sum_{i=a}^{a\times b} \frac {1} {i^{2/3}} \approx
-  \frac{1}{k_1} \int_a^{a\times b} x^{-2/3} {\rm d} x =
-  \frac{1}{k_1} \cdot 3 \cdot [(a\times b)^{1/3} - a^{1/3}]
+Y_{bin} = \sum_{i\in bin} Y_i
 \]
 \[
-k^{eff} = \frac{k_1}{3} 
-  \frac{1}{ (a\times b)^{1/3} - a^{1/3} }
+\lambda^{eff}_{bin} = \lambda_{bin,last} \left(
+  \frac{Y_{bin,last}}{Y_{bin}}
+  \right)_{ss}
+  = \lambda_{bin,last} \left(
+  \frac{1}{\sum_{i\in bin} \frac{Y_i}{Y_{bin,last}} }
+  \right)_{ss}
 \]
-
-If we denote the atom number at the beginning of a bin as $N_{begin}$ and
-the one at the end as $N_{end}$, then we can write the effective rate as:
+For steady state,
+\[
+\frac{Y_i}{Y_j} = \frac{\lambda_i}{\lambda_j}
+\]
+so,
+\[
+\lambda^{eff}_{bin} = \lambda_{bin,last} \left(
+  \frac{1}{\sum_{i\in bin} \frac{\lambda_{bin,last}}{\lambda_i} }
+  \right)
+  = \frac{1}{\sum_{i\in bin} \frac{1}{\lambda_i} }
+  = \lambda_1 \frac{1}{\sum_{i\in bin} N_i^{-2/3}}
+\]
+If we apply the integral approximation,
 \begin{equation}
-k^{eff} = \frac{k_1}{3} 
-  \frac{1}{ N_{end}^{1/3} - N_{begin}^{1/3} }
+\lambda^{eff}_{bin}
+  \approx \lambda_1 \left( \int_{bin,fist}^{bin,last} x^{-2/3} {\rm d} x
+  \right)^{-1}
+  = \lambda_1 \frac{1}{N_{bin,last}^{1/3} - N_{bin,first}^{1/3}}
 \label{eq:rate}
@@
 
-We estimate $k_1$ as two single atoms collide together with thermal velocity
-and the transverse section.
+We estimate $\lambda_1$ as two single atoms collide together with thermal 
+velocity and the transverse section.
 \begin{equation}
-k_1 = \: <\! \sigma_1 v\! > \: = \pi R^2 \sqrt{3k_BT/m}
+\lambda_1 = \: <\! \sigma_1 v\! > \: = \pi R^2 \sqrt{3k_BT/m}
 \label{eq:k1}
@@
 
-The abundance change rates of $P_{begin}$, $P_{end}$ and $P_1$ due to 
-reaction $P_{begin} + X P_1 \longleftrightarrow P_{end} + \gamma$ are
+The abundance change rates of $Y_{bin,i}$, $Y_{bin,i+1}$ and $Y_1$
+due to 
+reaction ${\rm Bin}_i + X P_1 \to {\rm Bin}_{i+1} + \gamma$ are
 \[
-\frac{{\rm d}Y_{begin}}{{\rm d}t} =
-  -k^{eff} Y_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end}  
+\frac{{\rm d}Y_{bin,i}}{{\rm d}t} =
+  -\lambda_i^{eff} n_{atom} Y_{bin,i} Y_1
 \]
 \[
-\frac{{\rm d}Y_{end}}{{\rm d}t} =
-  k^{eff} Y_{atom} Y_{begin} Y_1 - \lambda_\gamma^{eff} Y_{end}  
+\frac{{\rm d}Y_{bin,i+1}}{{\rm d}t} =
+  \lambda_i^{eff} n_{atom} Y_{bin,i} Y_1
 \]
@@
 \frac{{\rm d}Y_1}{{\rm d}t} =
-  X( -k^{eff} Y_{atom} Y_{begin} Y_1 + \lambda_\gamma^{eff} Y_{end} )
+  X( -\lambda_i^{eff} n_{atom} Y_{bin,i} Y_1 )
 \]
-where $\lambda_\gamma^{eff}$ is the effective photodissociation rate which
-will be discussed later and $X$ is the factor to be determined that ensure
+where $X$ is the factor to be determined that ensure
 the total atom number conserved. Atom conservation requires
 \[
-N_{begin} \times \frac{{\rm d}Y_{begin}}{{\rm d}t} +
-N_{end} \times \frac{{\rm d}Y_{end}}{{\rm d}t} +
+N_{bin,i} \times \frac{{\rm d}Y_{bin,i}}{{\rm d}t} +
+N_{bin,i+1} \times \frac{{\rm d}Y_{bin,i+1}}{{\rm d}t} +
 \frac{{\rm d}Y_1}{{\rm d}t} = 0.
@@
 \[
-X = N_{end} - N_{begin}
+X = N_{bin,i+1} - N_{bin,i}
+\]
+
+Similarly the abundance change rates of $Y_{last}$, $Y_{bin,1}$ and 
+$Y_1$ due to reaction $P_{network,last} + X P_1 \to {\rm Bin}_1 + \gamma$ are
+\[
+\frac{{\rm d}Y_{last}}{{\rm d}t} =
+  -\lambda_{last} n_{atom} Y_{last} Y_1
+\]
+\[
+\frac{{\rm d}Y_{bin,1}}{{\rm d}t} =
+  \lambda_{last} n_{atom} Y_{last} Y_1
+\]
+\[
+\frac{{\rm d}Y_1}{{\rm d}t} =
+  (-\lambda_{last} n_{atom} Y_{last} Y_1) \times
+  (N_{bin,1} - N_{last})
+\]
+
+\section{Network Matrix}
+Let's look at the reaction between the last species in the continuous network
+and the first bin, 
+the changes of the root-finding functions are (how to call them?)
+(denoting $n_{atom}$ as $n_a$):
+\[
+f_{last} \: +\!\!= \: \lambda_{last} \, n_a Y_{last} Y_1
+\]
+\[
+f_{1} \: +\!\!= \: (\lambda_{last} \, n_a Y_{last} Y_1) 
+  (N_{bin,1} - N_{last})
+\]
+To find the abundance changes in the continuous network, we need to solve the
+matrix
+\[
+AX=B
+\]
+The matrix element changes due to this reaction are
+\[
+A_{last,last} \: +\!\!= \: \lambda_{last} \, n_a Y_1
+\]
+\[
+A_{last,1} \: +\!\!= \: \lambda_{last} \, n_a Y_{last}
+\]
+\[
+A_{1,last} \: +\!\!= \: (\lambda_{last} \, n_a Y_1)(N_{bin,1} - N_{last})
+\]
+\[
+A_{1,1} \: +\!\!= \: (\lambda_{last} \, n_a Y_{last})(N_{bin,1} - N_{last})
+\]
+The right-hand-side vector changes are
+\[
+B_{last} \: +\!\!= \: -f_{last} = -\lambda_{last} \, n_a Y_{last} Y_1 
+\]
+\[
+B_1 \:+\!\!=\: -f_1 = -(\lambda_{last}\,n_a Y_{last} Y_1)(N_{bin,1}-N_{last})
+\]
+
+Now let's look at the reactions between bins. 
+${\rm Bin}_i + (N_{bin,i+1}-N_{bin,i})P_1 \to {\rm Bin}_{i+1}$,
+where $i$ goes from 1 to $N-1$ with $N$ as the number of bins.
+\[
+\left( \frac{{\rm d}Y_1}{{\rm d}t}\right) _i =
+  ( -\lambda^{eff}_{bin,i} \, n_a Y_{bin,i} Y_1 )(N_{bin,i+1} - N_{bin,i})
+\]
+\[
+(f_{1})_i \: +\!\!= \: 
+  (\lambda^{eff}_{bin,i} \, n_a Y_{bin,i} Y_1) (N_{bin,i+1} - N_{bin,i})
+\]
+\[
+(A_{1,1})_i \: +\!\!= \: 
+  (\lambda^{eff}_{bin,i} \, n_a Y_{bin,i}) (N_{bin,i+1} - N_{bin,i})
+\]
+\[
+(B_1)_i \:+\!\!=\: -(f_1)_i = 
+  -(\lambda^{eff}_{bin,i} \, n_a Y_{bin,i} Y_1) (N_{bin,i+1} - N_{bin,i})
+\]
+We first solve the matrix equation for current $Y_{bin,i}$, and then compute
+the abundance changes in bins using the new abundances in the network 
+(as showed below).
+Then feed the new bin abundances back to the matrix. Iterate until converge.
+
+\section{Bin Abundances Change}
+
+Now let's look at the abundance changes in bins for each reaction discussed
+above. We are going to solve these changes implicitly. For $Y_{bin,1}$,
+\[
+\frac {Y_{bin,1}(t+\Delta t) - Y_{b1}(t)} {\Delta t} =
+  \lambda_{last} \, n_a Y_{last}(t+\Delta t) Y_1(t+\Delta t) -
+  \lambda^{eff}_{bin,1} \, n_a Y_{bin,1}(t+\Delta t) Y_1(t+\Delta t)
+\]
+\[
+Y_{bin,1}(t+\Delta t) = \frac
+  {\lambda_{last} \, n_a Y_{last}(t+\Delta t) Y_1(t+\Delta t) \Delta t +
+    Y_{bin,1}(t)}
+  {1 + \lambda^{eff}_{bin,1} \, n_a Y_1(t+\Delta t) \Delta t}
+\]
+Similarly for $Y_{bin,i}$ as $i$ goes from 2 to $N-1$:
+\[
+Y_{bin,i}(t+\Delta t) = \frac
+  {\lambda^{eff}_{bin,i-1} \, n_a Y_{bin,i-1}(t+\Delta t) Y_1(t+\Delta t) 
+    \Delta t +
+    Y_{bin,i}(t)}
+  {1 + \lambda^{eff}_{bin,i} \, n_a Y_1(t+\Delta t) \Delta t}
+\]
+For $Y_{bin,N}$ we don't have any destructive terms for now,
+\[
+Y_{bin,N}(t+\Delta t) = 
+  \lambda^{eff}_{bin,N-1} \, n_a Y_{bin,N-1}(t+\Delta t) Y_1(t+\Delta t) 
+    \Delta t +
+    Y_{bin,N}(t)
 \]

### 2013-07-27 carbon_evolve.cpp
Commit to save change, but not working yet.

@@ -38,7 +38,7 @@ evolve(
   gsl_vector *p_y_old, *p_rhs, *p_sol, *p_work;
   double d_dt;
   std::pair<double,double> check;
-  double check_bin = 0;
+  double check_bin = 0.;
   
   //==========================================================================
   // Evolve NSE + weak rates, if appropriate.
@@ -163,7 +163,7 @@ evolve(
     gsl_vector_free( p_work );
 
     //--------------------------------------------------------------------------
-    // Compute bin abundance changes.
+    // Evolve bins. 
     //--------------------------------------------------------------------------
 
     if( 
@@ -171,13 +171,13 @@ evolve(
       zone.getProperty( "run bin" ) == "yes"
     )
     {
- 
+     
       evolve_bin( zone, v_bin_old );
-
+    
       check_bin = check_bin_change( zone );
-
+    
     }
-
+    
     //--------------------------------------------------------------------------
     // Free matrix, p_rhs, and p_sol. Remember
     // Libnucnet__Zone__computeJacobianMatrix returns a new matrix and
@@ -193,7 +193,7 @@ evolve(
     // Exit iterations if converged.
     //--------------------------------------------------------------------------
 
-    if( check.first < D_MIN && check_bin < 1.e-8 ) break;
+    if( check.first < D_MIN && check_bin < D_MIN ) break;
 
   }
 
@@ -232,7 +232,7 @@ evolve(
     {
   
       zone.updateProperty(
-        "bin change", 
+        "bin abundance change", 
         boost::lexical_cast<std::string>( i ),
         boost::lexical_cast<std::string>( v_work[i-1] - v_bin_old[i-1] )
       );
@@ -268,18 +268,20 @@ update_bin_rates(
     exit( EXIT_FAILURE );
   }
 
-  double d_begin, d_end, d_rate;
+  double d_rate;
+  int i_begin, i_end;
+  int i_atom_number_diff;
 
   //==========================================================================
   // Get parameters.
   //==========================================================================
     
-  size_t i_bin_start =
-    boost::lexical_cast<size_t>( zone.getProperty( "bin start" ) ); 
[…]

### 2013-07-27 carbon_evolve.h

@@ -32,7 +32,12 @@ evolve( nnt::Zone& );
 
 double
 compute_effective_rate(
-  nnt::Zone &, double, double
+  nnt::Zone &, int
+);
+
+double
+compute_effective_rate(
+  nnt::Zone &, int, int
 );
 
 void
@@ -59,3 +64,9 @@ std::pair<WnMatrix *, gsl_vector *>
 get_evolution_matrix_and_vector( 
   nnt::Zone &
 );
+
+int
+compute_atom_numbers_in_bin(
+  int, int
+);
+

### 2013-07-27 carbon_hydro.cpp

@@ -148,6 +148,13 @@ get_nucnet( int argc, char **argv )
 
   Libnucnet__assignZoneDataFromXml( p_nucnet, argv[2], NULL );
 
+  //============================================================================
+  // Create bin molecules and reactions if desired. 
+  //============================================================================
+
+  if( my_user::update_bin_net( p_nucnet ) )
+    Libnucnet__assignZoneDataFromXml( p_nucnet, argv[2], NULL );
+
   return p_nucnet;
 
 }
@@ -185,6 +192,8 @@ initialize_zone( nnt::Zone& zone, char ** argv )
     nnt::s_T9,
     zone.getProperty( nnt::s_T9_0 )
   );
+
+  initialize_bin( zone );
 
 }
 
@@ -254,6 +263,8 @@ update_zone_properties( nnt::Zone& zone )
       nnt::s_RHO,
       boost::lexical_cast<std::string>( 1.e-30 )
     );
+
+  update_bin( zone );
 
 }
 
@@ -378,6 +389,10 @@ get_nucnet( int argc, char **argv )
     Libnucnet__Net__getNuc( Libnucnet__getNet( p_nucnet ) )
   );
 
+  my_user::add_default_reactions_to_net(
+    Libnucnet__getNet( p_nucnet )
+  );
+
   //============================================================================
   // Get zone data.
   //============================================================================
@@ -479,36 +494,7 @@ initialize_zone( nnt::Zone& zone, char ** argv )
   // Initialize bin abundances.
   //============================================================================
 
-  if( 
-    zone.hasProperty( "run bin" ) && 
-    zone.getProperty( "run bin" ) == "yes"
-  )
-  {
-
-    for(
-      unsigned i = 1;
-      i <= boost::lexical_cast<unsigned>( zone.getProperty( "bin number" ) );
-      i++
-    )
-    {
-
-      zone.updateProperty( 
-        "bin", 
-        boost::lexical_cast<std::string>( i ), 
-        "0." 
-      );
-
-      zone.updateProperty( 
-        "bin change", 
-        boost::lexical_cast<std::string>( i ), 
-        "0." 
-      );
-
-    }
-
-  }
-   
-  return;
+  initialize_bin( zone );
 
 }
 
@@ -530,12 +516,7 @@ update_zone_properties(
     v_log10_rho
   );
 
-  if(
[…]

### 2013-07-27 carbon_hydro.h

@@ -65,4 +65,8 @@ void get_trajectory_data( char * );
 
 double compute_carbon_k1( nnt::Zone & );
 
+void initialize_bin( nnt::Zone & );
+
+void update_bin( nnt::Zone & );
+
 #endif // CARBON_HYDRO

### 2013-07-27 my_network_utilities.cpp

@@ -33,7 +33,7 @@ add_default_molecules_to_nuc(
 )
 {
 
-  add_molecules_to_nuc( p_nuc, 1, 10 );
+  add_molecules_to_nuc( p_nuc, 1, (unsigned int) 1e1 );
 
 }
 
@@ -128,11 +128,21 @@ add_default_reactions_to_net(
   add_reactions_to_net(
     p_net,
     1,
+    10
+  );
+
+  add_forward_reactions_to_net( p_net, 10, 1e1 );
+
+/*
+  add_reactions_to_net(
+    p_net,
+    1,
     (unsigned int)
       Libnucnet__Nuc__getNumberOfSpecies(
         Libnucnet__Net__getNuc( p_net )
       )
   );
+*/
 
 }
 

### 2013-07-27 run_carbon.cpp

@@ -251,6 +251,8 @@ int main( int argc, char * argv[] ) {
       );
 
       if( 
+        zone.hasProperty( "run bin" ) &&
+        zone.getProperty( "run bin" ) == "yes" &&
         zone.hasProperty( "idl print" ) &&
         zone.getProperty( "idl print" ) == "yes"
       ) {
@@ -382,10 +384,17 @@ my_print_abundances(
 
     print_bin_abundances( zone );
 
+    std::cout << "1 - Xsum_network = " <<
+      1. - 
+      Libnucnet__Zone__computeAMoment( zone.getNucnetZone(), 1 ) << "  ";
+
+    double d_bin_mass = compute_bin_sum( zone );
+
     std::cout << "1 - Xsum = " <<
       1. - 
       Libnucnet__Zone__computeAMoment( zone.getNucnetZone(), 1 ) -
-      compute_bin_sum( zone ) <<
+      //compute_bin_sum( zone ) <<
+      d_bin_mass <<
       std::endl << std::endl;
 
   } else {
@@ -453,32 +462,38 @@ print_bin_abundances(
 {
 
   for(
-    size_t i = 1;
-    i <= boost::lexical_cast<size_t>( zone.getProperty( "bin number" ) );
+    int i = 1;
+    i <= boost::lexical_cast<int>( zone.getProperty( "bin number" ) );
     i++
   )
   {
 
     printf( "%16lu%16lu%16.6e%16.6e\n",
       (unsigned long)( 
-        boost::lexical_cast<size_t>( zone.getProperty( "bin start" ) ) *
+        boost::lexical_cast<int>( zone.getProperty( "bin start" ) ) *
         pow(
-          boost::lexical_cast<size_t>( zone.getProperty( "bin size" ) ),
-          i
-        )
+          boost::lexical_cast<int>( zone.getProperty( "bin factor" ) ),
+          i - 1
+        ) + 1
       ),
       (unsigned long)(
-        boost::lexical_cast<size_t>( zone.getProperty( "bin start" ) ) *
+        boost::lexical_cast<int>( zone.getProperty( "bin start" ) ) *
         pow(
-          boost::lexical_cast<size_t>( zone.getProperty( "bin size" ) ),
+          boost::lexical_cast<int>( zone.getProperty( "bin factor" ) ),
           i
         )
       ),
       boost::lexical_cast<double>( 
[…]
